### 2017-03-04 draft1.Rmd
formatted with rmd

---
author:
  - name: Ross Jacobucci
    affiliation: University of Notre Dame
    address: >
      First line
      Second line
    email: rcjacobuc@gmail.com
    url: rjacobucci.com
title:
  formatted: "\\pkg{regsem}: Regularized Structural Equation Modeling"
  # If you use tex in the formatted title, also supply version without
  plain:     "regsem: Regularized Structural Equation Modeling"
  # For running headers, if needed
  short:     "\\pkg{regsem}"
abstract: >
  The \pkg{regsem} package in \proglang{R}, an implementation of Regularized Structural Equation Modeling [@jacobucci2016regularized], was recently developed with the goal incorporating various forms of penalized likelihood estimation with a broad array of structural equations models. The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator (\textit{lasso}; [@Tibshirani1996], along with sparser extensions. The paper details both the algorithmic details and an overview of the use of \pkg{regsem} through both a factor analysis and latent growth curve models. 
keywords:
  # at least one keyword must be supplied
  formatted: [regularization, structural equation modeling, latent variables, "\\proglang{R}"]
  plain:     [regularization, structural equation modeling, latent variables, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{float}
  \usepackage{algorithm}
  \usepackage[noend]{algpseudocode}
  \usepackage[subnum]{cases}

output: rticles::jss_article
bibliography: jss_regsem.bib
---
\setlength\parindent{24pt}
\setlength{\parskip}{0.5em}

# Introduction

The desire for simplicity in model structure comes by many names, including simple structure [@thurstone1937], variable complexity [@browne2001], parsimony [@raykov1999desirability; @marsh1996assessing], "sparse loadings" in the context of principal components analysis [@zou2006sparse], and lastly, "sparsistency", denoting that all parameters in a sparse model that are zero are correctly estimated as zero with probability tending to one [@lam2009sparsistency]. The goal is accurately and efficiently estimate a model that is parsimonious in allowing users to easily interpret the model's representation of reality. In Figure 1, this would entail testing whether the cross-loadings are necessary to the fit of the model, or whether they can be pared away without an meaningful increase in bias.

In the context of latent variables, reducing the complexity of models can come in many forms: selecting among multiple predictors of a latent variable, simplifying factor structure by removing cross-loadings, determining whether the addition of nonlinear terms are necessary in longitudinal models, and many others. As a simple running example, Figure 1 depicts a linear latent growth curve model with four time points and ten predictors for a simulated dataset.

```{r, eval=FALSE, include=FALSE}
library(lavaan)
library(semPlot)
library(semTools)

sim.mod <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10
s ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10"

dat <- simulateData(sim.mod,model.type="growth",sample.nobs=80,seed=1234)

mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"

out <- growth(mod1,dat,fixed.x=T)
summary(out)
fitmeasures(out)

semPaths(out, whatLabels="est",intercepts=FALSE,residuals=TRUE,exoCov=FALSE)
```

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{figs/growth_fig}
	\caption{Growth curve model with 10 predictors of both the intercept and slope}
\end{figure}

As an example, a researcher may want to test this model, but may only have a relatively small sample size (e.g. 80). However, there are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio as far below even the most liberal recommendations [e.g. 10:1 parameters to sample size; @kline2015principles]. In lieu of finding additional respondents, reducing the number of parameters estimated is one effective strategy. Specifically, the 20 estimated regressions from \textit{c1-c10} could be reduced to a number that makes the number of parameters estimated to sample size ratio more reasonable.

# Regularization

Although a whole host of methods exist to perform variable selection, the use of regularization has seen a wide array of application in the context of regression, and more recently, in areas such as graphical modeling, as well as a host of others. The two most common procedures for regularization in regression are the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996]; however, there are various alternative forms that can be seen as subsets or generalizations of these two procedures. Given an outcome vector \textit{y} and predictor matrix $X \in {R}^{n \times p}$ , the ridge estimates are defined as

$$\tag{1}
\hat{\beta}^{ridge}= argmin \Big\{ \sum_{i=1}^{N} (y_{i} = \beta_{0} - \sum_{j=1}^{p}x_{ij} \beta_{j})^{2}  + \lambda \sum_{j=1}^{p} \beta_{j}^{2}\Big\},
$$
\noindent
where $\beta_{0}$ is the intercept, $\beta_{j}$ is the coefficient for $x_{j}$, and $\lambda$ is the penalty that controls the amount of shrinkage.  Note that when $\lambda = 0$, equation 3 reduces to ordinary least squares regression. As $\lambda$ is increased, the $\beta$ parameters are shrunken towards zero. The lasso estimates are defined as

$$\tag{2}
\hat{\beta}^{lasso}= argmin \Big\{ \sum_{i=1}^{N} (y_{i} = \beta_{0} - \sum_{j=1}^{p}x_{ij} \beta_{j})^{2}  + \lambda \sum_{j=1}^{p}|\beta_{j}|\Big\}.
$$

\noindent
In lasso regression, the $l_{1}$-norm is used, instead of $l_{2}$-norm as in ridge, which also shrinks the $\beta$ parameters, but additionally drives the parameters all the way to zero, thus performing a form of subset selection.

In the context of our example depicted in Figure 1, to use lasso regression to select among the covariates, the growth model would need to be reduced to two factor scores, which neglects both the relationship between both the slope and intercept, reducing both to independent factor scores. Particularly in models with a greater number of latent variables, this becomes increasing problematic. A method that keeps the model structure, while allowing for a penalized estimation of specific parameters is regularized structural equation modeling [RegSEM; @jacobucci2016regularized]. RegSEM adds a penalty function to the traditional maximum likelihood cost function for SEMs. The maximum likelihood cost function for SEMs can be written as

$$\tag{3}
F_{ML}=log(\left|\Sigma\right|)+tr(C*\Sigma^{-1})-log(\left|C\right|)- p.
$$

\noindent
where $\Sigma$ is the model implied covariance matrix, $C$ is the observed covariance matrix, and $p$ is the number of estimated parameters. RegSem builds in an additional element to penalize certain model parameters yielding

$$\tag{4}
F_{regsem} = F_{ML} + \lambda P(\cdot)
$$

\noindent
where $\lambda$ is the regularization parameter and takes on a value between zero and infinity. When $\lambda$ is zero, MLE is performed, and when $\lambda$ is infinity, all penalized parameters are shrunk to zero. $P(\cdot)$ is a general function for summing the values of one or more of the model's parameter matrices. The two common forms of $P(\cdot)$ include both the Lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and Ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.

In our example, the twenty regression parameters from the covariates to both the intercept and slope would be penalized. Using lasso penalties, the absolute value of these twenty parameters would be summed and after being multiplied by the penalty $\lambda$, added to equation 4, resulting in:

$$\tag{5}
F_{lasso} = F_{ML} + \lambda * \left\| 	\begin{matrix}	
c1 \xrightarrow[]{} i\\
c2\xrightarrow[]{}i\\
\vdots \\
c10\xrightarrow[]{}i\\
c1\xrightarrow[]{}s\\
\vdots \\
c10\xrightarrow[]{}s\\
\end{matrix}  \right\|_{1}
$$

Although the fit of the model is easily calculated given a set of parameter estimates, traditional optimization procedures for SEM cannot be used given the non-differentiable nature of lasso penalties, and as detailed later, extensions.

## Optimization

One method that has become popular for optimizing penalized likelihood method is that of proximal gradient descent [e.g. p. 104 in @hastie2015statistical]. In comparison to one-step procedures common in SEM optimization, that only involve a method for calculating the step size and the direction (typically using the gradient and an approximation of the Hessian), proximal gradient descent can be formulated as a two-step procedure. With a stepsize of $\alpha^{t}$ and parameters $\theta^{t}$ at iteration \textit{t}:

\begin{enumerate}
	\item First, take a gradient step size $z = \theta^{t} - \alpha^{t} \nabla g(\theta^{t})$.
	\item Second, perform elementwise soft-thresholding $\theta^{t+1} = S_{\alpha^{t} \lambda}(z)$.
\end{enumerate}

where $S_{\alpha \lambda}(z)$ is the soft-thresholding operator [@donoho1995noising] used to overcome non-differentiability of the lasso penalty at the origin: 
\begin{equation}
S_{\alpha \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-\alpha \lambda)_{+}
\end{equation}
where $(x)_{+}$ is shorthand for max(x,0) and $\alpha$ is the step size. Henceforth, $\lambda$ is assumed to encompass both the penalty and the step size $s^{t}$. This procedure is only used to updated parameters that are subject to penalty. Non-penalized parameters are updated only using step 1 from above.

In contrast to only updating one parameter at a time in a coordinate-wise fashion, for RegSEM the optimization steps can be divided by both the \textit{A} and \textit{S} matrices. This block-wise gradient descent manifests itself as:

\noindent\begin{minipage}{\textwidth}
	%	\renewcommand\footnoterule{}    
	\begin{algorithm}[H]
		\begin{algorithmic}[1]
			%	\Procedure{RegSEM Block Coordinate Descent for Lasso}{}
			%	\footnotetext{Note: $A(pen)$ refers only to the penalized parameters, $vec()$ concatenates both vectors}
			\State Generate starting values for $\theta_{t}$
			\State Calculate initial fit $F_{t}$
			\State Set step size $\alpha$. .5 works well at this time.
			\State Set tolerance (tol). e.g. 1e-6
			\While {$|F_{t} - F_{t+1}| > tol$}
			\State Calculate gradient for A:$ \nabla (A) =:  \frac{\partial A}{\partial \theta_{t}}$
			\State $ \theta_{t+1^{*},A} =: \theta_{t,A} - \alpha \nabla(A)$
			\State  Update penalized parameters: $\theta_{t+1^{*},A(pen)} =: S_{\alpha \lambda}(\theta_{t+1^{*},A(pen)})$
			\State Calculate gradient for S:$ \nabla (S) =:  \frac{\partial S}{\partial \theta_{t+1^{*}}}$ 
			\State Update S parameters: $ \theta_{t+1^{*},S} =: \theta_{t,S} - \alpha \nabla(S)$
			\State $\theta_{t+1} =: \theta_{t+1^{*}}$ %vec(\theta_{t+1^{*},A},\theta_{t+1^{*},S})$
			\State Update $S_{t+1}, A_{t+1}$
			\State $ \Sigma_{t+1} = F(I-A_{t+1})^{-1}S_{t+1}(I-A_{t+1})^{-T}F^{T}$
			\State $ F_{t+1} = F_{ML}(\Sigma_{t+1},C) + \lambda \| A_{t+1}(pen) \|$
			\EndWhile
			%	\EndProcedure
		\end{algorithmic}
		\caption{RegSEM Block Coordinate Descent}
		\label{alg:seq}
	\end{algorithm}
\end{minipage}
\noindent
where step 13 is the calculation of the implied covariance matrix using RAM matrices and step 14 calculates the fit of the model with penalizing parameters in the \textit{A} matrix. Note that parameters from the \textit{S} matrix can also be penalized, however, this is much less common. This algorithm can be described as first order proximal block coordinate descent. For some SEM models, using block updates has been found to work better than standard gradient descent with the same soft thresholding of penalized parameters.

# Types of Penalties

Outside of both ridge and lasso penalties, a whole host of additional forms of regularization exist.

## Elastic Net

Most notably, the elastic net [@zou2005regularization] encompasses both the ridge and lasso, reaching a compromise between both through the addition of an additional parameter $\alpha$.

$$
P_{enet}(\theta_{j}) = 0.5(1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{2}
$$

with a soft-thresholding update of 
$$
S(\theta_{j})= 
\begin{cases}
0,&  |\theta_{j}| < \alpha\lambda\\
\frac{sgn(\theta_{j})(|\theta_{j}|-\alpha\lambda)}{1+(1-\alpha)\lambda},              & |\theta_{j}|\geq\alpha\lambda
\end{cases}
$$

\noindent
When $\alpha$ is zero, ridge is performed, and conversely when $\alpha$ is 1, lasso regularization is performed. This method harnesses the benefits of both methods, particularly when variable selection is warranted (lasso), but there may be collinearity between the variables (ridge).

## Adaptive Lasso

In using lasso penalties, difficulties emerge when the scale of variables differ dramatically. By only using one value of $\lambda$, this can add appreciable bias to the resulting estimates [e.g. @fan2001variable]. One method proposed for overcoming this limitation is the adaptive lasso [@zou2006adaptive]. Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (maximum likelihood estimate in SEM). This manifests itself as:
$$
F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
$$
\noindent
with, following the same form for the lasso, the soft-thresholding update is:
[\\]: ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf
$$
S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
$$
\noindent
In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant, parameters. Note that one limitation of this approach for SEM models is that the model needs to be estimable with maximum likelihood. Particularly for models with large numbers of variables, in relation to sample size, this may not be possible.

## Smoothly Clipped Absolute Deviation Penalty
[\\]: High dimensional statistics p. 32

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{figs/penalties}
	\caption{Comparison of types of penalties with $\lambda=0.5$}
\end{figure}

Two additional penalties that overcome some of the deficiencies of the lasso, producing sparser solutions, include the smoothly clipped absolute deviation penalty [SCAD; @fan2001variable] and the minimax concave penalty [MCP; @zhang2010nearly]. In comparison to the lasso, both the SCAD and MCP have much steeper penalties for smaller parameters, as is evident in Figure **.

The SCAD takes the form of:

$$
pen_{\lambda,\gamma}(\theta_{j}) = \lambda \big\{I(\theta_{j}\leq\lambda) + \frac{(\gamma \lambda-0)_{+}}{(\gamma-1)\lambda}I(\theta_{j}>\lambda)\big\}
$$

\noindent
with a soft-thresholding update of
$$
S(\theta_{j})= 
\begin{cases}
S(\theta_{j},\lambda),&  |\theta_{j}| \geq 2\lambda\\
\frac{\gamma-1}{\gamma-2}S(\theta_{j},\frac{\lambda\gamma}{\gamma-1}),              & 2\lambda < |\theta_{j}|\leq\alpha\lambda\\
\theta_{j} & |\theta_{j}| > \lambda \gamma
\end{cases}
$$

\noindent
As the the penalty in equation 11 is non-convex (as is the MCP), this makes computation more difficult. However, in the context of SEM this can be seen as less problematic, as equation 3 is also non-convex.

## Minimax Concave Penalty

@zhang2010nearly proposed the minimax concave penalty:

$$
pen_{\lambda,\gamma}(\theta_{j}) = \lambda\bigg(|\theta_{j}|-\frac{\theta_{j}^{2}}{2\lambda\gamma}\bigg)I(|\theta_{j}|<\lambda\gamma) +\frac{\lambda^{2}\gamma}{2}I(|\theta_{j}|\geq \lambda\gamma)
$$

\noindent
with a soft-thresholding update of
$$
S(\theta_{j})= 
\begin{cases}
\frac{\gamma}{\gamma-1}S(\theta_{j},\lambda),&  |\theta_{j}| \leq \lambda\gamma\\
\theta_{j} & |\theta_{j}| > \lambda \gamma
\end{cases}
$$

\noindent
As seen in Figure **, this results in similar amount of shrinkage for smaller estimates in comparison to the SCAD, however, less for larger estimates.

# Implementation

RegSEM is implemented as the \pkg{regsem} package in the \proglang{R} statistical environment. To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984, @mcardle2005] notation to derive an implied covariance matrix. The parameters of each SEM are translated into three matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths; e.g. factor loadings or regressions), and the \textit{symmetric} (\textit{S}; undirected paths; e.g. covariances or variances). See @jacobucci2016regularized for more detail on RAM notation.

Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package [@rosseel2012] for structural equation models. \pkg{lavaan} is a general SEM software program that can fit a wide array of models with various estimation methods. To use \pkg{regsem}, the user has to first fit the model in \pkg{lavaan}. As an example, below is the code for a one factor model fit in lavaan with the Holzinger-Swineford [@holzinger1939study] dataset.

```{r,message=FALSE}
library(lavaan)
mod <- "
f1 = ~ NA*x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9
f1~~1*f1
"
out <- cfa(mod,HolzingerSwineford1939)
```

After a model is run in lavaan, using \code{lavaan()} or any of the wrapper functions for fitting a model (i.e. \code{sem()}, \code{cfa()}, or \code{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem}. The \code{regsem()} function runs a model with one penalty value, whereas \code{multi_optim()} does the same but allows for the use of random starting values. However, the main function is \code{cv_regsem()} as this not only runs the model, but runs it across a vector of varying penalty values. For instance in the above one-factor model, each of the factor loadings can be tested with lasso penalties to determine whether each indicator is a necessary component of the latent factor.

```{r, message=FALSE, warning=FALSE,results='hide'}
library(regsem)
extractMatrices(out)["A"]
out.reg <- cv_regsem(out, type="lasso", 
                    pars_pen=c(1:9),n.lambda=15,jump=.05)
```

In this, the function \code{extractMatrices()} allows the user to examine at how the lavaan model is translated into RAM matrices. Further, by looking at the \textit{A} matrix, the parameter numbers corresponding to the factor loadings of interest for regularization can be identified. For this model, the factor loadings represent parameter numbers one through nine, of which we pass directly to the \code{pars_pen} argument of the \code{cv_regsem()} function (if \code{pars_pen=NULL} then all directed effects, outside of intercepts, are penalized). Additionally, we pass the arguments of how many values of penalty we want to test (\code{n.lambda=15}), how much the penalty should increase for each model (\code{jump=.05}), and finally that lasso estimation is used (\code{type="lasso"}).

The \code{out.reg} object contains two components, \code{out.reg[[1]]} has the parameter estimates for each of the 15 models, while \code{out.reg[[2]]} has the fit of each model. For the code above, using the \pkg{xtable} package to turn the output from  \code{out.reg[[2]]} into a table

```{r}
round(out.reg[[2]],3)
```

In this, the user can examine the penalty (lambda), whether the model converged ("conv"), with values of 0 indicating convergence, and the fit of each model. By default, two fit indices are output, both the root mean square error of approximation [RMSEA; @steiger1980], and the Bayesian information criteria [BIC; @schwarz1978estimating]. Both the RMSEA and BIC take into account the degrees of freedom of the model, an important point for model selection in the presence of lasso penalties (and other penalties that set parameters to zero). This concurs with work done on degrees of freedom for lasso regression, as @Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression. As the penalty increases, select parameter are set to zero, thus the degrees of freedom increases, which for fit indices that include the degrees of freedom in the calculation, means that although the likelihood of the model may only get worse (increase), both the RMSEA and BIC can improve (decrease) due to the impact of increased degrees of freedom.

Instead of examining the \code{out.reg[[1]]} output matrix of parameter estimates, it is easiest to plot the trajectory of each of the penalized parameters. This is accomplished with \code{plot_cv(out.reg,pars=1:9)}, resulting in:

```{r}
plot_cv(out.reg,pars=1:9)
```

# Comparison

To compare the different types of penalties in \pkg{regsem}, we return to the the initial example of the latent growth curve model. Using the same simulated data (see Appendix), the model can be run in \pkg{lavaan} as

```{r,eval=FALSE}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
```

To compare different types of penalties in \pkg{regsem}, it requires a different specification of the \code{type} argument. The options currently include maximum likelihood (\code{"none"}), ridge (\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso (\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}), and MCP (\code{"mcp"}). For the elastic net, there is an additional hyperparameter, $\alpha$ that controls the tradeoff between ridge and lasso penalties. This is specified as \code{alpha=} , which has a default of 0.5. Additionally, both the SCAD and MCP have the additional hyper parameter of $\gamma$, which is specified as \code{gamma=} and defaults to 3.7 per @fan2001variable.

For the purposes of comparison, each of the 20 covariate regressions were penalized using the lasso, adaptive lasso, SCAD, and MCP, and compared to the maximum likelihood estimates (see Appendix for code). In this model, the data were simulated to have two large effects (both \textit{c1} parameters), two small effects (both \textit{c2} parameters) and sixteen true zero effects (\textit{c3-c10} parameters). Note that the covariates were simulated to have zero covariance among each variable. If there was substantial collinearity among covariates, the elastic net would be more appropriate to simultaneously select predictors while also accounting for the collinearity. The parameter estimates corresponding the the best fit of the BIC are displayed in Table *

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(lavaan)
library(semPlot)
library(semTools)

#HS <- HolzingerSwineford1939

#mod <- "
#f1 =~ x1 + x2 + x3 + x4 + x5 + x6
#f2 =~ x7 + x8 + x9 + x4 + x5 + x6
#"
#out <- cfa(mod,HS)
#semPaths(out)

sim.mod <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10
s ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10"

dat <- simulateData(sim.mod,model.type="growth",sample.nobs=80,seed=1234)

mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"

out <- growth(mod1,dat,fixed.x=T)
summary(out)
fitmeasures(out)

semPaths(out, whatLabels="est",intercepts=FALSE,residuals=TRUE,exoCov=FALSE)

library(regsem);library(xtable)
best.pars <- matrix(NA,21,5)
extractMatrices(out)$A
reg.out <- cv_regsem(out,pars_pen=c(1:20),type="lasso",n.lambda=40,mult.start=FALSE,jump=.01)
reg.out

# ML
best.pars[21,1] <- reg.out[[2]][1,"BIC"]

best.pars[1:20,1] <- reg.out[[1]][1,1:20]

best.pars[21,2] <- min(reg.out[[2]][,"BIC"])
loc1 <- which(reg.out[[2]][,"BIC"] ==min(reg.out[[2]][,"BIC"]))
best.pars[1:20,2] <- reg.out[[1]][loc1,1:20]

reg.out2 <- cv_regsem(out,pars_pen=c(1:20),type="alasso",n.lambda=40,mult.start=FALSE,jump=.003)
reg.out2

best.pars[21,3] <- min(reg.out2[[2]][,"BIC"])
loc2 <- which(reg.out2[[2]][,"BIC"] ==min(reg.out2[[2]][,"BIC"]))
best.pars[1:20,3] <- reg.out2[[1]][loc2,1:20]

reg.out3 <- cv_regsem(out,pars_pen=c(1:20),type="scad",n.lambda=40,mult.start=FALSE,jump=.05)
reg.out3

best.pars[21,4] <- min(reg.out3[[2]][,"BIC"])
loc3 <- which(reg.out3[[2]][,"BIC"] ==min(reg.out3[[2]][,"BIC"]))
best.pars[1:20,4] <- reg.out3[[1]][loc3,1:20]

reg.out4 <- cv_regsem(out,pars_pen=c(1:20),type="mcp",n.lambda=40,mult.start=FALSE,jump=.2)
reg.out4

best.pars[21,5] <- min(reg.out4[[2]][,"BIC"])
loc4 <- which(reg.out4[[2]][,"BIC"] ==min(reg.out4[[2]][,"BIC"]))
best.pars[1:20,5] <- reg.out4[[1]][loc4,1:20]

colnames(best.pars) <- c("ML","lasso","alasso","SCAD","MCP")
rownames(best.pars) <- c("c1 -> i","c2 -> i","c3 -> i","c4 -> i","c5 -> i","c6 -> i","c7 -> i","c8 -> i","c9 -> i","c10 -> i",
                         "c1 -> s","c2 -> s","c3 -> s","c4 -> s","c5 -> s","c6 -> s","c7 -> s","c8 -> s","c9 -> s","c10 -> s","BIC")
xtable(best.pars)
```

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrr}
		\hline
		& ML & lasso & alasso & SCAD & MCP \\ 
		\hline
		c1 -$>$ i & 0.17 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c2 -$>$ i & -0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c3 -$>$ i & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c4 -$>$ i & 0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c5 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c6 -$>$ i & -0.52* & 0.00 & 0.00 & 0.00 & -0.24 \\ 
		c7 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c8 -$>$ i & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c9 -$>$ i & 0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c10 -$>$ i & -0.12 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c1 -$>$ s & 1.47* & 1.44 & 1.60 & 1.62 & 1.61 \\ 
		c2 -$>$ s & 0.32* & 0.20 & 0.29 & 0.35 & 0.34 \\ 
		c3 -$>$ s & 0.21 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
		c4 -$>$ s & -0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c5 -$>$ s & -0.25 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c6 -$>$ s & 0.37* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c7 -$>$ s & -0.21 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c8 -$>$ s & 0.27* & 0.04 & 0.00 & 0.00 & 0.00 \\ 
		c9 -$>$ s & -0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c10 -$>$ s & 0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		BIC & 3530.61 & 3484.27 & 3475.40 & 3474.85 & 3476.96 \\ 
		\hline
	\end{tabular}
\caption{Parameter estimates for the final models across five estimation methods. Note that * represent significant parameters at p < .05 for maximum likelihood estimation.}
\end{table}

While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect. The lasso and MCP mistakenly identified one false effect each. As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.

To compare the performance of each penalization method further, particularly in the presence of small number of parameters to sample size ratios, a small scale simulation study was conducted. The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size. Each run was replicated 200 times, with the corresponding code in the Appendix. The results are displayed in Table *

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrrrr}
		\hline
		& N & ML & lasso & alasso & SCAD & MCP \\ 
		\hline
		 & 80.00 & 0.09 & 0.05 & \textbf{0.04} & 0.05 & 0.05 \\ 
		False Positives & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.04 \\ 
		 & 1000.00 & 0.05 & 0.05 & \textbf{0.01} & \textbf{0.01} & 0.19 \\ 
		 & 80.00 & 0.45 & \textbf{0.41} & 0.43 & 0.45 & 0.54 \\ 
		False Negatives & 200.00 & 0.30 & \textbf{0.24} & 0.29 & 0.29 & 0.45 \\ 
		 & 1000.00 & 0.10 & \textbf{0.09} & 0.17 & 0.19 & 0.24 \\ 
		\hline
	\end{tabular}
	\caption{Results from the simulation using the model in Figure 1. Each condition was replicated 200 times. False positives represent concluding that the simulated regressions of zero were concluded as nonzero. False negatives are concluding that either the simulated regression values of 1 or 0.2 are in fact zero. Bolded values represent the smallest error per condition.}
\end{table}

# Discussion

## Future Directions

## Limitation

## Conclusion

### 2017-03-04 draft1.tex
formatted with rmd

--- 2017-03-04 draft1.Rmd
@@
----
-author:
-  - name: Ross Jacobucci
-    affiliation: University of Notre Dame
-    address: >
-      First line
-      Second line
-    email: rcjacobuc@gmail.com
-    url: rjacobucci.com
-title:
-  formatted: "\\pkg{regsem}: Regularized Structural Equation Modeling"
-  # If you use tex in the formatted title, also supply version without
-  plain:     "regsem: Regularized Structural Equation Modeling"
-  # For running headers, if needed
-  short:     "\\pkg{regsem}"
-abstract: >
-  The \pkg{regsem} package in \proglang{R}, an implementation of Regularized Structural Equation Modeling [@jacobucci2016regularized], was recently developed with the goal incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
-The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator (\textit{lasso}; [@Tibshirani1996], along with sparser extensions.
-The paper details both the algorithmic details and an overview of the use of \pkg{regsem} through both a factor analysis and latent growth curve models.
-keywords:
-  # at least one keyword must be supplied
-  formatted: [regularization, structural equation modeling, latent variables, "\\proglang{R}"]
-  plain:     [regularization, structural equation modeling, latent variables, R]
-preamble: >
-  \usepackage{amsmath}
-  \usepackage{float}
-  \usepackage{algorithm}
-  \usepackage[noend]{algpseudocode}
-  \usepackage[subnum]{cases}
+\documentclass[article]{jss}
+\usepackage[utf8]{inputenc}
 
-output: rticles::jss_article
-bibliography: jss_regsem.bib
----
-\setlength\parindent{24pt}
-\setlength{\parskip}{0.5em}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-# Introduction
+\author{
+Ross Jacobucci\\University of Notre Dame
+}
+\title{\pkg{regsem}: Regularized Structural Equation Modeling}
+\Keywords{regularization, structural equation modeling, latent variables, \proglang{R}}
 
-The desire for simplicity in model structure comes by many names, including simple structure [@thurstone1937], variable complexity [@browne2001], parsimony [@raykov1999desirability; @marsh1996assessing], "sparse loadings" in the context of principal components analysis [@zou2006sparse], and lastly, "sparsistency", denoting that all parameters in a sparse model that are zero are correctly estimated as zero with probability tending to one [@lam2009sparsistency].
-The goal is accurately and efficiently estimate a model that is parsimonious in allowing users to easily interpret the model's representation of reality.
-In Figure 1, this would entail testing whether the cross-loadings are necessary to the fit of the model, or whether they can be pared away without an meaningful increase in bias.
+\Abstract{
+The \pkg{regsem} package in \proglang{R}, an implementation of
+Regularized Structural Equation Modeling (Jacobucci, Grimm, and McArdle
+2016), was recently developed with the goal incorporating various forms
+of penalized likelihood estimation with a broad array of structural
+equations models. The forms of regularization include both the
+\textit{ridge} (Hoerl and Kennard 1970) and the least absolute shrinkage
+and selection operator (\textit{lasso}; (Tibshirani 1996), along with
+sparser extensions. The paper details both the algorithmic details and
+an overview of the use of \pkg{regsem} through both a factor analysis
+and latent growth curve models.
+}
 
-In the context of latent variables, reducing the complexity of models can come in many forms: selecting among multiple predictors of a latent variable, simplifying factor structure by removing cross-loadings, determining whether the addition of nonlinear terms are necessary in longitudinal models, and many others.
-As a simple running example, Figure 1 depicts a linear latent growth curve model with four time points and ten predictors for a simulated dataset.
+\Plainauthor{Ross Jacobucci}
+\Plaintitle{regsem: Regularized Structural Equation Modeling}
+\Shorttitle{\pkg{regsem}}
+\Plainkeywords{regularization, structural equation modeling, latent variables, R}
 
-```{r, eval=FALSE, include=FALSE}
-library(lavaan)
-library(semPlot)
-library(semTools)
+%% publication information
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+\Submitdate{}
+%% \Acceptdate{2012-06-04}
 
-sim.mod <- "
-i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
-i ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10
-s ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10"
+\Address{
+    Ross Jacobucci\\
+  University of Notre Dame\\
+  First line Second line\\
+  E-mail: \href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}\\
+  URL: rjacobucci.com\\~\\
+  }
 
-dat <- simulateData(sim.mod,model.type="growth",sample.nobs=80,seed=1234)
+\usepackage{amsmath} \usepackage{float} \usepackage{algorithm}
+\usepackage[noend]{algpseudocode} \usepackage[subnum]{cases}
 
-mod1 <- "
-i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ x1 + 1*x2 + 2*x3 + 3*x4
-i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
-s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
-"
+\begin{document}
 
-out <- growth(mod1,dat,fixed.x=T)
-summary(out)
-fitmeasures(out)
+\setlength\parindent{24pt} \setlength{\parskip}{0.5em}
 
-semPaths(out, whatLabels="est",intercepts=FALSE,residuals=TRUE,exoCov=FALSE)
-```
+\section{Introduction}\label{introduction}
+
+The desire for simplicity in model structure comes by many names,
+including simple structure (Thurstone 1935), variable complexity (Browne
+2001), parsimony (Raykov and Marcoulides 1999; Marsh and Hau 1996),
+``sparse loadings'' in the context of principal components analysis
+(Zou, Hastie, and Tibshirani 2006), and lastly, ``sparsistency'',
+denoting that all parameters in a sparse model that are zero are
+correctly estimated as zero with probability tending to one (Lam and Fan
+2009). The goal is accurately and efficiently estimate a model that is
+parsimonious in allowing users to easily interpret the model's
+representation of reality. In Figure 1, this would entail testing
+whether the cross-loadings are necessary to the fit of the model, or
+whether they can be pared away without an meaningful increase in bias.
+
+In the context of latent variables, reducing the complexity of models
+can come in many forms: selecting among multiple predictors of a latent
+variable, simplifying factor structure by removing cross-loadings,
+determining whether the addition of nonlinear terms are necessary in
+longitudinal models, and many others. As a simple running example,
+Figure 1 depicts a linear latent growth curve model with four time
+points and ten predictors for a simulated dataset.
 
@@
 
-As an example, a researcher may want to test this model, but may only have a relatively small sample size (e.g.
-80).
-However, there are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio as far below even the most liberal recommendations [e.g.
-10:1 parameters to sample size; @kline2015principles].
-In lieu of finding additional respondents, reducing the number of parameters estimated is one effective strategy.
-Specifically, the 20 estimated regressions from \textit{c1-c10} could be reduced to a number that makes the number of parameters estimated to sample size ratio more reasonable.
+As an example, a researcher may want to test this model, but may only
+have a relatively small sample size (e.g.~80). However, there are 29
+estimated parameters in this model, resulting in a estimated parameter
+to sample size ratio as far below even the most liberal recommendations
+(e.g.~10:1 parameters to sample size; Kline 2015). In lieu of finding
+additional respondents, reducing the number of parameters estimated is
+one effective strategy. Specifically, the 20 estimated regressions from
+\textit{c1-c10} could be reduced to a number that makes the number of
+parameters estimated to sample size ratio more reasonable.
 
-# Regularization
+\section{Regularization}\label{regularization}
 
-Although a whole host of methods exist to perform variable selection, the use of regularization has seen a wide array of application in the context of regression, and more recently, in areas such as graphical modeling, as well as a host of others.
-The two most common procedures for regularization in regression are the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996]; however, there are various alternative forms that can be seen as subsets or generalizations of these two procedures.
-Given an outcome vector \textit{y} and predictor matrix $X \in {R}^{n \times p}$ , the ridge estimates are defined as
+Although a whole host of methods exist to perform variable selection,
+the use of regularization has seen a wide array of application in the
+context of regression, and more recently, in areas such as graphical
+modeling, as well as a host of others. The two most common procedures
+for regularization in regression are the \textit{ridge} (Hoerl and
+Kennard 1970) and the least absolute shrinkage and selection operator
+(\textit{lasso}; Tibshirani 1996); however, there are various
+alternative forms that can be seen as subsets or generalizations of
+these two procedures. Given an outcome vector \textit{y} and predictor
+matrix \(X \in {R}^{n \times p}\) , the ridge estimates are defined as
 
-$$\tag{1}
+\[\tag{1}
 \hat{\beta}^{ridge}= argmin \Big\{ \sum_{i=1}^{N} (y_{i} = \beta_{0} - \sum_{j=1}^{p}x_{ij} \beta_{j})^{2}  + \lambda \sum_{j=1}^{p} \beta_{j}^{2}\Big\},
-$$
-\noindent
-where $\beta_{0}$ is the intercept, $\beta_{j}$ is the coefficient for $x_{j}$, and $\lambda$ is the penalty that controls the amount of shrinkage.
-Note that when $\lambda = 0$, equation 3 reduces to ordinary least squares regression.
-As $\lambda$ is increased, the $\beta$ parameters are shrunken towards zero.
-The lasso estimates are defined as
+\] \noindent
+where \(\beta_{0}\) is the intercept, \(\beta_{j}\) is the coefficient
+for \(x_{j}\), and \(\lambda\) is the penalty that controls the amount
+of shrinkage. Note that when \(\lambda = 0\), equation 3 reduces to
+ordinary least squares regression. As \(\lambda\) is increased, the
+\(\beta\) parameters are shrunken towards zero. The lasso estimates are
+defined as
 
-$$\tag{2}
+\[\tag{2}
 \hat{\beta}^{lasso}= argmin \Big\{ \sum_{i=1}^{N} (y_{i} = \beta_{0} - \sum_{j=1}^{p}x_{ij} \beta_{j})^{2}  + \lambda \sum_{j=1}^{p}|\beta_{j}|\Big\}.
-$$
+\]
 
 \noindent
-In lasso regression, the $l_{1}$-norm is used, instead of $l_{2}$-norm as in ridge, which also shrinks the $\beta$ parameters, but additionally drives the parameters all the way to zero, thus performing a form of subset selection.
+In lasso regression, the \(l_{1}\)-norm is used, instead of
+\(l_{2}\)-norm as in ridge, which also shrinks the \(\beta\) parameters,
+but additionally drives the parameters all the way to zero, thus
+performing a form of subset selection.
 
-In the context of our example depicted in Figure 1, to use lasso regression to select among the covariates, the growth model would need to be reduced to two factor scores, which neglects both the relationship between both the slope and intercept, reducing both to independent factor scores.
-Particularly in models with a greater number of latent variables, this becomes increasing problematic.
-A method that keeps the model structure, while allowing for a penalized estimation of specific parameters is regularized structural equation modeling [RegSEM; @jacobucci2016regularized].
-RegSEM adds a penalty function to the traditional maximum likelihood cost function for SEMs.
-The maximum likelihood cost function for SEMs can be written as
+In the context of our example depicted in Figure 1, to use lasso
+regression to select among the covariates, the growth model would need
+to be reduced to two factor scores, which neglects both the relationship
+between both the slope and intercept, reducing both to independent
+factor scores. Particularly in models with a greater number of latent
+variables, this becomes increasing problematic. A method that keeps the
+model structure, while allowing for a penalized estimation of specific
+parameters is regularized structural equation modeling (RegSEM;
+Jacobucci, Grimm, and McArdle 2016). RegSEM adds a penalty function to
+the traditional maximum likelihood cost function for SEMs. The maximum
+likelihood cost function for SEMs can be written as
 
-$$\tag{3}
+\[\tag{3}
 F_{ML}=log(\left|\Sigma\right|)+tr(C*\Sigma^{-1})-log(\left|C\right|)- p.
-$$
+\]
 
 \noindent
-where $\Sigma$ is the model implied covariance matrix, $C$ is the observed covariance matrix, and $p$ is the number of estimated parameters.
-RegSem builds in an additional element to penalize certain model parameters yielding
+where \(\Sigma\) is the model implied covariance matrix, \(C\) is the
+observed covariance matrix, and \(p\) is the number of estimated
+parameters. RegSem builds in an additional element to penalize certain
+model parameters yielding
 
-$$\tag{4}
+\[\tag{4}
 F_{regsem} = F_{ML} + \lambda P(\cdot)
-$$
+\]
 
 \noindent
-where $\lambda$ is the regularization parameter and takes on a value between zero and infinity.
-When $\lambda$ is zero, MLE is performed, and when $\lambda$ is infinity, all penalized parameters are shrunk to zero.
-$P(\cdot)$ is a general function for summing the values of one or more of the model's parameter matrices.
-The two common forms of $P(\cdot)$ include both the Lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and Ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.
+where \(\lambda\) is the regularization parameter and takes on a value
+between zero and infinity. When \(\lambda\) is zero, MLE is performed,
+and when \(\lambda\) is infinity, all penalized parameters are shrunk to
+zero. \(P(\cdot)\) is a general function for summing the values of one
+or more of the model's parameter matrices. The two common forms of
+\(P(\cdot)\) include both the Lasso (\(\| \cdot \|_{1}\)), which
+penalizes the sum of the absolute values of the parameters, and Ridge
+(\(\| \cdot \|_{2}\)), which penalizes the sum of the squared values of
+the parameters.
 
-In our example, the twenty regression parameters from the covariates to both the intercept and slope would be penalized.
-Using lasso penalties, the absolute value of these twenty parameters would be summed and after being multiplied by the penalty $\lambda$, added to equation 4, resulting in:
+In our example, the twenty regression parameters from the covariates to
+both the intercept and slope would be penalized. Using lasso penalties,
+the absolute value of these twenty parameters would be summed and after
+being multiplied by the penalty \(\lambda\), added to equation 4,
+resulting in:
 
-$$\tag{5}
+\[\tag{5}
 F_{lasso} = F_{ML} + \lambda * \left\|  \begin{matrix}  
@@
 \end{matrix}  \right\|_{1}
-$$
+\]
 
-Although the fit of the model is easily calculated given a set of parameter estimates, traditional optimization procedures for SEM cannot be used given the non-differentiable nature of lasso penalties, and as detailed later, extensions.
+Although the fit of the model is easily calculated given a set of
+parameter estimates, traditional optimization procedures for SEM cannot
+be used given the non-differentiable nature of lasso penalties, and as
+detailed later, extensions.
 
-## Optimization
+\subsection{Optimization}\label{optimization}
 
-One method that has become popular for optimizing penalized likelihood method is that of proximal gradient descent [e.g.
-p.
-104 in @hastie2015statistical].
-In comparison to one-step procedures common in SEM optimization, that only involve a method for calculating the step size and the direction (typically using the gradient and an approximation of the Hessian), proximal gradient descent can be formulated as a two-step procedure.
-With a stepsize of $\alpha^{t}$ and parameters $\theta^{t}$ at iteration \textit{t}:
+One method that has become popular for optimizing penalized likelihood
+method is that of proximal gradient descent (e.g.~p.~104 in Hastie,
+Tibshirani, and Wainwright 2015). In comparison to one-step procedures
+common in SEM optimization, that only involve a method for calculating
+the step size and the direction (typically using the gradient and an
+approximation of the Hessian), proximal gradient descent can be
+formulated as a two-step procedure. With a stepsize of \(\alpha^{t}\)
+and parameters \(\theta^{t}\) at iteration \textit{t}:
 
@@
 
-where $S_{\alpha \lambda}(z)$ is the soft-thresholding operator [@donoho1995noising] used to overcome non-differentiability of the lasso penalty at the origin: 
+where \(S_{\alpha \lambda}(z)\) is the soft-thresholding operator
+(Donoho 1995) used to overcome non-differentiability of the lasso
+penalty at the origin:
+
 \begin{equation}
@@
 \end{equation}
-where $(x)_{+}$ is shorthand for max(x,0) and $\alpha$ is the step size.
-Henceforth, $\lambda$ is assumed to encompass both the penalty and the step size $s^{t}$.
-This procedure is only used to updated parameters that are subject to penalty.
-Non-penalized parameters are updated only using step 1 from above.
 
-In contrast to only updating one parameter at a time in a coordinate-wise fashion, for RegSEM the optimization steps can be divided by both the \textit{A} and \textit{S} matrices.
-This block-wise gradient descent manifests itself as:
+where \((x)_{+}\) is shorthand for max(x,0) and \(\alpha\) is the step
+size. Henceforth, \(\lambda\) is assumed to encompass both the penalty
+and the step size \(s^{t}\). This procedure is only used to updated
+parameters that are subject to penalty. Non-penalized parameters are
+updated only using step 1 from above.
 
-\noindent\begin{minipage}{\textwidth}
+In contrast to only updating one parameter at a time in a
+coordinate-wise fashion, for RegSEM the optimization steps can be
+divided by both the \textit{A} and \textit{S} matrices. This block-wise
+gradient descent manifests itself as:
+
+\noindent
+
+\begin{minipage}{\textwidth}
     %   \renewcommand\footnoterule{}    
@@
 \end{minipage}
+
 \noindent
-where step 13 is the calculation of the implied covariance matrix using RAM matrices and step 14 calculates the fit of the model with penalizing parameters in the \textit{A} matrix.
-Note that parameters from the \textit{S} matrix can also be penalized, however, this is much less common.
-This algorithm can be described as first order proximal block coordinate descent.
-For some SEM models, using block updates has been found to work better than standard gradient descent with the same soft thresholding of penalized parameters.
+where step 13 is the calculation of the implied covariance matrix using
+RAM matrices and step 14 calculates the fit of the model with penalizing
+parameters in the \textit{A} matrix. Note that parameters from the
+\textit{S} matrix can also be penalized, however, this is much less
+common. This algorithm can be described as first order proximal block
+coordinate descent. For some SEM models, using block updates has been
+found to work better than standard gradient descent with the same soft
+thresholding of penalized parameters.
 
-# Types of Penalties
+\section{Types of Penalties}\label{types-of-penalties}
 
-Outside of both ridge and lasso penalties, a whole host of additional forms of regularization exist.
+Outside of both ridge and lasso penalties, a whole host of additional
+forms of regularization exist.
 
-## Elastic Net
+\subsection{Elastic Net}\label{elastic-net}
 
-Most notably, the elastic net [@zou2005regularization] encompasses both the ridge and lasso, reaching a compromise between both through the addition of an additional parameter $\alpha$.
+Most notably, the elastic net (Zou and Hastie 2005) encompasses both the
+ridge and lasso, reaching a compromise between both through the addition
+of an additional parameter \(\alpha\).
 
-$$
+\[
 P_{enet}(\theta_{j}) = 0.5(1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{2}
-$$
+\]
 
-with a soft-thresholding update of 
-$$
+with a soft-thresholding update of \[
 S(\theta_{j})= 
@@
 \end{cases}
-$$
+\]
 
 \noindent
-When $\alpha$ is zero, ridge is performed, and conversely when $\alpha$ is 1, lasso regularization is performed.
-This method harnesses the benefits of both methods, particularly when variable selection is warranted (lasso), but there may be collinearity between the variables (ridge).
+When \(\alpha\) is zero, ridge is performed, and conversely when
+\(\alpha\) is 1, lasso regularization is performed. This method
+harnesses the benefits of both methods, particularly when variable
+selection is warranted (lasso), but there may be collinearity between
+the variables (ridge).
 
-## Adaptive Lasso
+\subsection{Adaptive Lasso}\label{adaptive-lasso}
 
-In using lasso penalties, difficulties emerge when the scale of variables differ dramatically.
-By only using one value of $\lambda$, this can add appreciable bias to the resulting estimates [e.g.
-@fan2001variable].
-One method proposed for overcoming this limitation is the adaptive lasso [@zou2006adaptive].
-Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (maximum likelihood estimate in SEM).
-This manifests itself as:
-$$
+In using lasso penalties, difficulties emerge when the scale of
+variables differ dramatically. By only using one value of \(\lambda\),
+this can add appreciable bias to the resulting estimates (e.g. Fan and
+Li 2001). One method proposed for overcoming this limitation is the
+adaptive lasso (Zou 2006). Instead of penalizing parameters directly,
+each parameter is scaled by the un-penalized estimated (maximum
+likelihood estimate in SEM). This manifests itself as: \[
 F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
-$$
-\noindent
-with, following the same form for the lasso, the soft-thresholding update is:
-[\\]: ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf
-$$
+\] \noindent
+with, following the same form for the lasso, the soft-thresholding
+update is:
+\href{High\%20dimensional\%20statistics\%20p.\%2032}{\textbackslash{}}:
+\url{ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf}
+\[
 S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
-$$
-\noindent
-In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant, parameters.
-Note that one limitation of this approach for SEM models is that the model needs to be estimable with maximum likelihood.
-Particularly for models with large numbers of variables, in relation to sample size, this may not be possible.
+\] \noindent
+In this, larger penalties are given for non-significant (smaller)
+parameters, limiting the bias in estimating larger, significant,
+parameters. Note that one limitation of this approach for SEM models is
+that the model needs to be estimable with maximum likelihood.
+Particularly for models with large numbers of variables, in relation to
+sample size, this may not be possible.
 
-## Smoothly Clipped Absolute Deviation Penalty
-[\\]: High dimensional statistics p. 32
+\subsection{Smoothly Clipped Absolute Deviation
+Penalty}\label{smoothly-clipped-absolute-deviation-penalty}
 
@@
 
-Two additional penalties that overcome some of the deficiencies of the lasso, producing sparser solutions, include the smoothly clipped absolute deviation penalty [SCAD; @fan2001variable] and the minimax concave penalty [MCP; @zhang2010nearly].
-In comparison to the lasso, both the SCAD and MCP have much steeper penalties for smaller parameters, as is evident in Figure **.
+Two additional penalties that overcome some of the deficiencies of the
+lasso, producing sparser solutions, include the smoothly clipped
+absolute deviation penalty (SCAD; Fan and Li 2001) and the minimax
+concave penalty (MCP; Zhang 2010). In comparison to the lasso, both the
+SCAD and MCP have much steeper penalties for smaller parameters, as is
+evident in Figure **.
 
@@
 
-$$
+\[
 pen_{\lambda,\gamma}(\theta_{j}) = \lambda \big\{I(\theta_{j}\leq\lambda) + \frac{(\gamma \lambda-0)_{+}}{(\gamma-1)\lambda}I(\theta_{j}>\lambda)\big\}
-$$
+\]
 
 \noindent
-with a soft-thresholding update of
-$$
+with a soft-thresholding update of \[
 S(\theta_{j})= 
@@
 \end{cases}
-$$
+\]
 
 \noindent
-As the the penalty in equation 11 is non-convex (as is the MCP), this makes computation more difficult.
-However, in the context of SEM this can be seen as less problematic, as equation 3 is also non-convex.
+As the the penalty in equation 11 is non-convex (as is the MCP), this
+makes computation more difficult. However, in the context of SEM this
+can be seen as less problematic, as equation 3 is also non-convex.
 
-## Minimax Concave Penalty
+\subsection{Minimax Concave Penalty}\label{minimax-concave-penalty}
 
-@zhang2010nearly proposed the minimax concave penalty:
+Zhang (2010) proposed the minimax concave penalty:
 
-$$
+\[
 pen_{\lambda,\gamma}(\theta_{j}) = \lambda\bigg(|\theta_{j}|-\frac{\theta_{j}^{2}}{2\lambda\gamma}\bigg)I(|\theta_{j}|<\lambda\gamma) +\frac{\lambda^{2}\gamma}{2}I(|\theta_{j}|\geq \lambda\gamma)
-$$
+\]
 
 \noindent
-with a soft-thresholding update of
-$$
+with a soft-thresholding update of \[
 S(\theta_{j})= 
@@
 \end{cases}
-$$
+\]
 
 \noindent
-As seen in Figure **, this results in similar amount of shrinkage for smaller estimates in comparison to the SCAD, however, less for larger estimates.
+As seen in Figure **, this results in similar amount of shrinkage for
+smaller estimates in comparison to the SCAD, however, less for larger
+estimates.
 
-# Implementation
+\section{Implementation}\label{implementation}
 
-RegSEM is implemented as the \pkg{regsem} package in the \proglang{R} statistical environment.
-To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984, @mcardle2005] notation to derive an implied covariance matrix.
-The parameters of each SEM are translated into three matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths; e.g.
-factor loadings or regressions), and the \textit{symmetric} (\textit{S}; undirected paths; e.g.
-covariances or variances).
-See @jacobucci2016regularized for more detail on RAM notation.
+RegSEM is implemented as the \pkg{regsem} package in the \proglang{R}
+statistical environment. To estimate the maximum likelihood fit of the
+model, \pkg{regsem} uses \textit{Reticular Action Model} (RAM; J. J.
+McArdle and McDonald 1984, McArdle (2005)) notation to derive an implied
+covariance matrix. The parameters of each SEM are translated into three
+matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric}
+(\textit{A}; directed paths; e.g.~factor loadings or regressions), and
+the \textit{symmetric} (\textit{S}; undirected paths; e.g.~covariances
+or variances). See Jacobucci, Grimm, and McArdle (2016) for more detail
+on RAM notation.
 
-Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package [@rosseel2012] for structural equation models.
-\pkg{lavaan} is a general SEM software program that can fit a wide array of models with various estimation methods.
-To use \pkg{regsem}, the user has to first fit the model in \pkg{lavaan}.
-As an example, below is the code for a one factor model fit in lavaan with the Holzinger-Swineford [@holzinger1939study] dataset.
+Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package
+(Rosseel 2012) for structural equation models. \pkg{lavaan} is a general
+SEM software program that can fit a wide array of models with various
+estimation methods. To use \pkg{regsem}, the user has to first fit the
+model in \pkg{lavaan}. As an example, below is the code for a one factor
+model fit in lavaan with the Holzinger-Swineford (Holzinger and
+Swineford 1939) dataset.
 
-```{r,message=FALSE}
+\begin{CodeChunk}
+\begin{CodeInput}
 library(lavaan)
@@
 out <- cfa(mod,HolzingerSwineford1939)
-```
+\end{CodeInput}
+\end{CodeChunk}
 
-After a model is run in lavaan, using \code{lavaan()} or any of the wrapper functions for fitting a model (i.e.
-\code{sem()}, \code{cfa()}, or \code{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem}.
-The \code{regsem()} function runs a model with one penalty value, whereas \code{multi_optim()} does the same but allows for the use of random starting values.
-However, the main function is \code{cv_regsem()} as this not only runs the model, but runs it across a vector of varying penalty values.
-For instance in the above one-factor model, each of the factor loadings can be tested with lasso penalties to determine whether each indicator is a necessary component of the latent factor.
+After a model is run in lavaan, using \code{lavaan()} or any of the
+wrapper functions for fitting a model (i.e. \code{sem()}, \code{cfa()},
+or \code{growth()}), the object is then used by the regsem package to
+translate the model into RAM notation and run using one of three
+functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem}.
+The \code{regsem()} function runs a model with one penalty value,
+whereas \code{multi_optim()} does the same but allows for the use of
+random starting values. However, the main function is \code{cv_regsem()}
+as this not only runs the model, but runs it across a vector of varying
+penalty values. For instance in the above one-factor model, each of the
+factor loadings can be tested with lasso penalties to determine whether
+each indicator is a necessary component of the latent factor.
 
-```{r, message=FALSE, warning=FALSE,results='hide'}
+\begin{CodeChunk}
+\begin{CodeInput}
 library(regsem)
@@
                     pars_pen=c(1:9),n.lambda=15,jump=.05)
-```
+\end{CodeInput}
+\end{CodeChunk}
 
-In this, the function \code{extractMatrices()} allows the user to examine at how the lavaan model is translated into RAM matrices.
-Further, by looking at the \textit{A} matrix, the parameter numbers corresponding to the factor loadings of interest for regularization can be identified.
-For this model, the factor loadings represent parameter numbers one through nine, of which we pass directly to the \code{pars_pen} argument of the \code{cv_regsem()} function (if \code{pars_pen=NULL} then all directed effects, outside of intercepts, are penalized).
-Additionally, we pass the arguments of how many values of penalty we want to test (\code{n.lambda=15}), how much the penalty should increase for each model (\code{jump=.05}), and finally that lasso estimation is used (\code{type="lasso"}).
+In this, the function \code{extractMatrices()} allows the user to
+examine at how the lavaan model is translated into RAM matrices.
+Further, by looking at the \textit{A} matrix, the parameter numbers
+corresponding to the factor loadings of interest for regularization can
+be identified. For this model, the factor loadings represent parameter
+numbers one through nine, of which we pass directly to the
+\code{pars_pen} argument of the \code{cv_regsem()} function (if
+\code{pars_pen=NULL} then all directed effects, outside of intercepts,
+are penalized). Additionally, we pass the arguments of how many values
+of penalty we want to test (\code{n.lambda=15}), how much the penalty
+should increase for each model (\code{jump=.05}), and finally that lasso
+estimation is used (\code{type="lasso"}).
 
-The \code{out.reg} object contains two components, \code{out.reg[[1]]} has the parameter estimates for each of the 15 models, while \code{out.reg[[2]]} has the fit of each model.
-For the code above, using the \pkg{xtable} package to turn the output from  \code{out.reg[[2]]} into a table
+The \code{out.reg} object contains two components, \code{out.reg[[1]]}
+has the parameter estimates for each of the 15 models, while
+\code{out.reg[[2]]} has the fit of each model. For the code above, using
+the \pkg{xtable} package to turn the output from \code{out.reg[[2]]}
+into a table
 
-```{r}
+\begin{CodeChunk}
+\begin{CodeInput}
 round(out.reg[[2]],3)
-```
+\end{CodeInput}
+\begin{CodeOutput}
+      lambda conv rmsea      BIC
+ [1,]   0.00    0 0.188 7805.177
+ [2,]   0.05    0 0.191 7815.389
+ [3,]   0.10    0 0.199 7840.590
+ [4,]   0.15    0 0.210 7875.842
+ [5,]   0.20    0 0.203 7886.147
+ [6,]   0.25    0 0.210 7911.816
+ [7,]   0.30    0 0.214 7934.454
+ [8,]   0.35    0 0.220 7960.670
+ [9,]   0.40    0 0.227 7991.033
+[10,]   0.45    0 0.229 8009.416
+[11,]   0.50    0 0.234 8034.805
+[12,]   0.55    0 0.242 8069.487
+[13,]   0.60    0 0.286 8360.539
+[14,]   0.65    0 0.286 8360.530
+[15,]   0.70    0 0.286 8360.525
+\end{CodeOutput}
+\end{CodeChunk}
 
-In this, the user can examine the penalty (lambda), whether the model converged ("conv"), with values of 0 indicating convergence, and the fit of each model.
-By default, two fit indices are output, both the root mean square error of approximation [RMSEA; @steiger1980], and the Bayesian information criteria [BIC; @schwarz1978estimating].
-Both the RMSEA and BIC take into account the degrees of freedom of the model, an important point for model selection in the presence of lasso penalties (and other penalties that set parameters to zero).
-This concurs with work done on degrees of freedom for lasso regression, as @Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression.
-As the penalty increases, select parameter are set to zero, thus the degrees of freedom increases, which for fit indices that include the degrees of freedom in the calculation, means that although the likelihood of the model may only get worse (increase), both the RMSEA and BIC can improve (decrease) due to the impact of increased degrees of freedom.
+In this, the user can examine the penalty (lambda), whether the model
+converged (``conv''), with values of 0 indicating convergence, and the
+fit of each model. By default, two fit indices are output, both the root
+mean square error of approximation (RMSEA; Steiger and Lind 1980), and
+the Bayesian information criteria (BIC; Schwarz 1978). Both the RMSEA
+and BIC take into account the degrees of freedom of the model, an
+important point for model selection in the presence of lasso penalties
+(and other penalties that set parameters to zero). This concurs with
+work done on degrees of freedom for lasso regression, as Zou, Hastie,
+and Tibshirani (2007) proved that the number of nonzero coefficients is
+an unbiased estimate of the degrees of freedom for regression. As the
+penalty increases, select parameter are set to zero, thus the degrees of
+freedom increases, which for fit indices that include the degrees of
+freedom in the calculation, means that although the likelihood of the
+model may only get worse (increase), both the RMSEA and BIC can improve
+(decrease) due to the impact of increased degrees of freedom.
 
-Instead of examining the \code{out.reg[[1]]} output matrix of parameter estimates, it is easiest to plot the trajectory of each of the penalized parameters.
-This is accomplished with \code{plot_cv(out.reg,pars=1:9)}, resulting in:
+Instead of examining the \code{out.reg[[1]]} output matrix of parameter
+estimates, it is easiest to plot the trajectory of each of the penalized
+parameters. This is accomplished with \code{plot_cv(out.reg,pars=1:9)},
+resulting in:
 
-```{r}
+\begin{CodeChunk}
+\begin{CodeInput}
 plot_cv(out.reg,pars=1:9)
-```
+\end{CodeInput}
 
-# Comparison
+\begin{center}\includegraphics{draft1_files/figure-latex/unnamed-chunk-5-1} \end{center}
 
-To compare the different types of penalties in \pkg{regsem}, we return to the the initial example of the latent growth curve model.
-Using the same simulated data (see Appendix), the model can be run in \pkg{lavaan} as
+\end{CodeChunk}
 
-```{r,eval=FALSE}
+\section{Comparison}\label{comparison}
+
+To compare the different types of penalties in \pkg{regsem}, we return
+to the the initial example of the latent growth curve model. Using the
+same simulated data (see Appendix), the model can be run in \pkg{lavaan}
+as
+
+\begin{CodeChunk}
+\begin{CodeInput}
 mod1 <- "
@@
 lav.growth <- growth(mod1,dat,fixed.x=T)
-```
+\end{CodeInput}
+\end{CodeChunk}
 
-To compare different types of penalties in \pkg{regsem}, it requires a different specification of the \code{type} argument.
-The options currently include maximum likelihood (\code{"none"}), ridge (\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso (\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}), and MCP (\code{"mcp"}).
-For the elastic net, there is an additional hyperparameter, $\alpha$ that controls the tradeoff between ridge and lasso penalties.
-This is specified as \code{alpha=} , which has a default of 0.5.
-Additionally, both the SCAD and MCP have the additional hyper parameter of $\gamma$, which is specified as \code{gamma=} and defaults to 3.7 per @fan2001variable.
+To compare different types of penalties in \pkg{regsem}, it requires a
+different specification of the \code{type} argument. The options
+currently include maximum likelihood (\code{"none"}), ridge
+(\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso
+(\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}),
+and MCP (\code{"mcp"}). For the elastic net, there is an additional
+hyperparameter, \(\alpha\) that controls the tradeoff between ridge and
+lasso penalties. This is specified as \code{alpha=} , which has a
+default of 0.5. Additionally, both the SCAD and MCP have the additional
+hyper parameter of \(\gamma\), which is specified as \code{gamma=} and
+defaults to 3.7 per Fan and Li (2001).
 
-For the purposes of comparison, each of the 20 covariate regressions were penalized using the lasso, adaptive lasso, SCAD, and MCP, and compared to the maximum likelihood estimates (see Appendix for code).
-In this model, the data were simulated to have two large effects (both \textit{c1} parameters), two small effects (both \textit{c2} parameters) and sixteen true zero effects (\textit{c3-c10} parameters).
-Note that the covariates were simulated to have zero covariance among each variable.
-If there was substantial collinearity among covariates, the elastic net would be more appropriate to simultaneously select predictors while also accounting for the collinearity.
-The parameter estimates corresponding the the best fit of the BIC are displayed in Table *
-
-```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
-library(lavaan)
-library(semPlot)
-library(semTools)
-
-#HS <- HolzingerSwineford1939
-
-#mod <- "
-#f1 =~ x1 + x2 + x3 + x4 + x5 + x6
-#f2 =~ x7 + x8 + x9 + x4 + x5 + x6
-#"
-#out <- cfa(mod,HS)
-#semPaths(out)
-
-sim.mod <- "
-i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
-i ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10
-s ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10"
-
-dat <- simulateData(sim.mod,model.type="growth",sample.nobs=80,seed=1234)
-
-mod1 <- "
-i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ x1 + 1*x2 + 2*x3 + 3*x4
-i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
-s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
-"
-
-out <- growth(mod1,dat,fixed.x=T)
-summary(out)
-fitmeasures(out)
-
-semPaths(out, whatLabels="est",intercepts=FALSE,residuals=TRUE,exoCov=FALSE)
-
-library(regsem);library(xtable)
-best.pars <- matrix(NA,21,5)
-extractMatrices(out)$A
-reg.out <- cv_regsem(out,pars_pen=c(1:20),type="lasso",n.lambda=40,mult.start=FALSE,jump=.01)
-reg.out
-
-# ML
-best.pars[21,1] <- reg.out[[2]][1,"BIC"]
-
-best.pars[1:20,1] <- reg.out[[1]][1,1:20]
-
-best.pars[21,2] <- min(reg.out[[2]][,"BIC"])
-loc1 <- which(reg.out[[2]][,"BIC"] ==min(reg.out[[2]][,"BIC"]))
-best.pars[1:20,2] <- reg.out[[1]][loc1,1:20]
-
-reg.out2 <- cv_regsem(out,pars_pen=c(1:20),type="alasso",n.lambda=40,mult.start=FALSE,jump=.003)
-reg.out2
-
-best.pars[21,3] <- min(reg.out2[[2]][,"BIC"])
-loc2 <- which(reg.out2[[2]][,"BIC"] ==min(reg.out2[[2]][,"BIC"]))
-best.pars[1:20,3] <- reg.out2[[1]][loc2,1:20]
-
-reg.out3 <- cv_regsem(out,pars_pen=c(1:20),type="scad",n.lambda=40,mult.start=FALSE,jump=.05)
-reg.out3
-
-best.pars[21,4] <- min(reg.out3[[2]][,"BIC"])
-loc3 <- which(reg.out3[[2]][,"BIC"] ==min(reg.out3[[2]][,"BIC"]))
-best.pars[1:20,4] <- reg.out3[[1]][loc3,1:20]
-
-reg.out4 <- cv_regsem(out,pars_pen=c(1:20),type="mcp",n.lambda=40,mult.start=FALSE,jump=.2)
-reg.out4
-
-best.pars[21,5] <- min(reg.out4[[2]][,"BIC"])
-loc4 <- which(reg.out4[[2]][,"BIC"] ==min(reg.out4[[2]][,"BIC"]))
-best.pars[1:20,5] <- reg.out4[[1]][loc4,1:20]
-
-colnames(best.pars) <- c("ML","lasso","alasso","SCAD","MCP")
-rownames(best.pars) <- c("c1 -> i","c2 -> i","c3 -> i","c4 -> i","c5 -> i","c6 -> i","c7 -> i","c8 -> i","c9 -> i","c10 -> i",
-                         "c1 -> s","c2 -> s","c3 -> s","c4 -> s","c5 -> s","c6 -> s","c7 -> s","c8 -> s","c9 -> s","c10 -> s","BIC")
-xtable(best.pars)
-```
+For the purposes of comparison, each of the 20 covariate regressions
+were penalized using the lasso, adaptive lasso, SCAD, and MCP, and
+compared to the maximum likelihood estimates (see Appendix for code). In
+this model, the data were simulated to have two large effects (both
+\textit{c1} parameters), two small effects (both \textit{c2} parameters)
+and sixteen true zero effects (\textit{c3-c10} parameters). Note that
+the covariates were simulated to have zero covariance among each
+variable. If there was substantial collinearity among covariates, the
+elastic net would be more appropriate to simultaneously select
+predictors while also accounting for the collinearity. The parameter
+estimates corresponding the the best fit of the BIC are displayed in
+Table *
 
@@
 
-While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect.
-The lasso and MCP mistakenly identified one false effect each.
-As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
+While every regularization method erroneously set both simulated true
+intercept effects as zero (as in maximum likelihood, which accounts for
+these errors), both the adaptive lasso and SCAD correctly identified
+every true zero effect. The lasso and MCP mistakenly identified one
+false effect each. As expected given the small ratio between number of
+estimated parameters and sample size, maximum likelihood mistakenly
+identified 3 false effects as significant.
 
-To compare the performance of each penalization method further, particularly in the presence of small number of parameters to sample size ratios, a small scale simulation study was conducted.
-The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size.
-Each run was replicated 200 times, with the corresponding code in the Appendix.
+To compare the performance of each penalization method further,
+particularly in the presence of small number of parameters to sample
+size ratios, a small scale simulation study was conducted. The same
+model and effects was kept, but the sample size was varied to include
+80, 200, and 1000 to demonstrate how maximum likelihood estimation of
+effects improves as sample size increases, while each of the
+regularization methods performs well regardless of sample size. Each run
+was replicated 200 times, with the corresponding code in the Appendix.
 The results are displayed in Table *
@@
 
-# Discussion
+\section{Discussion}\label{discussion}
 
-## Future Directions
+\subsection{Future Directions}\label{future-directions}
 
-## Limitation
+\subsection{Limitation}\label{limitation}
 
-## Conclusion
+\subsection*{Conclusion}\label{conclusion}
+\addcontentsline{toc}{subsection}{Conclusion}
+
+\hypertarget{refs}{}
+\hypertarget{ref-browne2001}{}
+Browne, Michael W. 2001. ``An Overview of Analytic Rotation in
+Exploratory Factor Analysis.'' \emph{Multivariate Behavioral Research}
+36 (1). Taylor \& Francis: 111--50.
+
+\hypertarget{ref-donoho1995noising}{}
+Donoho, David L. 1995. ``De-Noising by Soft-Thresholding.'' \emph{IEEE
+Transactions on Information Theory} 41 (3). IEEE: 613--27.
+
+\hypertarget{ref-fan2001variable}{}
+Fan, Jianqing, and Runze Li. 2001. ``Variable Selection via Nonconcave
+Penalized Likelihood and Its Oracle Properties.'' \emph{Journal of the
+American Statistical Association} 96 (456). Taylor \& Francis: 1348--60.
+
+\hypertarget{ref-hastie2015statistical}{}
+Hastie, Trevor, Robert Tibshirani, and Martin Wainwright. 2015.
+\emph{Statistical Learning with Sparsity: The Lasso and
+Generalizations}. CRC Press.
+
+\hypertarget{ref-hoerl1970}{}
+Hoerl, Arthur E, and Robert W Kennard. 1970. ``Ridge Regression: Biased
+Estimation for Nonorthogonal Problems.'' \emph{Technometrics} 12 (1).
+Taylor \& Francis Group: 55--67.
+
+\hypertarget{ref-holzinger1939study}{}
+Holzinger, Karl John, and Frances Swineford. 1939. ``A Study in Factor
+Analysis: The Stability of a Bi-Factor Solution.'' \emph{Supplementary
+Educational Monographs}.
+
+\hypertarget{ref-jacobucci2016regularized}{}
+Jacobucci, Ross, Kevin J Grimm, and John J McArdle. 2016. ``Regularized
+Structural Equation Modeling.'' \emph{Structural Equation Modeling: A
+Multidisciplinary Journal} 23 (4). Taylor \& Francis: 555--66.
+
+\hypertarget{ref-kline2015principles}{}
+Kline, Rex B. 2015. \emph{Principles and Practice of Structural Equation
+Modeling}. Guilford publications.
+
+\hypertarget{ref-lam2009sparsistency}{}
+Lam, Clifford, and Jianqing Fan. 2009. ``Sparsistency and Rates of
+Convergence in Large Covariance Matrix Estimation.'' \emph{Annals of
+Statistics} 37 (6B). NIH Public Access: 4254.
+
+\hypertarget{ref-marsh1996assessing}{}
+Marsh, Herbert W, and Kit-Tai Hau. 1996. ``Assessing Goodness of Fit: Is
+Parsimony Always Desirable?'' \emph{The Journal of Experimental
+Education} 64 (4). Taylor \& Francis: 364--90.
+
+\hypertarget{ref-McArdle_1984}{}
+McArdle, J. Jack, and Roderick P. McDonald. 1984. ``Some Algebraic
+Properties of the Reticular Action Model for Moment Structures.''
+\emph{British Journal of Mathematical and Statistical Psychology} 37
+(2). Wiley-Blackwell: 234--51.
+
+\hypertarget{ref-mcardle2005}{}
+McArdle, John J. 2005. ``The Development of the Ram Rules for Latent
+Variable Structural Equation Modeling.'' \emph{Contemporary
+Psychometrics: A Festschrift for Roderick P. McDonald}. Erlbaum. Mahwah,
+NJ, 225--73.
+
+\hypertarget{ref-raykov1999desirability}{}
+Raykov, Tenko, and George A Marcoulides. 1999. ``On Desirability of
+Parsimony in Structural Equation Model Selection.'' \emph{Structural
+Equation Modeling: A Multidisciplinary Journal} 6 (3). Taylor \&
+Francis: 292--300.
+
+\hypertarget{ref-rosseel2012}{}
+Rosseel, Yves. 2012. ``Lavaan: An R Package for Structural Equation
+Modeling.'' \emph{Journal of Statistical Software} 48 (2): 1--36.
+
+\hypertarget{ref-schwarz1978estimating}{}
+Schwarz, Gideon. 1978. ``Estimating the Dimension of a Model.''
+\emph{The Annals of Statistics} 6 (2). Institute of Mathematical
+Statistics: 461--64.
+
+\hypertarget{ref-steiger1980}{}
+Steiger, James H, and John C Lind. 1980. ``Statistically Based Tests for
+the Number of Common Factors.'' In \emph{Annual Meeting of the
+Psychometric Society, Iowa City, Ia}. Vol. 758.
+
+\hypertarget{ref-thurstone1937}{}
+Thurstone, L. L. 1935. \emph{The Vectors of Mind}. Chicago, IL:
+University of Chicago Press.
+
+\hypertarget{ref-Tibshirani1996}{}
+Tibshirani, Robert. 1996. ``Regression Shrinkage and Selection via the
+Lasso.'' \emph{Journal of the Royal Statistical Society. Series B
+(Methodological)} 58 (1). Wiley for the Royal Statistical Society:
+267--88.
+
+\hypertarget{ref-zhang2010nearly}{}
+Zhang, Cun-Hui. 2010. ``Nearly Unbiased Variable Selection Under Minimax
+Concave Penalty.'' \emph{The Annals of Statistics} 38 (2). Institute of
+Mathematical Statistics: 894--942.
+
+\hypertarget{ref-zou2006adaptive}{}
+Zou, Hui. 2006. ``The Adaptive Lasso and Its Oracle Properties.''
+\emph{Journal of the American Statistical Association} 101 (476). Taylor
+\& Francis: 1418--29.
+
+\hypertarget{ref-zou2005regularization}{}
+Zou, Hui, and Trevor Hastie. 2005. ``Regularization and Variable
+Selection via the Elastic Net.'' \emph{Journal of the Royal Statistical
+Society: Series B (Statistical Methodology)} 67 (2). Wiley Online
+Library: 301--20.
+
+\hypertarget{ref-zou2006sparse}{}
+Zou, Hui, Trevor Hastie, and Robert Tibshirani. 2006. ``Sparse Principal
+Component Analysis.'' \emph{Journal of Computational and Graphical
+Statistics} 15 (2). Taylor \& Francis: 265--86.
+
+\hypertarget{ref-Zou2007}{}
+---------. 2007. ``On the Degrees of Freedom of the Lasso.'' \emph{The
+Annals of Statistics} 35 (5). Institute of Mathematical Statistics:
+2173--92.
+doi:\href{https://doi.org/10.1214/009053607000000127}{10.1214/009053607000000127}.
+
+\end{document}

### 2017-03-07 draft1.Rmd
add

@@
 with, following the same form for the lasso, the soft-thresholding update is:
+
 [\\]: ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf
+
 $$
@@
 
+After a final model (penalty) is chosen, user's have the option either just use the output from \code{cv_regsem()}, or the final model can be re-run with either \code{regsem()} or \code{multi_optim()} to attain additional information.
+In the model above, the best fitting penalty, according to the BIC, is $\lambda=0$.
+However, for demonstration purposes, we can choose a penalty of 0.2.
+With this, the model is re-run with \code{regsem()}
+
+```{r, message=FALSE, warning=FALSE}
+mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
+#summary(mod.out)
+```
+
+Note that the arguments used above correspond to the same arguments in \code{multi_optim()}.
+However, \code{multi_optim()} has additional optional arguments corresponding to the number or random starts to try.
+Additional fit indices can be attained through the \code{fit_indices()} function.
+
+```{r}
+fit_indices(mod.out)
+```
+\noindent
+These same fit measures can be accessed through \code{cv_regsem}, through changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
+Finally, instead of assessing these fit indices on the same sample that the models were run on, a holdout dataset could be used.
+This can be done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with \code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the holdout covariance matrix.
+
 # Comparison
@@
 i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ x1 + 1*x2 + 2*x3 + 3*x4
-i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
-s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
+s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
+i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
+s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
 "
@@
 i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
-s =~ x1 + 1*x2 + 2*x3 + 3*x4
+s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
 i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
@@
   \hline
-		c1 -$>$ i & 0.17 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c2 -$>$ i & -0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c3 -$>$ i & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c4 -$>$ i & 0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c5 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c6 -$>$ i & -0.52* & 0.00 & 0.00 & 0.00 & -0.24 \\ 
-		c7 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c8 -$>$ i & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c9 -$>$ i & 0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c10 -$>$ i & -0.12 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c1 -$>$ s & 1.47* & 1.44 & 1.60 & 1.62 & 1.61 \\ 
-		c2 -$>$ s & 0.32* & 0.20 & 0.29 & 0.35 & 0.34 \\ 
-		c3 -$>$ s & 0.21 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
-		c4 -$>$ s & -0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c5 -$>$ s & -0.25 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c6 -$>$ s & 0.37* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c7 -$>$ s & -0.21 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c8 -$>$ s & 0.27* & 0.04 & 0.00 & 0.00 & 0.00 \\ 
-		c9 -$>$ s & -0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		c10 -$>$ s & 0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-		BIC & 3530.61 & 3484.27 & 3475.40 & 3474.85 & 3476.96 \\ 
+c1 -$>$ i & 0.92* & 0.72 & 0.91 & 0.94 & 0.92 \\ 
+  c2 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c3 -$>$ i & 0.10 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c4 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c5 -$>$ i & 0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c6 -$>$ i & -0.25 & 0.00 & 0.00 & 0.00 & -0.19 \\ 
+  c7 -$>$ i & 0.11 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c8 -$>$ i & -0.13 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c9 -$>$ i & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c10 -$>$ i & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c1 -$>$ s & 1.18* & 1.09 & 1.22 & 1.24 & 1.24 \\ 
+  c2 -$>$ s & 0.29* & 0.19 & 0.28 & 0.35 & 0.35 \\ 
+  c3 -$>$ s & 0.18 & 0.09 & 0.00 & 0.00 & 0.00 \\ 
+  c4 -$>$ s & -0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c5 -$>$ s & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c6 -$>$ s & 0.25* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c7 -$>$ s & -0.18 & -0.04 & 0.00 & 0.00 & 0.00 \\ 
+  c8 -$>$ s & 0.26* & 0.10 & 0.00 & 0.00 & 0.00 \\ 
+  c9 -$>$ s & -0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c10 -$>$ s & 0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  BIC & 3465.28 & 3427.46 & 3415.05 & 3414.38 & 3417.20 \\ 
    \hline
@@
 While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect.
-The lasso and MCP mistakenly identified one false effect each.
-As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
+The lasso identified two false effects while the MCP mistakenly identified one.
+Additionally, the lasso estimation of the true effects was attentuated in comparison to the other regularization methods.
+This is in line with previous research (cite), necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed, see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
 
@@
 The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size.
-Each run was replicated 200 times, with the corresponding code in the Appendix.
+Each run was replicated 200 times.
 The results are displayed in Table *
@@
 
+This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized SEM method and the usage of the package itself.
+
 ## Future Directions
 
-## Limitation
+## Limitations
+
+With highly constrained structural equation models, achieving convergence can be particularly problematic in using \pkg{regsem}.
+For instance, with the latent change score model (cite jack), Bayesian regularization methods have less difficulty in reaching convergence across chains (cite chapter).
+With the advent of additional sparsity inducing priors, along with new forms of software such as STAN (cite stan), for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.
 

### 2017-03-07 draft1.tex
add

@@
 update is:
-\href{High\%20dimensional\%20statistics\%20p.\%2032}{\textbackslash{}}:
-\url{ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf}
+
 \[
@@
 
+After a final model (penalty) is chosen, user's have the option either
+just use the output from \code{cv_regsem()}, or the final model can be
+re-run with either \code{regsem()} or \code{multi_optim()} to attain
+additional information. In the model above, the best fitting penalty,
+according to the BIC, is \(\lambda=0\). However, for demonstration
+purposes, we can choose a penalty of 0.2. With this, the model is re-run
+with \code{regsem()}
+
+\begin{CodeChunk}
+\begin{CodeInput}
+mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
+#summary(mod.out)
+\end{CodeInput}
+\end{CodeChunk}
+
+Note that the arguments used above correspond to the same arguments in
+\code{multi_optim()}. However, \code{multi_optim()} has additional
+optional arguments corresponding to the number or random starts to try.
+Additional fit indices can be attained through the \code{fit_indices()}
+function.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+fit_indices(mod.out)
+\end{CodeInput}
+\begin{CodeOutput}
+$Data_Type
+[1] "Train"
+
+$fits
+          Fmin         varFit              p          chisq        p.chisq 
+       0.69087        0.00000        9.00000      415.90286        0.00000 
+          nfac             df           npar              N baseline.chisq 
+       1.00000       31.00000       14.00000      301.00000      918.85159 
+   baseline.df           logl            ncp          rmsea    rmsea.lower 
+      36.00000    -3903.04360        1.28301        0.20344        0.18598 
+   rmsea.upper     rmsea.pval            CFI            TLI            BIC 
+            NA        0.00000        0.56402        0.49370     7885.98674 
+           AIC           CAIC         EBIC.5        EBIC.25 
+    7834.08719     7983.11043     8051.12157     8017.06459 
+\end{CodeOutput}
+\end{CodeChunk}
+
+\noindent
+These same fit measures can be accessed through \code{cv_regsem},
+through changing the defaults with the \code{fit.ret=c("rmsea","BIC")}
+argument. Finally, instead of assessing these fit indices on the same
+sample that the models were run on, a holdout dataset could be used.
+This can be done two ways: either with
+\code{cv_regsem(...,fit.ret2="test")} or with
+\code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the
+holdout covariance matrix.
+
 \section{Comparison}\label{comparison}
@@
   \hline
-        c1 -$>$ i & 0.17 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c2 -$>$ i & -0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c3 -$>$ i & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c4 -$>$ i & 0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c5 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c6 -$>$ i & -0.52* & 0.00 & 0.00 & 0.00 & -0.24 \\ 
-        c7 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c8 -$>$ i & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c9 -$>$ i & 0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c10 -$>$ i & -0.12 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c1 -$>$ s & 1.47* & 1.44 & 1.60 & 1.62 & 1.61 \\ 
-        c2 -$>$ s & 0.32* & 0.20 & 0.29 & 0.35 & 0.34 \\ 
-        c3 -$>$ s & 0.21 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
-        c4 -$>$ s & -0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c5 -$>$ s & -0.25 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c6 -$>$ s & 0.37* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c7 -$>$ s & -0.21 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c8 -$>$ s & 0.27* & 0.04 & 0.00 & 0.00 & 0.00 \\ 
-        c9 -$>$ s & -0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        c10 -$>$ s & 0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-        BIC & 3530.61 & 3484.27 & 3475.40 & 3474.85 & 3476.96 \\ 
+c1 -$>$ i & 0.92* & 0.72 & 0.91 & 0.94 & 0.92 \\ 
+  c2 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c3 -$>$ i & 0.10 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c4 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c5 -$>$ i & 0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c6 -$>$ i & -0.25 & 0.00 & 0.00 & 0.00 & -0.19 \\ 
+  c7 -$>$ i & 0.11 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c8 -$>$ i & -0.13 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c9 -$>$ i & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c10 -$>$ i & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c1 -$>$ s & 1.18* & 1.09 & 1.22 & 1.24 & 1.24 \\ 
+  c2 -$>$ s & 0.29* & 0.19 & 0.28 & 0.35 & 0.35 \\ 
+  c3 -$>$ s & 0.18 & 0.09 & 0.00 & 0.00 & 0.00 \\ 
+  c4 -$>$ s & -0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c5 -$>$ s & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c6 -$>$ s & 0.25* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c7 -$>$ s & -0.18 & -0.04 & 0.00 & 0.00 & 0.00 \\ 
+  c8 -$>$ s & 0.26* & 0.10 & 0.00 & 0.00 & 0.00 \\ 
+  c9 -$>$ s & -0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  c10 -$>$ s & 0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  BIC & 3465.28 & 3427.46 & 3415.05 & 3414.38 & 3417.20 \\ 
    \hline
@@
 these errors), both the adaptive lasso and SCAD correctly identified
-every true zero effect. The lasso and MCP mistakenly identified one
-false effect each. As expected given the small ratio between number of
-estimated parameters and sample size, maximum likelihood mistakenly
-identified 3 false effects as significant.
+every true zero effect. The lasso identified two false effects while the
+MCP mistakenly identified one. Additionally, the lasso estimation of the
+true effects was attentuated in comparison to the other regularization
+methods. This is in line with previous research (cite), necessitating
+the use of a two-step relaxed lasso method (Meinshausen 2007, see
+Jacobucci, Grimm, and McArdle (2016)) As expected given the small ratio
+between number of estimated parameters and sample size, maximum
+likelihood mistakenly identified 3 false effects as significant.
 
@@
 regularization methods performs well regardless of sample size. Each run
-was replicated 200 times, with the corresponding code in the Appendix.
-The results are displayed in Table *
+was replicated 200 times. The results are displayed in Table *
 
@@
 
+This paper provides an introduction to the \pkg{regsem} package,
+outlining the mathematical details of the regularized SEM method and the
+usage of the package itself.
+
 \subsection{Future Directions}\label{future-directions}
 
-\subsection{Limitation}\label{limitation}
+\subsection{Limitations}\label{limitations}
+
+With highly constrained structural equation models, achieving
+convergence can be particularly problematic in using \pkg{regsem}. For
+instance, with the latent change score model (cite jack), Bayesian
+regularization methods have less difficulty in reaching convergence
+across chains (cite chapter). With the advent of additional sparsity
+inducing priors, along with new forms of software such as STAN (cite
+stan), for some models it may be more appropriate to use these Bayesian
+regularization methods over their frequentist counterparts.
 
@@
 
+\hypertarget{ref-meinshausen2007relaxed}{}
+Meinshausen, Nicolai. 2007. ``Relaxed Lasso.'' \emph{Computational
+Statistics \& Data Analysis} 52 (1). Elsevier: 374--93.
+
 \hypertarget{ref-raykov1999desirability}{}

### 2017-03-07 draft1.Rmd
first full draft

@@
 
-This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized SEM method and the usage of the package itself.
+This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized structural equation modeling [RegSEM; @jacobucci2016regularized] method and the usage of the package itself.
+RegSEM allows the use of regularization while keeping the structural equation model intact, adding penalization directly into the estimation of the model.
+The application of RegSEM was detailed using two example models: a latent growth curve model with 20 predictors of both the latent intercept and slope, along with a factor analysis with one latent factor.
+With the latent growth curve model, the small parameter to sample size ratio resulted in a larger number of false positives in using maximum likelihood estimation.
+In both the simulated example and the small simulation, the different types of regularization in \pkg{regsem} demonstrated better false positive and negative rates in comparison to maxiumum likelihood across sample sizes.
 
-## Future Directions
+Broadly speaking, there is a growing amount of research into the integration between data mining methods and latent variable models.
+Specifically, beyond regularized SEM, this has taken form of item response theory and regularization [@sun2016latent], pairing both structural equation models with decision trees [@brandmaier2013], exploratory psychological network analaysis [e.g.
+@epskamp2016generalized], along with many others.
+The amount of pairing between methods that have generally been housed in separate camps will only increase into the future.
+This type of research will be facilitated by the general upsurge in the creation of open source software that gives users a general framework to test models.
+This was the motivation behind creating the \pkg{regsem} package in that users can estimate models ranging from simple factor analysis models, to latent longitudinal models with few to many time points, and finally to models with a large number of latent and observed variables.
+The use of regularization allows for the estimation of much larger structural equation models than before.
+Specifically, given that latent variables, as discussed in this article, are more commonly used in the social and behavioral sciences, sample sizes are generally not large.
+To estimate large models with sample sizes invites increasing amounts of bias, and as demonstrated with the simulated data in this paper, regularization can be used to reduce the complexity of the model, decreasing both the bias and variance.
 
-## Limitations
+With highly constrained structural equation models, achieving model convergence can be particularly problematic in using \pkg{regsem}.
+For instance, with the latent change score model [@mcardle2001latent], Bayesian regularization methods have less difficulty in reaching convergence across chains (Jacobucci and Grimm 2017).
+With the recent advent of additional sparsity inducing priors, along with new forms of software such as STAN [@carpenter2016stan], for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.
+Particularly with structural equation models, although some research exists [@feng2017bayesian], much more is warranted.
 
-With highly constrained structural equation models, achieving convergence can be particularly problematic in using \pkg{regsem}.
-For instance, with the latent change score model (cite jack), Bayesian regularization methods have less difficulty in reaching convergence across chains (cite chapter).
-With the advent of additional sparsity inducing priors, along with new forms of software such as STAN (cite stan), for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.
+Future research with \pkg{regsem} should focus on a number of avenues.
+One is comparing the different forms of regularization, delineating which method may best best in which circumstances.
+Additionally, as structural equation models become larger, with the advent of much larger datasets, speed will become a principal concern.
+Although 40 penalties in the models tested above can be run in a matter of seconds on a standard laptop, larger models can take much longer.
+To handle this, future implementation with \pkg{regsem} will test the inclusion of different types of optimization, specifically testing whether computation of the Hessian (or approximate Hessian) can reduce the number of optimization steps.
 
 ## Conclusion
+
+This paper provided a brief overview on the use of the \pkg{regsem} package as an implementation of regularized structural equation model.
+Because structural equation modeling encompasses a wide array of latent variable models, the \pkg{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.
+Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
+RegSEM is a method that operates at all ends of the data size spectrum: allowing for a reduction in complexity when the sample size is small, along with  dimension reduction in the presence of large data (both $N$ and $P$).
+
+# References

### 2017-03-07 draft1.tex
first full draft

@@
 This paper provides an introduction to the \pkg{regsem} package,
-outlining the mathematical details of the regularized SEM method and the
-usage of the package itself.
+outlining the mathematical details of the regularized structural
+equation modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) method
+and the usage of the package itself. RegSEM allows the use of
+regularization while keeping the structural equation model intact,
+adding penalization directly into the estimation of the model. The
+application of RegSEM was detailed using two example models: a latent
+growth curve model with 20 predictors of both the latent intercept and
+slope, along with a factor analysis with one latent factor. With the
+latent growth curve model, the small parameter to sample size ratio
+resulted in a larger number of false positives in using maximum
+likelihood estimation. In both the simulated example and the small
+simulation, the different types of regularization in \pkg{regsem}
+demonstrated better false positive and negative rates in comparison to
+maxiumum likelihood across sample sizes.
 
-\subsection{Future Directions}\label{future-directions}
+Broadly speaking, there is a growing amount of research into the
+integration between data mining methods and latent variable models.
+Specifically, beyond regularized SEM, this has taken form of item
+response theory and regularization (Sun et al. 2016), pairing both
+structural equation models with decision trees (Brandmaier et al. 2013),
+exploratory psychological network analaysis (e.g. Epskamp, Rhemtulla,
+and Borsboom 2016), along with many others. The amount of pairing
+between methods that have generally been housed in separate camps will
+only increase into the future. This type of research will be facilitated
+by the general upsurge in the creation of open source software that
+gives users a general framework to test models. This was the motivation
+behind creating the \pkg{regsem} package in that users can estimate
+models ranging from simple factor analysis models, to latent
+longitudinal models with few to many time points, and finally to models
+with a large number of latent and observed variables. The use of
+regularization allows for the estimation of much larger structural
+equation models than before. Specifically, given that latent variables,
+as discussed in this article, are more commonly used in the social and
+behavioral sciences, sample sizes are generally not large. To estimate
+large models with sample sizes invites increasing amounts of bias, and
+as demonstrated with the simulated data in this paper, regularization
+can be used to reduce the complexity of the model, decreasing both the
+bias and variance.
 
-\subsection{Limitations}\label{limitations}
+With highly constrained structural equation models, achieving model
+convergence can be particularly problematic in using \pkg{regsem}. For
+instance, with the latent change score model (McArdle and Hamagami
+2001), Bayesian regularization methods have less difficulty in reaching
+convergence across chains (Jacobucci and Grimm 2017). With the recent
+advent of additional sparsity inducing priors, along with new forms of
+software such as STAN (Carpenter et al. 2016), for some models it may be
+more appropriate to use these Bayesian regularization methods over their
+frequentist counterparts. Particularly with structural equation models,
+although some research exists (Feng, Wu, and Song 2017), much more is
+warranted.
 
-With highly constrained structural equation models, achieving
-convergence can be particularly problematic in using \pkg{regsem}. For
-instance, with the latent change score model (cite jack), Bayesian
-regularization methods have less difficulty in reaching convergence
-across chains (cite chapter). With the advent of additional sparsity
-inducing priors, along with new forms of software such as STAN (cite
-stan), for some models it may be more appropriate to use these Bayesian
-regularization methods over their frequentist counterparts.
+Future research with \pkg{regsem} should focus on a number of avenues.
+One is comparing the different forms of regularization, delineating
+which method may best best in which circumstances. Additionally, as
+structural equation models become larger, with the advent of much larger
+datasets, speed will become a principal concern. Although 40 penalties
+in the models tested above can be run in a matter of seconds on a
+standard laptop, larger models can take much longer. To handle this,
+future implementation with \pkg{regsem} will test the inclusion of
+different types of optimization, specifically testing whether
+computation of the Hessian (or approximate Hessian) can reduce the
+number of optimization steps.
 
-\subsection*{Conclusion}\label{conclusion}
-\addcontentsline{toc}{subsection}{Conclusion}
+\subsection{Conclusion}\label{conclusion}
+
+This paper provided a brief overview on the use of the \pkg{regsem}
+package as an implementation of regularized structural equation model.
+Because structural equation modeling encompasses a wide array of latent
+variable models, the \pkg{regsem} package was created as a general
+package for including different forms of regularization into a host of
+latent variable models. Future updates to \pkg{regsem} will focus on
+decreasing the computational time of large latent variable models in
+order to provide an avenue of testing for researchers collecting larger
+and larger datasets. RegSEM is a method that operates at all ends of the
+data size spectrum: allowing for a reduction in complexity when the
+sample size is small, along with dimension reduction in the presence of
+large data (both \(N\) and \(P\)).
+
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
 
 \hypertarget{refs}{}
+\hypertarget{ref-brandmaier2013}{}
+Brandmaier, Andreas M., Timo von Oertzen, John J. McArdle, and Ulman
+Lindenberger. 2013. ``Structural Equation Model Trees.''
+\emph{Psychological Methods} 18 (1): 71--86.
+
 \hypertarget{ref-browne2001}{}
@@
 
+\hypertarget{ref-carpenter2016stan}{}
+Carpenter, Bob, Andrew Gelman, Matt Hoffman, Daniel Lee, Ben Goodrich,
+Michael Betancourt, Michael A Brubaker, Jiqiang Guo, Peter Li, and Allen
+Riddell. 2016. ``Stan: A Probabilistic Programming Language.''
+\emph{Journal of Statistical Software} 20.
+
 \hypertarget{ref-donoho1995noising}{}
@@
 Transactions on Information Theory} 41 (3). IEEE: 613--27.
+
+\hypertarget{ref-epskamp2016generalized}{}
+Epskamp, Sacha, Mijke Rhemtulla, and Denny Borsboom. 2016. ``Generalized
+Network Psychometrics: Combining Network and Latent Variable Models.''
+\emph{ArXiv Preprint ArXiv:1605.09288}.
 
@@
 American Statistical Association} 96 (456). Taylor \& Francis: 1348--60.
+
+\hypertarget{ref-feng2017bayesian}{}
+Feng, Xiang-Nan, Hao-Tian Wu, and Xin-Yuan Song. 2017. ``Bayesian
+Regularized Multivariate Generalized Latent Variable Models.''
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}. Taylor
+\& Francis, 1--18.
 
@@
 
+\hypertarget{ref-mcardle2001latent}{}
+McArdle, John J, and Fumiaki Hamagami. 2001. ``Latent Difference Score
+Structural Models for Linear Dynamic Analyses with Incomplete
+Longitudinal Data.'' American Psychological Association.
+
 \hypertarget{ref-meinshausen2007relaxed}{}
@@
 Psychometric Society, Iowa City, Ia}. Vol. 758.
+
+\hypertarget{ref-sun2016latent}{}
+Sun, Jianan, Yunxiao Chen, Jingchen Liu, Zhiliang Ying, and Tao Xin.
+2016. ``Latent Variable Selection for Multidimensional Item Response
+Theory Models via L\_ \(\{\)1\(\}\) Regularization.''
+\emph{Psychometrika} 81 (4). Springer: 921--39.
 

### 2017-03-08 draft1.Rmd
update sim table

@@
 best.pars[21,2] <- min(reg.out[[2]][,"BIC"])
-loc1 <- which(reg.out[[2]][,"BIC"] ==min(reg.out[[2]][,"BIC"]))
+loc1 <- which(reg.out[[2]][,"BIC"] ==min(reg.out[[2]][,"BIC"]))[1]
 best.pars[1:20,2] <- reg.out[[1]][loc1,1:20]
@@
 best.pars[21,3] <- min(reg.out2[[2]][,"BIC"])
-loc2 <- which(reg.out2[[2]][,"BIC"] ==min(reg.out2[[2]][,"BIC"]))
+loc2 <- which(reg.out2[[2]][,"BIC"] ==min(reg.out2[[2]][,"BIC"]))[1]
 best.pars[1:20,3] <- reg.out2[[1]][loc2,1:20]
@@
 best.pars[21,4] <- min(reg.out3[[2]][,"BIC"])
-loc3 <- which(reg.out3[[2]][,"BIC"] ==min(reg.out3[[2]][,"BIC"]))
+loc3 <- which(reg.out3[[2]][,"BIC"] ==min(reg.out3[[2]][,"BIC"]))[1]
 best.pars[1:20,4] <- reg.out3[[1]][loc3,1:20]
@@
 best.pars[21,5] <- min(reg.out4[[2]][,"BIC"])
-loc4 <- which(reg.out4[[2]][,"BIC"] ==min(reg.out4[[2]][,"BIC"]))
+loc4 <- which(reg.out4[[2]][,"BIC"] ==min(reg.out4[[2]][,"BIC"]))[1]
 best.pars[1:20,5] <- reg.out4[[1]][loc4,1:20]
@@
 \centering
-	\begin{tabular}{rrrrrrrr}
+\begin{tabular}{rrrrrrr}
   \hline
@@
   \hline
-		 & 80.00 & 0.09 & 0.05 & \textbf{0.04} & 0.05 & 0.05 \\ 
-		False Positives & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.04 \\ 
-		 & 1000.00 & 0.05 & 0.05 & \textbf{0.01} & \textbf{0.01} & 0.19 \\ 
-		 & 80.00 & 0.45 & \textbf{0.41} & 0.43 & 0.45 & 0.54 \\ 
-		False Negatives & 200.00 & 0.30 & \textbf{0.24} & 0.29 & 0.29 & 0.45 \\ 
-		 & 1000.00 & 0.10 & \textbf{0.09} & 0.17 & 0.19 & 0.24 \\ 
+1 & 80.00 & 0.08 & 0.08 & 0.04 & 0.05 & 0.04 \\ 
+  2 & 200.00 & 0.06 & 0.05 & 0.02 & 0.03 & 0.03 \\ 
+  3 & 1000.00 & 0.05 & 0.08 & 0.01 & 0.01 & 0.28 \\ 
+  4 & 80.00 & 0.33 & 0.31 & 0.35 & 0.35 & 0.45 \\ 
+  5 & 200.00 & 0.19 & 0.19 & 0.23 & 0.26 & 0.45 \\ 
+  6 & 1000.00 & 0.00 & 0.00 & 0.00 & 0.01 & 0.14 \\ 
    \hline

### 2017-03-08 draft1.Rmd
draft sent to sarfaraz

@@
     address: >
-      First line
-      Second line
+      118 Haggar Hall, 
+      Notre Dame, IN 46556
     email: rcjacobuc@gmail.com
@@
 abstract: >
-  The \pkg{regsem} package in \proglang{R}, an implementation of Regularized Structural Equation Modeling [@jacobucci2016regularized], was recently developed with the goal incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
-The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator (\textit{lasso}; [@Tibshirani1996], along with sparser extensions.
-The paper details both the algorithmic details and an overview of the use of \pkg{regsem} through both a factor analysis and latent growth curve models.
+  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
+The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996], along with sparser extensions.
+RegSEM is particularly useful for structural equation models that have a small parameter to sample size ratio, as the addition of penalties can reduce the complexity, thus reducing the bias of the parameter estimates.
+The paper details the algorithmic details and an overview of the use of \pkg{regsem} with the application of both factor analysis and latent growth curve models.
 keywords:
@@
 The goal is accurately and efficiently estimate a model that is parsimonious in allowing users to easily interpret the model's representation of reality.
-In Figure 1, this would entail testing whether the cross-loadings are necessary to the fit of the model, or whether they can be pared away without an meaningful increase in bias.
-
 In the context of latent variables, reducing the complexity of models can come in many forms: selecting among multiple predictors of a latent variable, simplifying factor structure by removing cross-loadings, determining whether the addition of nonlinear terms are necessary in longitudinal models, and many others.
-As a simple running example, Figure 1 depicts a linear latent growth curve model with four time points and ten predictors for a simulated dataset.
+As a simple running example, Figure 1 depicts a linear latent growth curve model [e.g.
+@meredith1990latent] with four time points and ten predictors for a simulated dataset.
 
@@
 10:1 parameters to sample size; @kline2015principles].
-In lieu of finding additional respondents, reducing the number of parameters estimated is one effective strategy.
+In lieu of finding additional respondents, reducing the number of parameters estimated is one effective strategy for reducing bias.
 Specifically, the 20 estimated regressions from \textit{c1-c10} could be reduced to a number that makes the number of parameters estimated to sample size ratio more reasonable.
+To explore this further, the next section provides an overview of regularization, and how different forms can be used to perform variable selection across a broad range of models.
 
@@
 where $\beta_{0}$ is the intercept, $\beta_{j}$ is the coefficient for $x_{j}$, and $\lambda$ is the penalty that controls the amount of shrinkage.
-Note that when $\lambda = 0$, equation 3 reduces to ordinary least squares regression.
+Note that when $\lambda = 0$, Equation 3 reduces to ordinary least squares regression.
 As $\lambda$ is increased, the $\beta$ parameters are shrunken towards zero.
@@
 In the context of our example depicted in Figure 1, to use lasso regression to select among the covariates, the growth model would need to be reduced to two factor scores, which neglects both the relationship between both the slope and intercept, reducing both to independent factor scores.
-Particularly in models with a greater number of latent variables, this becomes increasing problematic.
-A method that keeps the model structure, while allowing for a penalized estimation of specific parameters is regularized structural equation modeling [RegSEM; @jacobucci2016regularized].
-RegSEM adds a penalty function to the traditional maximum likelihood cost function for SEMs.
+Particularly in models with a greater number of latent variables, this becomes increasingly problematic.
+A method that keeps the model structure, while allowing for penalized estimation of specific parameters is regularized structural equation modeling [RegSEM; @jacobucci2016regularized].
+RegSEM adds a penalty function to the traditional maximum likelihood estimation (MLE) for structural equation models (SEMs).
 The maximum likelihood cost function for SEMs can be written as
@@
 where $\Sigma$ is the model implied covariance matrix, $C$ is the observed covariance matrix, and $p$ is the number of estimated parameters.
-RegSem builds in an additional element to penalize certain model parameters yielding
+RegSEM builds in an additional element to penalize certain model parameters yielding
 
@@
 $P(\cdot)$ is a general function for summing the values of one or more of the model's parameter matrices.
-The two common forms of $P(\cdot)$ include both the Lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and Ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.
+The two common forms of $P(\cdot)$ include both the lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.
 
@@
 $$
-
-Although the fit of the model is easily calculated given a set of parameter estimates, traditional optimization procedures for SEM cannot be used given the non-differentiable nature of lasso penalties, and as detailed later, extensions.
+\noindent
+Although the fit of the model is easily calculated given a set of parameter estimates, traditional optimization procedures for SEM cannot be used given the non-differentiable nature of lasso penalties, and as detailed later, sparse extensions.
 
@@
 In comparison to one-step procedures common in SEM optimization, that only involve a method for calculating the step size and the direction (typically using the gradient and an approximation of the Hessian), proximal gradient descent can be formulated as a two-step procedure.
-With a stepsize of $\alpha^{t}$ and parameters $\theta^{t}$ at iteration \textit{t}:
+With a stepsize of $s^{t}$ and parameters $\theta^{t}$ at iteration \textit{t}:
 
 \begin{enumerate}
-	\item First, take a gradient step size $z = \theta^{t} - \alpha^{t} \nabla g(\theta^{t})$.
-	\item Second, perform elementwise soft-thresholding $\theta^{t+1} = S_{\alpha^{t} \lambda}(z)$.
+	\item First, take a gradient step size $z = \theta^{t} - s^{t} \nabla g(\theta^{t})$.
+	\item Second, perform elementwise soft-thresholding $\theta^{t+1} = S_{s^{t} \lambda}(z)$.
 \end{enumerate}
 
-where $S_{\alpha \lambda}(z)$ is the soft-thresholding operator [@donoho1995noising] used to overcome non-differentiability of the lasso penalty at the origin: 
+where $S_{s^{t} \lambda}(z)$ is the soft-thresholding operator [@donoho1995noising] used to overcome non-differentiability of the lasso penalty at the origin: 
 \begin{equation}
-S_{\alpha \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-\alpha \lambda)_{+}
+S_{s^{t} \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-s^{t} \lambda)_{+}
 \end{equation}
-where $(x)_{+}$ is shorthand for max(x,0) and $\alpha$ is the step size.
+\noindent
+where $(x)_{+}$ is shorthand for max(x,0) and $s^{t}$ is the step size.
 Henceforth, $\lambda$ is assumed to encompass both the penalty and the step size $s^{t}$.
@@
 			\State Calculate initial fit $F_{t}$
-			\State Set step size $\alpha$. .5 works well at this time.
+			\State Set step size $s$. .1 works well at this time.
 			\State Set tolerance (tol). e.g. 1e-6
@@
 			\State Calculate gradient for A:$ \nabla (A) =:  \frac{\partial A}{\partial \theta_{t}}$
-			\State $ \theta_{t+1^{*},A} =: \theta_{t,A} - \alpha \nabla(A)$
-			\State  Update penalized parameters: $\theta_{t+1^{*},A(pen)} =: S_{\alpha \lambda}(\theta_{t+1^{*},A(pen)})$
+			\State $ \theta_{t+1^{*},A} =: \theta_{t,A} - s \nabla(A)$
+			\State  Update penalized parameters: $\theta_{t+1^{*},A(pen)} =: S_{s \lambda}(\theta_{t+1^{*},A(pen)})$
 			\State Calculate gradient for S:$ \nabla (S) =:  \frac{\partial S}{\partial \theta_{t+1^{*}}}$ 
-			\State Update S parameters: $ \theta_{t+1^{*},S} =: \theta_{t,S} - \alpha \nabla(S)$
+			\State Update S parameters: $ \theta_{t+1^{*},S} =: \theta_{t,S} - s \nabla(S)$
 			\State $\theta_{t+1} =: \theta_{t+1^{*}}$ %vec(\theta_{t+1^{*},A},\theta_{t+1^{*},S})$
@@
 
-Most notably, the elastic net [@zou2005regularization] encompasses both the ridge and lasso, reaching a compromise between both through the addition of an additional parameter $\alpha$.
+Most notably, the elastic net [@zou2005regularization] encompasses both the ridge and lasso, reaching a compromise between both through the addition of an additional parameter $\alpha$, manifesting itself as
 
@@
 One method proposed for overcoming this limitation is the adaptive lasso [@zou2006adaptive].
-Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (maximum likelihood estimate in SEM).
-This manifests itself as:
+Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (MLE parameter estimates in SEM).
+The adaptive lasso results in:
 $$
@@
 \noindent
-In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant, parameters.
-Note that one limitation of this approach for SEM models is that the model needs to be estimable with maximum likelihood.
+In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant parameters.
+Note that one limitation of this approach for SEM models is that the model needs to be estimable with MLE.
 Particularly for models with large numbers of variables, in relation to sample size, this may not be possible.
@@
 Two additional penalties that overcome some of the deficiencies of the lasso, producing sparser solutions, include the smoothly clipped absolute deviation penalty [SCAD; @fan2001variable] and the minimax concave penalty [MCP; @zhang2010nearly].
-In comparison to the lasso, both the SCAD and MCP have much steeper penalties for smaller parameters, as is evident in Figure **.
+In comparison to the lasso, both the SCAD and MCP have much smaller penalties for large parameters, where the amount of penalty for small penalties is similar to the lasso, as is evident in Figure 2.
 
@@
 \noindent
+for $\gamma > 2$.
 As the the penalty in equation 11 is non-convex (as is the MCP), this makes computation more difficult.
@@
 \noindent
-As seen in Figure **, this results in similar amount of shrinkage for smaller estimates in comparison to the SCAD, however, less for larger estimates.
+for $\gamma > 0$.
+As seen in Figure 2, this results in similar amount of shrinkage for smaller estimates in comparison to the SCAD, however, less for larger estimates.
+For both the SCAD and MCP, both the $\gamma$ and $\lambda$ parameters are used as hyper-parameters.
+This involves testing models over a two-dimensional array of parameters, however, $\gamma$ can be fixed to 3.7 per @fan2001variable.
 
@@
 
-RegSEM is implemented as the \pkg{regsem} package in the \proglang{R} statistical environment.
+RegSEM is implemented as the \pkg{regsem} package [@jacobucci2016package] in the \proglang{R} statistical environment [@statspackage].
 To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984, @mcardle2005] notation to derive an implied covariance matrix.
@@
 To use \pkg{regsem}, the user has to first fit the model in \pkg{lavaan}.
-As an example, below is the code for a one factor model fit in lavaan with the Holzinger-Swineford [@holzinger1939study] dataset.
+As an example, below is the code for a one factor model fit in lavaan with the @holzinger1939study dataset.
 
@@
 After a model is run in lavaan, using \code{lavaan()} or any of the wrapper functions for fitting a model (i.e.
-\code{sem()}, \code{cfa()}, or \code{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem}.
+\code{sem()}, \code{cfa()}, or \code{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem()}.
 The \code{regsem()} function runs a model with one penalty value, whereas \code{multi_optim()} does the same but allows for the use of random starting values.
 However, the main function is \code{cv_regsem()} as this not only runs the model, but runs it across a vector of varying penalty values.
-For instance in the above one-factor model, each of the factor loadings can be tested with lasso penalties to determine whether each indicator is a necessary component of the latent factor.
+For instance in the above one-factor model, each of the factor loadings can be tested with lasso penalties to determine whether each indicator is a necessary component of the latent factor:
 
@@
 
-The \code{out.reg} object contains two components, \code{out.reg[[1]]} has the parameter estimates for each of the 15 models, while \code{out.reg[[2]]} has the fit of each model.
-For the code above, using the \pkg{xtable} package to turn the output from  \code{out.reg[[2]]} into a table
+The \code{out.reg} object contains two components, \code{out.reg[[1]]} has the parameter estimates for each of the 15 models,
 
 ```{r}
-round(out.reg[[2]],3)
+head(round(out.reg[[1]],2),5)
 ```
 
-In this, the user can examine the penalty (lambda), whether the model converged ("conv"), with values of 0 indicating convergence, and the fit of each model.
+\noindent
+while \code{out.reg[[2]]} looks like:
+
+```{r}
+round(out.reg[[2]],2)
+```
+
+In this, the user can examine the penalty (lambda), whether the model converged ("conv"=0), and the fit of each model.
 By default, two fit indices are output, both the root mean square error of approximation [RMSEA; @steiger1980], and the Bayesian information criteria [BIC; @schwarz1978estimating].
 Both the RMSEA and BIC take into account the degrees of freedom of the model, an important point for model selection in the presence of lasso penalties (and other penalties that set parameters to zero).
-This concurs with work done on degrees of freedom for lasso regression, as @Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression.
+Based on work done on degrees of freedom for lasso regression, as @Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression.
 As the penalty increases, select parameter are set to zero, thus the degrees of freedom increases, which for fit indices that include the degrees of freedom in the calculation, means that although the likelihood of the model may only get worse (increase), both the RMSEA and BIC can improve (decrease) due to the impact of increased degrees of freedom.
 
-Instead of examining the \code{out.reg[[1]]} output matrix of parameter estimates, it is easiest to plot the trajectory of each of the penalized parameters.
+Instead of examining the \code{out.reg[[1]]} output matrix of parameter estimates, users also have the option to plot the trajectory of each of the penalized parameters.
 This is accomplished with \code{plot_cv(out.reg,pars=1:9)}, resulting in:
@@
 
-After a final model (penalty) is chosen, user's have the option either just use the output from \code{cv_regsem()}, or the final model can be re-run with either \code{regsem()} or \code{multi_optim()} to attain additional information.
+After a final model (penalty) is chosen, users have the option either just use the output from \code{cv_regsem()}, or the final model can be re-run with either \code{regsem()} or \code{multi_optim()} to attain additional information.
 In the model above, the best fitting penalty, according to the BIC, is $\lambda=0$.
@@
 
-To compare the different types of penalties in \pkg{regsem}, we return to the the initial example of the latent growth curve model.
-Using the same simulated data (see Appendix), the model can be run in \pkg{lavaan} as
+To compare the different types of penalties in \pkg{regsem}, we return to the the initial example of the latent growth curve model displayed in Figure 1.
+Using the same simulated data, the model can be run in \pkg{lavaan} as
 
@@
 
-For the purposes of comparison, each of the 20 covariate regressions were penalized using the lasso, adaptive lasso, SCAD, and MCP, and compared to the maximum likelihood estimates (see Appendix for code).
+For the purposes of comparison, each of the 20 covariate regressions were penalized using the lasso, adaptive lasso, SCAD, and MCP, and compared to the maximum likelihood estimates.
 In this model, the data were simulated to have two large effects (both \textit{c1} parameters), two small effects (both \textit{c2} parameters) and sixteen true zero effects (\textit{c3-c10} parameters).
@@
 If there was substantial collinearity among covariates, the elastic net would be more appropriate to simultaneously select predictors while also accounting for the collinearity.
-The parameter estimates corresponding the the best fit of the BIC are displayed in Table *
+The parameter estimates corresponding the the best fit of the BIC are has the fit of each model, resulting in Table 1, created using the \pkg{xtable} package [@dahl2009xtable].
 
@@
 Additionally, the lasso estimation of the true effects was attentuated in comparison to the other regularization methods.
-This is in line with previous research (cite), necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed, see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
+This is in line with previous research [@fan2001variable], necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed, see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
 
@@
 Each run was replicated 200 times.
-The results are displayed in Table *
+For each regularization method, the BIC was used to choose a final model among the 40 penalty vales.
+The results are displayed in Table 2.
 
@@
   \hline
-1 & 80.00 & 0.08 & 0.08 & 0.04 & 0.05 & 0.04 \\ 
-  2 & 200.00 & 0.06 & 0.05 & 0.02 & 0.03 & 0.03 \\ 
-  3 & 1000.00 & 0.05 & 0.08 & 0.01 & 0.01 & 0.28 \\ 
-  4 & 80.00 & 0.33 & 0.31 & 0.35 & 0.35 & 0.45 \\ 
-  5 & 200.00 & 0.19 & 0.19 & 0.23 & 0.26 & 0.45 \\ 
-  6 & 1000.00 & 0.00 & 0.00 & 0.00 & 0.01 & 0.14 \\ 
+1 & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & \textbf{0.04} \\ 
+  2 & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.03 \\ 
+  3 & 1000.00 & 0.05 & 0.08 & \textbf{0.01} & \textbf{0.01} & 0.28 \\ 
+  4 & 80.00 & 0.33 & \textbf{0.31} & 0.35 & 0.35 & 0.45 \\ 
+  5 & 200.00 & \textbf{0.19} & \textbf{0.19} & 0.23 & 0.26 & 0.45 \\ 
+  6 & 1000.00 & \textbf{0.00} & \textbf{0.00} & \textbf{0.00} & 0.01 & 0.14 \\ 
    \hline
@@
 
+For false positive, the adaptive lasso demonstrated the best performance, where the performance of maximum likelihood estimation leveled off at the 0.05 level at a sample size of 1000 as expected.
+For false negatives, lasso penalties demonstrated similar results to maximum likelihood.
+This was expected given the tendency of the lasso to under-penalize small coefficients in comparison to the other regularization methods.
+The adaptive lasso and SCAD demonstrated slightly worse results, however, outside of the MCP, each method made either zero or near zero errors at a sample size of 1000.
+The poor performance of the MCP may be in part due to fixing the $\gamma$ penalty to 3.7.
+Varying this parameter may improve the performance of the method.
+In summary, the regularization methods demonstrated an improvement over maximum likelihood, particularly at small samples, for a model that had a large number of estimated parameters.
+
 # Discussion
 
-This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized structural equation modeling [RegSEM; @jacobucci2016regularized] method and the usage of the package itself.
+This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized structural equation modeling [RegSEM; @jacobucci2016regularized] method and the usage of the \pkg{regsem} package.
 RegSEM allows the use of regularization while keeping the structural equation model intact, adding penalization directly into the estimation of the model.
@@
 Broadly speaking, there is a growing amount of research into the integration between data mining methods and latent variable models.
-Specifically, beyond regularized SEM, this has taken form of item response theory and regularization [@sun2016latent], pairing both structural equation models with decision trees [@brandmaier2013], exploratory psychological network analaysis [e.g.
+Specifically, beyond RegSEM, this has taken form of item response theory and regularization [@sun2016latent], pairing both structural equation models with decision trees [@brandmaier2013], exploratory psychological network analaysis [e.g.
 @epskamp2016generalized], along with many others.
@@
 Specifically, given that latent variables, as discussed in this article, are more commonly used in the social and behavioral sciences, sample sizes are generally not large.
-To estimate large models with sample sizes invites increasing amounts of bias, and as demonstrated with the simulated data in this paper, regularization can be used to reduce the complexity of the model, decreasing both the bias and variance.
+To estimate large models with small sample sizes invites increasing amounts of bias, and as demonstrated with the simulated data in this paper.
+Regularization can be used to reduce the complexity of the model, thus decreasing both the bias and variance.
 
@@
 For instance, with the latent change score model [@mcardle2001latent], Bayesian regularization methods have less difficulty in reaching convergence across chains (Jacobucci and Grimm 2017).
-With the recent advent of additional sparsity inducing priors, along with new forms of software such as STAN [@carpenter2016stan], for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.
-Particularly with structural equation models, although some research exists [@feng2017bayesian], much more is warranted.
+With the recent advent of additional sparsity inducing priors, along with new forms of software such as Stan [@carpenter2016stan], for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.
+In the realm of Bayesian regularization for structural equation models, although some research exists [@feng2017bayesian], much more is warranted.
 
 Future research with \pkg{regsem} should focus on a number of avenues.
-One is comparing the different forms of regularization, delineating which method may best best in which circumstances.
-Additionally, as structural equation models become larger, with the advent of much larger datasets, speed will become a principal concern.
+One is comparing the different forms of regularization, delineating which method may best best in which setting.
+Additionally, as structural equation models become larger, with the advent of much larger datasets, computational speed will become a principal concern.
 Although 40 penalties in the models tested above can be run in a matter of seconds on a standard laptop, larger models can take much longer.
@@
 Because structural equation modeling encompasses a wide array of latent variable models, the \pkg{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.
-Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
+RegSEM, and thus the \pkg{regsem} package, has been evaluated in a wide array of SEM models, including confirmatory factor analysis [@jacobucci2016regularized], latent change score models (Jacobucci and Grimm 2017), mediation models [@serang2017xmed].Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
 RegSEM is a method that operates at all ends of the data size spectrum: allowing for a reduction in complexity when the sample size is small, along with  dimension reduction in the presence of large data (both $N$ and $P$).

### 2017-03-08 draft1.tex
update sim table
draft sent to sarfaraz

@@
 The \pkg{regsem} package in \proglang{R}, an implementation of
-Regularized Structural Equation Modeling (Jacobucci, Grimm, and McArdle
-2016), was recently developed with the goal incorporating various forms
-of penalized likelihood estimation with a broad array of structural
-equations models. The forms of regularization include both the
-\textit{ridge} (Hoerl and Kennard 1970) and the least absolute shrinkage
-and selection operator (\textit{lasso}; (Tibshirani 1996), along with
-sparser extensions. The paper details both the algorithmic details and
-an overview of the use of \pkg{regsem} through both a factor analysis
-and latent growth curve models.
+regularized structural equation modeling (RegSEM; Jacobucci, Grimm, and
+McArdle 2016), was recently developed with the goal incorporating
+various forms of penalized likelihood estimation with a broad array of
+structural equations models. The forms of regularization include both
+the \textit{ridge} (Hoerl and Kennard 1970) and the least absolute
+shrinkage and selection operator (\textit{lasso}; Tibshirani 1996),
+along with sparser extensions. RegSEM is particularly useful for
+structural equation models that have a small parameter to sample size
+ratio, as the addition of penalties can reduce the complexity, thus
+reducing the bias of the parameter estimates. The paper details the
+algorithmic details and an overview of the use of \pkg{regsem} with the
+application of both factor analysis and latent growth curve models.
 }
@@
   University of Notre Dame\\
-  First line Second line\\
+  118 Haggar Hall, Notre Dame, IN 46556\\
   E-mail: \href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}\\
@@
 parsimonious in allowing users to easily interpret the model's
-representation of reality. In Figure 1, this would entail testing
-whether the cross-loadings are necessary to the fit of the model, or
-whether they can be pared away without an meaningful increase in bias.
-
-In the context of latent variables, reducing the complexity of models
-can come in many forms: selecting among multiple predictors of a latent
-variable, simplifying factor structure by removing cross-loadings,
-determining whether the addition of nonlinear terms are necessary in
-longitudinal models, and many others. As a simple running example,
-Figure 1 depicts a linear latent growth curve model with four time
-points and ten predictors for a simulated dataset.
+representation of reality. In the context of latent variables, reducing
+the complexity of models can come in many forms: selecting among
+multiple predictors of a latent variable, simplifying factor structure
+by removing cross-loadings, determining whether the addition of
+nonlinear terms are necessary in longitudinal models, and many others.
+As a simple running example, Figure 1 depicts a linear latent growth
+curve model (e.g. Meredith and Tisak 1990) with four time points and ten
+predictors for a simulated dataset.
 
@@
 additional respondents, reducing the number of parameters estimated is
-one effective strategy. Specifically, the 20 estimated regressions from
-\textit{c1-c10} could be reduced to a number that makes the number of
-parameters estimated to sample size ratio more reasonable.
+one effective strategy for reducing bias. Specifically, the 20 estimated
+regressions from \textit{c1-c10} could be reduced to a number that makes
+the number of parameters estimated to sample size ratio more reasonable.
+To explore this further, the next section provides an overview of
+regularization, and how different forms can be used to perform variable
+selection across a broad range of models.
 
@@
 for \(x_{j}\), and \(\lambda\) is the penalty that controls the amount
-of shrinkage. Note that when \(\lambda = 0\), equation 3 reduces to
+of shrinkage. Note that when \(\lambda = 0\), Equation 3 reduces to
 ordinary least squares regression. As \(\lambda\) is increased, the
@@
 factor scores. Particularly in models with a greater number of latent
-variables, this becomes increasing problematic. A method that keeps the
-model structure, while allowing for a penalized estimation of specific
+variables, this becomes increasingly problematic. A method that keeps
+the model structure, while allowing for penalized estimation of specific
 parameters is regularized structural equation modeling (RegSEM;
 Jacobucci, Grimm, and McArdle 2016). RegSEM adds a penalty function to
-the traditional maximum likelihood cost function for SEMs. The maximum
-likelihood cost function for SEMs can be written as
+the traditional maximum likelihood estimation (MLE) for structural
+equation models (SEMs). The maximum likelihood cost function for SEMs
+can be written as
 
@@
 observed covariance matrix, and \(p\) is the number of estimated
-parameters. RegSem builds in an additional element to penalize certain
+parameters. RegSEM builds in an additional element to penalize certain
 model parameters yielding
@@
 or more of the model's parameter matrices. The two common forms of
-\(P(\cdot)\) include both the Lasso (\(\| \cdot \|_{1}\)), which
-penalizes the sum of the absolute values of the parameters, and Ridge
+\(P(\cdot)\) include both the lasso (\(\| \cdot \|_{1}\)), which
+penalizes the sum of the absolute values of the parameters, and ridge
 (\(\| \cdot \|_{2}\)), which penalizes the sum of the squared values of
@@
 \end{matrix}  \right\|_{1}
-\]
-
+\] \noindent
 Although the fit of the model is easily calculated given a set of
@@
 be used given the non-differentiable nature of lasso penalties, and as
-detailed later, extensions.
+detailed later, sparse extensions.
 
@@
 approximation of the Hessian), proximal gradient descent can be
-formulated as a two-step procedure. With a stepsize of \(\alpha^{t}\)
-and parameters \(\theta^{t}\) at iteration \textit{t}:
+formulated as a two-step procedure. With a stepsize of \(s^{t}\) and
+parameters \(\theta^{t}\) at iteration \textit{t}:
 
 \begin{enumerate}
-    \item First, take a gradient step size $z = \theta^{t} - \alpha^{t} \nabla g(\theta^{t})$.
-    \item Second, perform elementwise soft-thresholding $\theta^{t+1} = S_{\alpha^{t} \lambda}(z)$.
+    \item First, take a gradient step size $z = \theta^{t} - s^{t} \nabla g(\theta^{t})$.
+    \item Second, perform elementwise soft-thresholding $\theta^{t+1} = S_{s^{t} \lambda}(z)$.
 \end{enumerate}
 
-where \(S_{\alpha \lambda}(z)\) is the soft-thresholding operator
-(Donoho 1995) used to overcome non-differentiability of the lasso
-penalty at the origin:
+where \(S_{s^{t} \lambda}(z)\) is the soft-thresholding operator (Donoho
+1995) used to overcome non-differentiability of the lasso penalty at the
+origin:
 
 \begin{equation}
-S_{\alpha \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-\alpha \lambda)_{+}
+S_{s^{t} \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-s^{t} \lambda)_{+}
 \end{equation}
 
-where \((x)_{+}\) is shorthand for max(x,0) and \(\alpha\) is the step
+\noindent
+where \((x)_{+}\) is shorthand for max(x,0) and \(s^{t}\) is the step
 size. Henceforth, \(\lambda\) is assumed to encompass both the penalty
@@
             \State Calculate initial fit $F_{t}$
-            \State Set step size $\alpha$. .5 works well at this time.
+            \State Set step size $s$. .1 works well at this time.
             \State Set tolerance (tol). e.g. 1e-6
@@
             \State Calculate gradient for A:$ \nabla (A) =:  \frac{\partial A}{\partial \theta_{t}}$
-            \State $ \theta_{t+1^{*},A} =: \theta_{t,A} - \alpha \nabla(A)$
-            \State  Update penalized parameters: $\theta_{t+1^{*},A(pen)} =: S_{\alpha \lambda}(\theta_{t+1^{*},A(pen)})$
+            \State $ \theta_{t+1^{*},A} =: \theta_{t,A} - s \nabla(A)$
+            \State  Update penalized parameters: $\theta_{t+1^{*},A(pen)} =: S_{s \lambda}(\theta_{t+1^{*},A(pen)})$
             \State Calculate gradient for S:$ \nabla (S) =:  \frac{\partial S}{\partial \theta_{t+1^{*}}}$ 
-            \State Update S parameters: $ \theta_{t+1^{*},S} =: \theta_{t,S} - \alpha \nabla(S)$
+            \State Update S parameters: $ \theta_{t+1^{*},S} =: \theta_{t,S} - s \nabla(S)$
             \State $\theta_{t+1} =: \theta_{t+1^{*}}$ %vec(\theta_{t+1^{*},A},\theta_{t+1^{*},S})$
@@
 ridge and lasso, reaching a compromise between both through the addition
-of an additional parameter \(\alpha\).
+of an additional parameter \(\alpha\), manifesting itself as
 
@@
 adaptive lasso (Zou 2006). Instead of penalizing parameters directly,
-each parameter is scaled by the un-penalized estimated (maximum
-likelihood estimate in SEM). This manifests itself as: \[
+each parameter is scaled by the un-penalized estimated (MLE parameter
+estimates in SEM). The adaptive lasso results in: \[
 F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
@@
 In this, larger penalties are given for non-significant (smaller)
-parameters, limiting the bias in estimating larger, significant,
+parameters, limiting the bias in estimating larger, significant
 parameters. Note that one limitation of this approach for SEM models is
-that the model needs to be estimable with maximum likelihood.
-Particularly for models with large numbers of variables, in relation to
-sample size, this may not be possible.
+that the model needs to be estimable with MLE. Particularly for models
+with large numbers of variables, in relation to sample size, this may
+not be possible.
 
@@
 concave penalty (MCP; Zhang 2010). In comparison to the lasso, both the
-SCAD and MCP have much steeper penalties for smaller parameters, as is
-evident in Figure **.
+SCAD and MCP have much smaller penalties for large parameters, where the
+amount of penalty for small penalties is similar to the lasso, as is
+evident in Figure 2.
 
@@
 \noindent
-As the the penalty in equation 11 is non-convex (as is the MCP), this
-makes computation more difficult. However, in the context of SEM this
-can be seen as less problematic, as equation 3 is also non-convex.
+for \(\gamma > 2\). As the the penalty in equation 11 is non-convex (as
+is the MCP), this makes computation more difficult. However, in the
+context of SEM this can be seen as less problematic, as equation 3 is
+also non-convex.
 
@@
 \noindent
-As seen in Figure **, this results in similar amount of shrinkage for
-smaller estimates in comparison to the SCAD, however, less for larger
-estimates.
+for \(\gamma > 0\). As seen in Figure 2, this results in similar amount
+of shrinkage for smaller estimates in comparison to the SCAD, however,
+less for larger estimates. For both the SCAD and MCP, both the
+\(\gamma\) and \(\lambda\) parameters are used as hyper-parameters. This
+involves testing models over a two-dimensional array of parameters,
+however, \(\gamma\) can be fixed to 3.7 per Fan and Li (2001).
 
@@
 
-RegSEM is implemented as the \pkg{regsem} package in the \proglang{R}
-statistical environment. To estimate the maximum likelihood fit of the
-model, \pkg{regsem} uses \textit{Reticular Action Model} (RAM; J. J.
-McArdle and McDonald 1984, McArdle (2005)) notation to derive an implied
-covariance matrix. The parameters of each SEM are translated into three
-matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric}
-(\textit{A}; directed paths; e.g.~factor loadings or regressions), and
-the \textit{symmetric} (\textit{S}; undirected paths; e.g.~covariances
-or variances). See Jacobucci, Grimm, and McArdle (2016) for more detail
-on RAM notation.
+RegSEM is implemented as the \pkg{regsem} package (Jacobucci 2017) in
+the \proglang{R} statistical environment (R Core Team 2017). To estimate
+the maximum likelihood fit of the model, \pkg{regsem} uses
+\textit{Reticular Action Model} (RAM; J. J. McArdle and McDonald 1984,
+McArdle (2005)) notation to derive an implied covariance matrix. The
+parameters of each SEM are translated into three matrices: the
+\textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A};
+directed paths; e.g.~factor loadings or regressions), and the
+\textit{symmetric} (\textit{S}; undirected paths; e.g.~covariances or
+variances). See Jacobucci, Grimm, and McArdle (2016) for more detail on
+RAM notation.
 
@@
 model in \pkg{lavaan}. As an example, below is the code for a one factor
-model fit in lavaan with the Holzinger-Swineford (Holzinger and
-Swineford 1939) dataset.
+model fit in lavaan with the Holzinger and Swineford (1939) dataset.
 
@@
 translate the model into RAM notation and run using one of three
-functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem}.
+functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem()}.
 The \code{regsem()} function runs a model with one penalty value,
@@
 factor loadings can be tested with lasso penalties to determine whether
-each indicator is a necessary component of the latent factor.
+each indicator is a necessary component of the latent factor:
 
@@
 The \code{out.reg} object contains two components, \code{out.reg[[1]]}
-has the parameter estimates for each of the 15 models, while
-\code{out.reg[[2]]} has the fit of each model. For the code above, using
-the \pkg{xtable} package to turn the output from \code{out.reg[[2]]}
-into a table
+has the parameter estimates for each of the 15 models,
 
@@
 \begin{CodeInput}
-round(out.reg[[2]],3)
+head(round(out.reg[[1]],2),5)
+\end{CodeInput}
+\begin{CodeOutput}
+     f1 -> x1 f1 -> x2 f1 -> x3 f1 -> x4 f1 -> x5 f1 -> x6 f1 -> x7
+[1,]     0.51     0.26     0.25     0.98     1.08     0.92     0.20
+[2,]     0.41     0.17     0.17     0.89     0.98     0.83     0.12
+[3,]     0.33     0.10     0.10     0.83     0.91     0.77     0.06
+[4,]     0.27     0.04     0.04     0.78     0.87     0.72     0.01
+[5,]     0.21     0.00     0.00     0.75     0.83     0.69     0.00
+     f1 -> x8 f1 -> x9 x1 ~~ x1 x2 ~~ x2 x3 ~~ x3 x4 ~~ x4 x5 ~~ x5
+[1,]     0.20     0.31     1.10     1.31     1.21     0.38     0.49
+[2,]     0.13     0.23     1.11     1.32     1.22     0.38     0.48
+[3,]     0.08     0.17     1.13     1.33     1.23     0.38     0.47
+[4,]     0.03     0.12     1.15     1.35     1.25     0.38     0.46
+[5,]     0.00     0.07     1.18     1.36     1.26     0.39     0.46
+     x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
+[1,]     0.36     1.15     0.98     0.92
+[2,]     0.36     1.15     0.99     0.93
+[3,]     0.36     1.16     1.00     0.94
+[4,]     0.37     1.17     1.01     0.96
+[5,]     0.38     1.18     1.02     0.97
+\end{CodeOutput}
+\end{CodeChunk}
+
+\noindent
+while \code{out.reg[[2]]} looks like:
+
+\begin{CodeChunk}
+\begin{CodeInput}
+round(out.reg[[2]],2)
 \end{CodeInput}
@@
       lambda conv rmsea     BIC
- [1,]   0.00    0 0.188 7805.177
- [2,]   0.05    0 0.191 7815.389
- [3,]   0.10    0 0.199 7840.590
- [4,]   0.15    0 0.210 7875.842
- [5,]   0.20    0 0.203 7886.147
- [6,]   0.25    0 0.210 7911.816
- [7,]   0.30    0 0.214 7934.454
- [8,]   0.35    0 0.220 7960.670
- [9,]   0.40    0 0.227 7991.033
-[10,]   0.45    0 0.229 8009.416
-[11,]   0.50    0 0.234 8034.805
-[12,]   0.55    0 0.242 8069.487
-[13,]   0.60    0 0.286 8360.539
-[14,]   0.65    0 0.286 8360.530
-[15,]   0.70    0 0.286 8360.525
+ [1,]   0.00    0  0.19 7805.18
+ [2,]   0.05    0  0.19 7815.39
+ [3,]   0.10    0  0.20 7840.59
+ [4,]   0.15    0  0.21 7875.84
+ [5,]   0.20    0  0.20 7886.15
+ [6,]   0.25    0  0.21 7911.82
+ [7,]   0.30    0  0.21 7934.45
+ [8,]   0.35    0  0.22 7960.67
+ [9,]   0.40    0  0.23 7991.03
+[10,]   0.45    0  0.23 8009.42
+[11,]   0.50    0  0.23 8034.81
+[12,]   0.55    0  0.24 8069.49
+[13,]   0.60    0  0.29 8360.54
+[14,]   0.65    0  0.29 8360.53
+[15,]   0.70    0  0.29 8360.52
 \end{CodeOutput}
@@
 In this, the user can examine the penalty (lambda), whether the model
-converged (``conv''), with values of 0 indicating convergence, and the
-fit of each model. By default, two fit indices are output, both the root
-mean square error of approximation (RMSEA; Steiger and Lind 1980), and
-the Bayesian information criteria (BIC; Schwarz 1978). Both the RMSEA
-and BIC take into account the degrees of freedom of the model, an
-important point for model selection in the presence of lasso penalties
-(and other penalties that set parameters to zero). This concurs with
-work done on degrees of freedom for lasso regression, as Zou, Hastie,
-and Tibshirani (2007) proved that the number of nonzero coefficients is
-an unbiased estimate of the degrees of freedom for regression. As the
-penalty increases, select parameter are set to zero, thus the degrees of
-freedom increases, which for fit indices that include the degrees of
-freedom in the calculation, means that although the likelihood of the
-model may only get worse (increase), both the RMSEA and BIC can improve
-(decrease) due to the impact of increased degrees of freedom.
+converged (``conv''=0), and the fit of each model. By default, two fit
+indices are output, both the root mean square error of approximation
+(RMSEA; Steiger and Lind 1980), and the Bayesian information criteria
+(BIC; Schwarz 1978). Both the RMSEA and BIC take into account the
+degrees of freedom of the model, an important point for model selection
+in the presence of lasso penalties (and other penalties that set
+parameters to zero). Based on work done on degrees of freedom for lasso
+regression, as Zou, Hastie, and Tibshirani (2007) proved that the number
+of nonzero coefficients is an unbiased estimate of the degrees of
+freedom for regression. As the penalty increases, select parameter are
+set to zero, thus the degrees of freedom increases, which for fit
+indices that include the degrees of freedom in the calculation, means
+that although the likelihood of the model may only get worse (increase),
+both the RMSEA and BIC can improve (decrease) due to the impact of
+increased degrees of freedom.
 
 Instead of examining the \code{out.reg[[1]]} output matrix of parameter
-estimates, it is easiest to plot the trajectory of each of the penalized
-parameters. This is accomplished with \code{plot_cv(out.reg,pars=1:9)},
-resulting in:
+estimates, users also have the option to plot the trajectory of each of
+the penalized parameters. This is accomplished with
+\code{plot_cv(out.reg,pars=1:9)}, resulting in:
 
@@
 
-\begin{center}\includegraphics{draft1_files/figure-latex/unnamed-chunk-5-1} \end{center}
+\begin{center}\includegraphics{draft1_files/figure-latex/unnamed-chunk-6-1} \end{center}
 
@@
 
-After a final model (penalty) is chosen, user's have the option either
+After a final model (penalty) is chosen, users have the option either
 just use the output from \code{cv_regsem()}, or the final model can be
@@
 To compare the different types of penalties in \pkg{regsem}, we return
-to the the initial example of the latent growth curve model. Using the
-same simulated data (see Appendix), the model can be run in \pkg{lavaan}
-as
+to the the initial example of the latent growth curve model displayed in
+Figure 1. Using the same simulated data, the model can be run in
+\pkg{lavaan} as
 
@@
 were penalized using the lasso, adaptive lasso, SCAD, and MCP, and
-compared to the maximum likelihood estimates (see Appendix for code). In
-this model, the data were simulated to have two large effects (both
-\textit{c1} parameters), two small effects (both \textit{c2} parameters)
-and sixteen true zero effects (\textit{c3-c10} parameters). Note that
-the covariates were simulated to have zero covariance among each
-variable. If there was substantial collinearity among covariates, the
-elastic net would be more appropriate to simultaneously select
-predictors while also accounting for the collinearity. The parameter
-estimates corresponding the the best fit of the BIC are displayed in
-Table *
+compared to the maximum likelihood estimates. In this model, the data
+were simulated to have two large effects (both \textit{c1} parameters),
+two small effects (both \textit{c2} parameters) and sixteen true zero
+effects (\textit{c3-c10} parameters). Note that the covariates were
+simulated to have zero covariance among each variable. If there was
+substantial collinearity among covariates, the elastic net would be more
+appropriate to simultaneously select predictors while also accounting
+for the collinearity. The parameter estimates corresponding the the best
+fit of the BIC are has the fit of each model, resulting in Table 1,
+created using the \pkg{xtable} package (Dahl 2009).
 
@@
 true effects was attentuated in comparison to the other regularization
-methods. This is in line with previous research (cite), necessitating
-the use of a two-step relaxed lasso method (Meinshausen 2007, see
-Jacobucci, Grimm, and McArdle (2016)) As expected given the small ratio
-between number of estimated parameters and sample size, maximum
-likelihood mistakenly identified 3 false effects as significant.
+methods. This is in line with previous research (Fan and Li 2001),
+necessitating the use of a two-step relaxed lasso method (Meinshausen
+2007, see Jacobucci, Grimm, and McArdle (2016)) As expected given the
+small ratio between number of estimated parameters and sample size,
+maximum likelihood mistakenly identified 3 false effects as significant.
 
@@
 regularization methods performs well regardless of sample size. Each run
-was replicated 200 times. The results are displayed in Table *
+was replicated 200 times. For each regularization method, the BIC was
+used to choose a final model among the 40 penalty vales. The results are
+displayed in Table 2.
 
@@
 \centering
-    \begin{tabular}{rrrrrrrr}
+\begin{tabular}{rrrrrrr}
   \hline
@@
   \hline
-         & 80.00 & 0.09 & 0.05 & \textbf{0.04} & 0.05 & 0.05 \\ 
-        False Positives & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.04 \\ 
-         & 1000.00 & 0.05 & 0.05 & \textbf{0.01} & \textbf{0.01} & 0.19 \\ 
-         & 80.00 & 0.45 & \textbf{0.41} & 0.43 & 0.45 & 0.54 \\ 
-        False Negatives & 200.00 & 0.30 & \textbf{0.24} & 0.29 & 0.29 & 0.45 \\ 
-         & 1000.00 & 0.10 & \textbf{0.09} & 0.17 & 0.19 & 0.24 \\ 
+1 & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & \textbf{0.04} \\ 
+  2 & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.03 \\ 
+  3 & 1000.00 & 0.05 & 0.08 & \textbf{0.01} & \textbf{0.01} & 0.28 \\ 
+  4 & 80.00 & 0.33 & \textbf{0.31} & 0.35 & 0.35 & 0.45 \\ 
+  5 & 200.00 & \textbf{0.19} & \textbf{0.19} & 0.23 & 0.26 & 0.45 \\ 
+  6 & 1000.00 & \textbf{0.00} & \textbf{0.00} & \textbf{0.00} & 0.01 & 0.14 \\ 
    \hline
@@
 
+For false positive, the adaptive lasso demonstrated the best
+performance, where the performance of maximum likelihood estimation
+leveled off at the 0.05 level at a sample size of 1000 as expected. For
+false negatives, lasso penalties demonstrated similar results to maximum
+likelihood. This was expected given the tendency of the lasso to
+under-penalize small coefficients in comparison to the other
+regularization methods. The adaptive lasso and SCAD demonstrated
+slightly worse results, however, outside of the MCP, each method made
+either zero or near zero errors at a sample size of 1000. The poor
+performance of the MCP may be in part due to fixing the \(\gamma\)
+penalty to 3.7. Varying this parameter may improve the performance of
+the method. In summary, the regularization methods demonstrated an
+improvement over maximum likelihood, particularly at small samples, for
+a model that had a large number of estimated parameters.
+
 \section{Discussion}\label{discussion}
@@
 equation modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) method
-and the usage of the package itself. RegSEM allows the use of
+and the usage of the \pkg{regsem} package. RegSEM allows the use of
 regularization while keeping the structural equation model intact,
@@
 integration between data mining methods and latent variable models.
-Specifically, beyond regularized SEM, this has taken form of item
-response theory and regularization (Sun et al. 2016), pairing both
-structural equation models with decision trees (Brandmaier et al. 2013),
-exploratory psychological network analaysis (e.g. Epskamp, Rhemtulla,
-and Borsboom 2016), along with many others. The amount of pairing
-between methods that have generally been housed in separate camps will
-only increase into the future. This type of research will be facilitated
-by the general upsurge in the creation of open source software that
-gives users a general framework to test models. This was the motivation
-behind creating the \pkg{regsem} package in that users can estimate
-models ranging from simple factor analysis models, to latent
-longitudinal models with few to many time points, and finally to models
-with a large number of latent and observed variables. The use of
-regularization allows for the estimation of much larger structural
-equation models than before. Specifically, given that latent variables,
-as discussed in this article, are more commonly used in the social and
-behavioral sciences, sample sizes are generally not large. To estimate
-large models with sample sizes invites increasing amounts of bias, and
-as demonstrated with the simulated data in this paper, regularization
-can be used to reduce the complexity of the model, decreasing both the
+Specifically, beyond RegSEM, this has taken form of item response theory
+and regularization (Sun et al. 2016), pairing both structural equation
+models with decision trees (Brandmaier et al. 2013), exploratory
+psychological network analaysis (e.g. Epskamp, Rhemtulla, and Borsboom
+2016), along with many others. The amount of pairing between methods
+that have generally been housed in separate camps will only increase
+into the future. This type of research will be facilitated by the
+general upsurge in the creation of open source software that gives users
+a general framework to test models. This was the motivation behind
+creating the \pkg{regsem} package in that users can estimate models
+ranging from simple factor analysis models, to latent longitudinal
+models with few to many time points, and finally to models with a large
+number of latent and observed variables. The use of regularization
+allows for the estimation of much larger structural equation models than
+before. Specifically, given that latent variables, as discussed in this
+article, are more commonly used in the social and behavioral sciences,
+sample sizes are generally not large. To estimate large models with
+small sample sizes invites increasing amounts of bias, and as
+demonstrated with the simulated data in this paper. Regularization can
+be used to reduce the complexity of the model, thus decreasing both the
 bias and variance.
@@
 advent of additional sparsity inducing priors, along with new forms of
-software such as STAN (Carpenter et al. 2016), for some models it may be
+software such as Stan (Carpenter et al. 2016), for some models it may be
 more appropriate to use these Bayesian regularization methods over their
-frequentist counterparts. Particularly with structural equation models,
-although some research exists (Feng, Wu, and Song 2017), much more is
-warranted.
+frequentist counterparts. In the realm of Bayesian regularization for
+structural equation models, although some research exists (Feng, Wu, and
+Song 2017), much more is warranted.
 
@@
 One is comparing the different forms of regularization, delineating
-which method may best best in which circumstances. Additionally, as
-structural equation models become larger, with the advent of much larger
-datasets, speed will become a principal concern. Although 40 penalties
-in the models tested above can be run in a matter of seconds on a
-standard laptop, larger models can take much longer. To handle this,
-future implementation with \pkg{regsem} will test the inclusion of
+which method may best best in which setting. Additionally, as structural
+equation models become larger, with the advent of much larger datasets,
+computational speed will become a principal concern. Although 40
+penalties in the models tested above can be run in a matter of seconds
+on a standard laptop, larger models can take much longer. To handle
+this, future implementation with \pkg{regsem} will test the inclusion of
 different types of optimization, specifically testing whether
@@
 package for including different forms of regularization into a host of
-latent variable models. Future updates to \pkg{regsem} will focus on
-decreasing the computational time of large latent variable models in
-order to provide an avenue of testing for researchers collecting larger
-and larger datasets. RegSEM is a method that operates at all ends of the
-data size spectrum: allowing for a reduction in complexity when the
-sample size is small, along with dimension reduction in the presence of
-large data (both \(N\) and \(P\)).
+latent variable models. RegSEM, and thus the \pkg{regsem} package, has
+been evaluated in a wide array of SEM models, including confirmatory
+factor analysis (Jacobucci, Grimm, and McArdle 2016), latent change
+score models (Jacobucci and Grimm 2017), mediation models (Serang et al.
+2017).Future updates to \pkg{regsem} will focus on decreasing the
+computational time of large latent variable models in order to provide
+an avenue of testing for researchers collecting larger and larger
+datasets. RegSEM is a method that operates at all ends of the data size
+spectrum: allowing for a reduction in complexity when the sample size is
+small, along with dimension reduction in the presence of large data
+(both \(N\) and \(P\)).
 
@@
 \emph{Journal of Statistical Software} 20.
+
+\hypertarget{ref-dahl2009xtable}{}
+Dahl, David B. 2009. ``Xtable: Export Tables to Latex or Html.'' \emph{R
+Package Version}, 1--5.
 
@@
 
+\hypertarget{ref-jacobucci2016package}{}
+Jacobucci, Ross. 2017. ``Package 'Regsem'.''
+\emph{Https://Cran.r-Project.org/Web/Packages/Regsem/Index.html}.
+
 \hypertarget{ref-jacobucci2016regularized}{}
@@
 
-\hypertarget{ref-McArdle_1984}{}
-McArdle, J. Jack, and Roderick P. McDonald. 1984. ``Some Algebraic
-Properties of the Reticular Action Model for Moment Structures.''
-\emph{British Journal of Mathematical and Statistical Psychology} 37
-(2). Wiley-Blackwell: 234--51.
-
 \hypertarget{ref-mcardle2005}{}
@@
 
+\hypertarget{ref-McArdle_1984}{}
+McArdle, John J., and Roderick P. McDonald. 1984. ``Some Algebraic
+Properties of the Reticular Action Model for Moment Structures.''
+\emph{British Journal of Mathematical and Statistical Psychology} 37
+(2). Wiley-Blackwell: 234--51.
+
 \hypertarget{ref-meinshausen2007relaxed}{}
@@
 Statistics \& Data Analysis} 52 (1). Elsevier: 374--93.
+
+\hypertarget{ref-meredith1990latent}{}
+Meredith, William, and John Tisak. 1990. ``Latent Curve Analysis.''
+\emph{Psychometrika} 55 (1). Springer: 107--22.
+
+\hypertarget{ref-statspackage}{}
+R Core Team. 2017. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
 
@@
 Statistics: 461--64.
+
+\hypertarget{ref-serang2017xmed}{}
+Serang, Sarfaraz, Ross Jacobucci, Kim Brimhall, and Kevin J Grimm. 2017.
+``Exploratory Mediation Analysis via Regularization.'' \emph{Structural
+Equation Modeling: A Multidisciplinary Journal}. Taylor \& Francis.
 

### 2017-03-14 draft1.Rmd
sarfaraz comments
add sarfaraz comments

@@
 The desire for simplicity in model structure comes by many names, including simple structure [@thurstone1937], variable complexity [@browne2001], parsimony [@raykov1999desirability; @marsh1996assessing], "sparse loadings" in the context of principal components analysis [@zou2006sparse], and lastly, "sparsistency", denoting that all parameters in a sparse model that are zero are correctly estimated as zero with probability tending to one [@lam2009sparsistency].
-The goal is accurately and efficiently estimate a model that is parsimonious in allowing users to easily interpret the model's representation of reality.
+The goal is to accurately and efficiently estimate a model that is parsimonious in allowing users to easily interpret the model's representation of reality.
 In the context of latent variables, reducing the complexity of models can come in many forms: selecting among multiple predictors of a latent variable, simplifying factor structure by removing cross-loadings, determining whether the addition of nonlinear terms are necessary in longitudinal models, and many others.
@@
 In lieu of finding additional respondents, reducing the number of parameters estimated is one effective strategy for reducing bias.
-Specifically, the 20 estimated regressions from \textit{c1-c10} could be reduced to a number that makes the number of parameters estimated to sample size ratio more reasonable.
+Specifically, the 20 estimated regressions from \textit{c1-c10} could be reduced to a number that makes the ratio of the parameters estimated to sample size more reasonable.
 To explore this further, the next section provides an overview of regularization, and how different forms can be used to perform variable selection across a broad range of models.
@@
 Henceforth, $\lambda$ is assumed to encompass both the penalty and the step size $s^{t}$.
-This procedure is only used to updated parameters that are subject to penalty.
+This procedure is only used to update parameters that are subject to penalty.
 Non-penalized parameters are updated only using step 1 from above.
@@
 for $\gamma > 2$.
-As the the penalty in equation 11 is non-convex (as is the MCP), this makes computation more difficult.
+As the the penalty in equation 11 is non-convex (as is the MCP), this makes the computation more difficult.
 However, in the context of SEM this can be seen as less problematic, as equation 3 is also non-convex.
@@
 To use \pkg{regsem}, the user has to first fit the model in \pkg{lavaan}.
-As an example, below is the code for a one factor model fit in lavaan with the @holzinger1939study dataset.
+Note that particularly in cases that the number of variables is larger than the sample size, the model in lavaan does not need to converge, let alone run.
+In this case, the \code{do.fit=FALSE} argument in lavaan can be used.
+###maybe move previous sentences### Below is the code for a one factor model fit in lavaan with the @holzinger1939study dataset.
 
@@
   \hline
-1 & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & \textbf{0.04} \\ 
-  2 & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.03 \\ 
-  3 & 1000.00 & 0.05 & 0.08 & \textbf{0.01} & \textbf{0.01} & 0.28 \\ 
-  4 & 80.00 & 0.33 & \textbf{0.31} & 0.35 & 0.35 & 0.45 \\ 
-  5 & 200.00 & \textbf{0.19} & \textbf{0.19} & 0.23 & 0.26 & 0.45 \\ 
-  6 & 1000.00 & \textbf{0.00} & \textbf{0.00} & \textbf{0.00} & 0.01 & 0.14 \\ 
+ & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & \textbf{0.20} \\ 
+  False Positives & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.06 \\ 
+   & 1000.00 & 0.05 & 0.08 & \textbf{0.01} & \textbf{0.01} & 0.02 \\ 
+   & 80.00 & 0.33 & \textbf{0.31} & 0.35 & 0.35 & 0.31 \\ 
+  False Negatives & 200.00 & \textbf{0.19} & \textbf{0.19} & 0.23 & 0.26 & 0.27 \\ 
+   & 1000.00 & \textbf{0.00} & \textbf{0.00} & \textbf{0.00} & 0.01 & 0.03 \\ 
    \hline
@@
 Broadly speaking, there is a growing amount of research into the integration between data mining methods and latent variable models.
-Specifically, beyond RegSEM, this has taken form of item response theory and regularization [@sun2016latent], pairing both structural equation models with decision trees [@brandmaier2013], exploratory psychological network analaysis [e.g.
+Specifically, beyond RegSEM, this has taken the form of item response theory and regularization [@sun2016latent], pairing both structural equation models with decision trees [@brandmaier2013], exploratory psychological network analaysis [e.g.
 @epskamp2016generalized], along with many others.
@@
 Future research with \pkg{regsem} should focus on a number of avenues.
-One is comparing the different forms of regularization, delineating which method may best best in which setting.
+One is comparing the different forms of regularization, delineating which method may be best in which setting.
 Additionally, as structural equation models become larger, with the advent of much larger datasets, computational speed will become a principal concern.
@@
 Because structural equation modeling encompasses a wide array of latent variable models, the \pkg{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.
-RegSEM, and thus the \pkg{regsem} package, has been evaluated in a wide array of SEM models, including confirmatory factor analysis [@jacobucci2016regularized], latent change score models (Jacobucci and Grimm 2017), mediation models [@serang2017xmed].Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
+RegSEM, and thus the \pkg{regsem} package, has been evaluated in a wide array of SEM models, including confirmatory factor analysis [@jacobucci2016regularized], latent change score models (Jacobucci and Grimm 2017), mediation models [@serang2017xmed].
+Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
 RegSEM is a method that operates at all ends of the data size spectrum: allowing for a reduction in complexity when the sample size is small, along with  dimension reduction in the presence of large data (both $N$ and $P$).

### 2017-03-14 draft1.tex
add sarfaraz comments

@@
 correctly estimated as zero with probability tending to one (Lam and Fan
-2009). The goal is accurately and efficiently estimate a model that is
-parsimonious in allowing users to easily interpret the model's
+2009). The goal is to accurately and efficiently estimate a model that
+is parsimonious in allowing users to easily interpret the model's
 representation of reality. In the context of latent variables, reducing
@@
 regressions from \textit{c1-c10} could be reduced to a number that makes
-the number of parameters estimated to sample size ratio more reasonable.
-To explore this further, the next section provides an overview of
+the ratio of the parameters estimated to sample size more reasonable. To
+explore this further, the next section provides an overview of
 regularization, and how different forms can be used to perform variable
@@
 size. Henceforth, \(\lambda\) is assumed to encompass both the penalty
-and the step size \(s^{t}\). This procedure is only used to updated
+and the step size \(s^{t}\). This procedure is only used to update
 parameters that are subject to penalty. Non-penalized parameters are
@@
 for \(\gamma > 2\). As the the penalty in equation 11 is non-convex (as
-is the MCP), this makes computation more difficult. However, in the
+is the MCP), this makes the computation more difficult. However, in the
 context of SEM this can be seen as less problematic, as equation 3 is
@@
 estimation methods. To use \pkg{regsem}, the user has to first fit the
-model in \pkg{lavaan}. As an example, below is the code for a one factor
-model fit in lavaan with the Holzinger and Swineford (1939) dataset.
+model in \pkg{lavaan}. Note that particularly in cases that the number
+of variables is larger than the sample size, the model in lavaan does
+not need to converge, let alone run. In this case, the
+\code{do.fit=FALSE} argument in lavaan can be used. \#\#\#maybe move
+previous sentences\#\#\# Below is the code for a one factor model fit in
+lavaan with the Holzinger and Swineford (1939) dataset.
 
@@
 integration between data mining methods and latent variable models.
-Specifically, beyond RegSEM, this has taken form of item response theory
-and regularization (Sun et al. 2016), pairing both structural equation
-models with decision trees (Brandmaier et al. 2013), exploratory
-psychological network analaysis (e.g. Epskamp, Rhemtulla, and Borsboom
-2016), along with many others. The amount of pairing between methods
-that have generally been housed in separate camps will only increase
-into the future. This type of research will be facilitated by the
-general upsurge in the creation of open source software that gives users
-a general framework to test models. This was the motivation behind
-creating the \pkg{regsem} package in that users can estimate models
-ranging from simple factor analysis models, to latent longitudinal
-models with few to many time points, and finally to models with a large
-number of latent and observed variables. The use of regularization
-allows for the estimation of much larger structural equation models than
-before. Specifically, given that latent variables, as discussed in this
-article, are more commonly used in the social and behavioral sciences,
-sample sizes are generally not large. To estimate large models with
-small sample sizes invites increasing amounts of bias, and as
-demonstrated with the simulated data in this paper. Regularization can
-be used to reduce the complexity of the model, thus decreasing both the
-bias and variance.
+Specifically, beyond RegSEM, this has taken the form of item response
+theory and regularization (Sun et al. 2016), pairing both structural
+equation models with decision trees (Brandmaier et al. 2013),
+exploratory psychological network analaysis (e.g. Epskamp, Rhemtulla,
+and Borsboom 2016), along with many others. The amount of pairing
+between methods that have generally been housed in separate camps will
+only increase into the future. This type of research will be facilitated
+by the general upsurge in the creation of open source software that
+gives users a general framework to test models. This was the motivation
+behind creating the \pkg{regsem} package in that users can estimate
+models ranging from simple factor analysis models, to latent
+longitudinal models with few to many time points, and finally to models
+with a large number of latent and observed variables. The use of
+regularization allows for the estimation of much larger structural
+equation models than before. Specifically, given that latent variables,
+as discussed in this article, are more commonly used in the social and
+behavioral sciences, sample sizes are generally not large. To estimate
+large models with small sample sizes invites increasing amounts of bias,
+and as demonstrated with the simulated data in this paper.
+Regularization can be used to reduce the complexity of the model, thus
+decreasing both the bias and variance.
 
@@
 One is comparing the different forms of regularization, delineating
-which method may best best in which setting. Additionally, as structural
+which method may be best in which setting. Additionally, as structural
 equation models become larger, with the advent of much larger datasets,
@@
 score models (Jacobucci and Grimm 2017), mediation models (Serang et al.
-2017).Future updates to \pkg{regsem} will focus on decreasing the
+2017). Future updates to \pkg{regsem} will focus on decreasing the
 computational time of large latent variable models in order to provide

### 2017-03-22 draft1.Rmd
revision

@@
 abstract: >
-  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
+  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
 The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996], along with sparser extensions.
 RegSEM is particularly useful for structural equation models that have a small parameter to sample size ratio, as the addition of penalties can reduce the complexity, thus reducing the bias of the parameter estimates.
-The paper details the algorithmic details and an overview of the use of \pkg{regsem} with the application of both factor analysis and latent growth curve models.
+The paper covers the algorithmic details and an overview of the use of \pkg{regsem} with the application of both factor analysis and latent growth curve models.
 keywords:
@@
 ---
-\setlength\parindent{24pt}
-\setlength{\parskip}{0.5em}
 
@@
 In the context of latent variables, reducing the complexity of models can come in many forms: selecting among multiple predictors of a latent variable, simplifying factor structure by removing cross-loadings, determining whether the addition of nonlinear terms are necessary in longitudinal models, and many others.
-As a simple running example, Figure 1 depicts a linear latent growth curve model [e.g.
-@meredith1990latent] with four time points and ten predictors for a simulated dataset.
 
@@
 
-As an example, a researcher may want to test this model, but may only have a relatively small sample size (e.g.
+As a simple running example, Figure 1 depicts a linear latent growth curve model [e.g.
+@meredith1990latent] with four time points and ten predictors for a simulated dataset.
+In this, a researcher may want to test this model, but may only have a relatively small sample size (e.g.
 80).
-However, there are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio as far below even the most liberal recommendations [e.g.
+There are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio as far below even the most liberal recommendations [e.g.
 10:1 parameters to sample size; @kline2015principles].
@@
 The two most common procedures for regularization in regression are the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996]; however, there are various alternative forms that can be seen as subsets or generalizations of these two procedures.
-Given an outcome vector \textit{y} and predictor matrix $X \in {R}^{n \times p}$ , the ridge estimates are defined as
+Given an outcome vector \textit{y} and predictor matrix $X \in {R}^{n \times p}$ , ridge estimates are defined as
 
@@
 $$
-\noindent
+
 where $\beta_{0}$ is the intercept, $\beta_{j}$ is the coefficient for $x_{j}$, and $\lambda$ is the penalty that controls the amount of shrinkage.
@@
 
-\noindent
 In lasso regression, the $l_{1}$-norm is used, instead of $l_{2}$-norm as in ridge, which also shrinks the $\beta$ parameters, but additionally drives the parameters all the way to zero, thus performing a form of subset selection.
@@
 
-\noindent
 where $\Sigma$ is the model implied covariance matrix, $C$ is the observed covariance matrix, and $p$ is the number of estimated parameters.
@@
 
-\noindent
 where $\lambda$ is the regularization parameter and takes on a value between zero and infinity.
@@
 $P(\cdot)$ is a general function for summing the values of one or more of the model's parameter matrices.
-The two common forms of $P(\cdot)$ include both the lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.
+Two common forms of $P(\cdot)$ include both the lasso ($\| \cdot \|_{1}$), which penalizes the sum of the absolute values of the parameters, and ridge ($\| \cdot \|_{2}$), which penalizes the sum of the squared values of the parameters.
 
@@
 $$
-\noindent
+
 Although the fit of the model is easily calculated given a set of parameter estimates, traditional optimization procedures for SEM cannot be used given the non-differentiable nature of lasso penalties, and as detailed later, sparse extensions.
@@
 \begin{equation}
-S_{s^{t} \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-s^{t} \lambda)_{+}
+S_{s^{t} \lambda}(z_{j}) = sign(\theta_{j})(|\theta_{j}|-s^{t} \lambda)_{+}
 \end{equation}
-\noindent
+
 where $(x)_{+}$ is shorthand for max(x,0) and $s^{t}$ is the step size.
@@
 
-In contrast to only updating one parameter at a time in a coordinate-wise fashion, for RegSEM the optimization steps can be divided by both the \textit{A} and \textit{S} matrices.
+In contrast to only updating one parameter at a time in a coordinate-wise fashion, for RegSEM the optimization steps can be divided by both the \textit{A} and \textit{S} matrices (see the Implementation section for more description on the RAM matrices).
 This block-wise gradient descent manifests itself as:
 
-\noindent\begin{minipage}{\textwidth}
+\begin{minipage}{\textwidth}
 	%	\renewcommand\footnoterule{}    
@@
 \end{minipage}
-\noindent
+
 where step 13 is the calculation of the implied covariance matrix using RAM matrices and step 14 calculates the fit of the model with penalizing parameters in the \textit{A} matrix.
@@
 
-\noindent
 When $\alpha$ is zero, ridge is performed, and conversely when $\alpha$ is 1, lasso regularization is performed.
@@
 $$
-\noindent
+
 with, following the same form for the lasso, the soft-thresholding update is:
@@
 $$
-\noindent
+
 In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant parameters.
@@
 
-\noindent
 with a soft-thresholding update of
@@
 
-\noindent
 for $\gamma > 2$.
@@
 
-@zhang2010nearly proposed the minimax concave penalty:
+A final regularization method developed to produce sparser penalties than the lasso was the minimax concave penalty [MCP,@zhang2010nearly]:
 
@@
 
-\noindent
 for $\gamma > 0$.
@@
 For both the SCAD and MCP, both the $\gamma$ and $\lambda$ parameters are used as hyper-parameters.
-This involves testing models over a two-dimensional array of parameters, however, $\gamma$ can be fixed to 3.7 per @fan2001variable.
+This involves testing models over a two-dimensional array of parameters, however, in \pkg{regsem}, $\gamma$ is by default fixed to 3.7 per @fan2001variable.
 
@@
 In this case, the \code{do.fit=FALSE} argument in lavaan can be used.
-###maybe move previous sentences### Below is the code for a one factor model fit in lavaan with the @holzinger1939study dataset.
+As a canonical example, below is the code for a confirmatory factor analysis model with one latent factor and nince indicators from the @holzinger1939study dataset.
 
@@
 
-\noindent
-while \code{out.reg[[2]]} looks like:
+while \code{out.reg[[2]]} contains information pertaining to the fit of each model:
 
@@
 Both the RMSEA and BIC take into account the degrees of freedom of the model, an important point for model selection in the presence of lasso penalties (and other penalties that set parameters to zero).
-Based on work done on degrees of freedom for lasso regression, as @Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression.
-As the penalty increases, select parameter are set to zero, thus the degrees of freedom increases, which for fit indices that include the degrees of freedom in the calculation, means that although the likelihood of the model may only get worse (increase), both the RMSEA and BIC can improve (decrease) due to the impact of increased degrees of freedom.
+@Zou2007 proved that the number of nonzero coefficients is an unbiased estimate of the degrees of freedom for regression.
+As the penalty increases, select parameters are set to zero, thus increasing the degrees of freedom, which for fit indices that include the degrees of freedom in the calculation, means that although the likelihood of the model may only get worse (increase), both the RMSEA and BIC can improve (decrease).
 
@@
 ```
-\noindent
-These same fit measures can be accessed through \code{cv_regsem}, through changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
+
+These same fit measures can be accessed through \code{cv_regsem} through changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
 Finally, instead of assessing these fit indices on the same sample that the models were run on, a holdout dataset could be used.
@@
 
-To compare different types of penalties in \pkg{regsem}, it requires a different specification of the \code{type} argument.
+Comparing different types of penalties in \pkg{regsem} requires a different specification of the \code{type} argument.
 The options currently include maximum likelihood (\code{"none"}), ridge (\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso (\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}), and MCP (\code{"mcp"}).
@@
 
-To compare the performance of each penalization method further, particularly in the presence of small number of parameters to sample size ratios, a small scale simulation study was conducted.
+To compare the performance of each penalization method further, particularly in the presence of a small parameter to sample size ratio, a small simulation study was conducted.
 The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size.
@@
   \hline
- & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & \textbf{0.20} \\ 
+ & 80.00 & 0.08 & 0.08 & \textbf{0.04} & 0.05 & 0.20 \\ 
   False Positives & 200.00 & 0.06 & 0.05 & \textbf{0.02} & 0.03 & 0.06 \\ 
@@
 
-For false positive, the adaptive lasso demonstrated the best performance, where the performance of maximum likelihood estimation leveled off at the 0.05 level at a sample size of 1000 as expected.
+For false positives, the adaptive lasso demonstrated the best performance, where the performance of maximum likelihood estimation leveled off at the 0.05 level at a sample size of 1000 as expected.
 For false negatives, lasso penalties demonstrated similar results to maximum likelihood.
@@
 Specifically, given that latent variables, as discussed in this article, are more commonly used in the social and behavioral sciences, sample sizes are generally not large.
-To estimate large models with small sample sizes invites increasing amounts of bias, and as demonstrated with the simulated data in this paper.
+To estimate large models with small sample sizes invites increasing amounts of bias as demonstrated with the simulated data in this paper.
 Regularization can be used to reduce the complexity of the model, thus decreasing both the bias and variance.
@@
 
-This paper provided a brief overview on the use of the \pkg{regsem} package as an implementation of regularized structural equation model.
+This paper provided a brief overview on the use of the \pkg{regsem} package as an implementation of regularized structural equation modeling.
 Because structural equation modeling encompasses a wide array of latent variable models, the \pkg{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.

### 2017-03-22 draft1.tex
revision

@@
 regularized structural equation modeling (RegSEM; Jacobucci, Grimm, and
-McArdle 2016), was recently developed with the goal incorporating
+McArdle 2016), was recently developed with the goal of incorporating
 various forms of penalized likelihood estimation with a broad array of
@@
 ratio, as the addition of penalties can reduce the complexity, thus
-reducing the bias of the parameter estimates. The paper details the
+reducing the bias of the parameter estimates. The paper covers the
 algorithmic details and an overview of the use of \pkg{regsem} with the
@@
 
-\setlength\parindent{24pt} \setlength{\parskip}{0.5em}
-
 \section{Introduction}\label{introduction}
@@
 nonlinear terms are necessary in longitudinal models, and many others.
-As a simple running example, Figure 1 depicts a linear latent growth
-curve model (e.g. Meredith and Tisak 1990) with four time points and ten
-predictors for a simulated dataset.
 
@@
 
-As an example, a researcher may want to test this model, but may only
-have a relatively small sample size (e.g.~80). However, there are 29
-estimated parameters in this model, resulting in a estimated parameter
-to sample size ratio as far below even the most liberal recommendations
-(e.g.~10:1 parameters to sample size; Kline 2015). In lieu of finding
-additional respondents, reducing the number of parameters estimated is
-one effective strategy for reducing bias. Specifically, the 20 estimated
-regressions from \textit{c1-c10} could be reduced to a number that makes
-the ratio of the parameters estimated to sample size more reasonable. To
-explore this further, the next section provides an overview of
-regularization, and how different forms can be used to perform variable
-selection across a broad range of models.
+As a simple running example, Figure 1 depicts a linear latent growth
+curve model (e.g. Meredith and Tisak 1990) with four time points and ten
+predictors for a simulated dataset. In this, a researcher may want to
+test this model, but may only have a relatively small sample size
+(e.g.~80). There are 29 estimated parameters in this model, resulting in
+a estimated parameter to sample size ratio as far below even the most
+liberal recommendations (e.g.~10:1 parameters to sample size; Kline
+2015). In lieu of finding additional respondents, reducing the number of
+parameters estimated is one effective strategy for reducing bias.
+Specifically, the 20 estimated regressions from \textit{c1-c10} could be
+reduced to a number that makes the ratio of the parameters estimated to
+sample size more reasonable. To explore this further, the next section
+provides an overview of regularization, and how different forms can be
+used to perform variable selection across a broad range of models.
 
@@
 these two procedures. Given an outcome vector \textit{y} and predictor
-matrix \(X \in {R}^{n \times p}\) , the ridge estimates are defined as
+matrix \(X \in {R}^{n \times p}\) , ridge estimates are defined as
 
@@
 \hat{\beta}^{ridge}= argmin \Big\{ \sum_{i=1}^{N} (y_{i} = \beta_{0} - \sum_{j=1}^{p}x_{ij} \beta_{j})^{2}  + \lambda \sum_{j=1}^{p} \beta_{j}^{2}\Big\},
-\] \noindent
+\]
+
 where \(\beta_{0}\) is the intercept, \(\beta_{j}\) is the coefficient
@@
 
-\noindent
 In lasso regression, the \(l_{1}\)-norm is used, instead of
@@
 
-\noindent
 where \(\Sigma\) is the model implied covariance matrix, \(C\) is the
@@
 
-\noindent
 where \(\lambda\) is the regularization parameter and takes on a value
@@
 zero. \(P(\cdot)\) is a general function for summing the values of one
-or more of the model's parameter matrices. The two common forms of
+or more of the model's parameter matrices. Two common forms of
 \(P(\cdot)\) include both the lasso (\(\| \cdot \|_{1}\)), which
@@
 \end{matrix}  \right\|_{1}
-\] \noindent
+\]
+
 Although the fit of the model is easily calculated given a set of
@@
 \begin{equation}
-S_{s^{t} \lambda}(z_{j}) = sign(z_{j})(|z_{j}|-s^{t} \lambda)_{+}
+S_{s^{t} \lambda}(z_{j}) = sign(\theta_{j})(|\theta_{j}|-s^{t} \lambda)_{+}
 \end{equation}
 
-\noindent
 where \((x)_{+}\) is shorthand for max(x,0) and \(s^{t}\) is the step
@@
 coordinate-wise fashion, for RegSEM the optimization steps can be
-divided by both the \textit{A} and \textit{S} matrices. This block-wise
-gradient descent manifests itself as:
-
-\noindent
+divided by both the \textit{A} and \textit{S} matrices (see the
+Implementation section for more description on the RAM matrices). This
+block-wise gradient descent manifests itself as:
 
@@
 
-\noindent
 where step 13 is the calculation of the implied covariance matrix using
@@
 
-\noindent
 When \(\alpha\) is zero, ridge is performed, and conversely when
@@
 F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
-\] \noindent
+\]
+
 with, following the same form for the lasso, the soft-thresholding
@@
 S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
-\] \noindent
+\]
+
 In this, larger penalties are given for non-significant (smaller)
@@
 
-\noindent
 with a soft-thresholding update of \[
@@
 
-\noindent
 for \(\gamma > 2\). As the the penalty in equation 11 is non-convex (as
@@
 
-Zhang (2010) proposed the minimax concave penalty:
+A final regularization method developed to produce sparser penalties
+than the lasso was the minimax concave penalty (MCP, Zhang 2010):
 
@@
 
-\noindent
 for \(\gamma > 0\). As seen in Figure 2, this results in similar amount
@@
 involves testing models over a two-dimensional array of parameters,
-however, \(\gamma\) can be fixed to 3.7 per Fan and Li (2001).
+however, in \pkg{regsem}, \(\gamma\) is by default fixed to 3.7 per Fan
+and Li (2001).
 
@@
 not need to converge, let alone run. In this case, the
-\code{do.fit=FALSE} argument in lavaan can be used. \#\#\#maybe move
-previous sentences\#\#\# Below is the code for a one factor model fit in
-lavaan with the Holzinger and Swineford (1939) dataset.
+\code{do.fit=FALSE} argument in lavaan can be used. As a canonical
+example, below is the code for a confirmatory factor analysis model with
+one latent factor and nince indicators from the Holzinger and Swineford
+(1939) dataset.
 
@@
 [4,]     0.03     0.12     1.15     1.35     1.25     0.38     0.46
-[5,]     0.00     0.07     1.18     1.36     1.26     0.39     0.46
+[5,]     0.00     0.07     1.18     1.37     1.26     0.39     0.46
      x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
@@
 
-\noindent
-while \code{out.reg[[2]]} looks like:
+while \code{out.reg[[2]]} contains information pertaining to the fit of
+each model:
 
@@
  [2,]   0.05    0  0.19 7815.39
- [3,]   0.10    0  0.20 7840.59
- [4,]   0.15    0  0.21 7875.84
- [5,]   0.20    0  0.20 7886.15
- [6,]   0.25    0  0.21 7911.82
- [7,]   0.30    0  0.21 7934.45
- [8,]   0.35    0  0.22 7960.67
- [9,]   0.40    0  0.23 7991.03
-[10,]   0.45    0  0.23 8009.42
-[11,]   0.50    0  0.23 8034.81
-[12,]   0.55    0  0.24 8069.49
-[13,]   0.60    0  0.29 8360.54
+ [3,]   0.10    0  0.20 7840.40
+ [4,]   0.15    0  0.21 7875.41
+ [5,]   0.20    0  0.20 7885.68
+ [6,]   0.25    0  0.21 7910.92
+ [7,]   0.30    0  0.21 7933.99
+ [8,]   0.35    0  0.22 7960.28
+ [9,]   0.40    0  0.23 7990.80
+[10,]   0.45    0  0.23 8007.95
+[11,]   0.50    0  0.23 8034.00
+[12,]   0.55    0  0.24 8069.15
+[13,]   0.60    0  0.29 8360.53
 [14,]   0.65    0  0.29 8360.53
-[15,]   0.70    0  0.29 8360.52
+[15,]   0.70    0  0.29 8360.51
 \end{CodeOutput}
@@
 in the presence of lasso penalties (and other penalties that set
-parameters to zero). Based on work done on degrees of freedom for lasso
-regression, as Zou, Hastie, and Tibshirani (2007) proved that the number
-of nonzero coefficients is an unbiased estimate of the degrees of
-freedom for regression. As the penalty increases, select parameter are
-set to zero, thus the degrees of freedom increases, which for fit
+parameters to zero). Zou, Hastie, and Tibshirani (2007) proved that the
+number of nonzero coefficients is an unbiased estimate of the degrees of
+freedom for regression. As the penalty increases, select parameters are
+set to zero, thus increasing the degrees of freedom, which for fit
 indices that include the degrees of freedom in the calculation, means
 that although the likelihood of the model may only get worse (increase),
-both the RMSEA and BIC can improve (decrease) due to the impact of
-increased degrees of freedom.
+both the RMSEA and BIC can improve (decrease).
 
@@
 
-\noindent
-These same fit measures can be accessed through \code{cv_regsem},
-through changing the defaults with the \code{fit.ret=c("rmsea","BIC")}
-argument. Finally, instead of assessing these fit indices on the same
-sample that the models were run on, a holdout dataset could be used.
-This can be done two ways: either with
-\code{cv_regsem(...,fit.ret2="test")} or with
+These same fit measures can be accessed through \code{cv_regsem} through
+changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
+Finally, instead of assessing these fit indices on the same sample that
+the models were run on, a holdout dataset could be used. This can be
+done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with
 \code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the
@@
 
-To compare different types of penalties in \pkg{regsem}, it requires a
+Comparing different types of penalties in \pkg{regsem} requires a
 different specification of the \code{type} argument. The options
@@
 To compare the performance of each penalization method further,
-particularly in the presence of small number of parameters to sample
-size ratios, a small scale simulation study was conducted. The same
-model and effects was kept, but the sample size was varied to include
-80, 200, and 1000 to demonstrate how maximum likelihood estimation of
-effects improves as sample size increases, while each of the
-regularization methods performs well regardless of sample size. Each run
-was replicated 200 times. For each regularization method, the BIC was
-used to choose a final model among the 40 penalty vales. The results are
-displayed in Table 2.
+particularly in the presence of a small parameter to sample size ratio,
+a small simulation study was conducted. The same model and effects was
+kept, but the sample size was varied to include 80, 200, and 1000 to
+demonstrate how maximum likelihood estimation of effects improves as
+sample size increases, while each of the regularization methods performs
+well regardless of sample size. Each run was replicated 200 times. For
+each regularization method, the BIC was used to choose a final model
+among the 40 penalty vales. The results are displayed in Table 2.
 
@@
 
-For false positive, the adaptive lasso demonstrated the best
+For false positives, the adaptive lasso demonstrated the best
 performance, where the performance of maximum likelihood estimation
@@
 behavioral sciences, sample sizes are generally not large. To estimate
-large models with small sample sizes invites increasing amounts of bias,
-and as demonstrated with the simulated data in this paper.
-Regularization can be used to reduce the complexity of the model, thus
-decreasing both the bias and variance.
+large models with small sample sizes invites increasing amounts of bias
+as demonstrated with the simulated data in this paper. Regularization
+can be used to reduce the complexity of the model, thus decreasing both
+the bias and variance.
 
@@
 This paper provided a brief overview on the use of the \pkg{regsem}
-package as an implementation of regularized structural equation model.
-Because structural equation modeling encompasses a wide array of latent
-variable models, the \pkg{regsem} package was created as a general
-package for including different forms of regularization into a host of
-latent variable models. RegSEM, and thus the \pkg{regsem} package, has
-been evaluated in a wide array of SEM models, including confirmatory
-factor analysis (Jacobucci, Grimm, and McArdle 2016), latent change
-score models (Jacobucci and Grimm 2017), mediation models (Serang et al.
-2017). Future updates to \pkg{regsem} will focus on decreasing the
-computational time of large latent variable models in order to provide
-an avenue of testing for researchers collecting larger and larger
-datasets. RegSEM is a method that operates at all ends of the data size
-spectrum: allowing for a reduction in complexity when the sample size is
-small, along with dimension reduction in the presence of large data
-(both \(N\) and \(P\)).
+package as an implementation of regularized structural equation
+modeling. Because structural equation modeling encompasses a wide array
+of latent variable models, the \pkg{regsem} package was created as a
+general package for including different forms of regularization into a
+host of latent variable models. RegSEM, and thus the \pkg{regsem}
+package, has been evaluated in a wide array of SEM models, including
+confirmatory factor analysis (Jacobucci, Grimm, and McArdle 2016),
+latent change score models (Jacobucci and Grimm 2017), mediation models
+(Serang et al. 2017). Future updates to \pkg{regsem} will focus on
+decreasing the computational time of large latent variable models in
+order to provide an avenue of testing for researchers collecting larger
+and larger datasets. RegSEM is a method that operates at all ends of the
+data size spectrum: allowing for a reduction in complexity when the
+sample size is small, along with dimension reduction in the presence of
+large data (both \(N\) and \(P\)).
 

### 2017-03-24 draft1.Rmd
final first draft

@@
 abstract: >
-  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation with a broad array of structural equations models.
+  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation in a broad array of structural equations models.
 The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996], along with sparser extensions.
@@
 80).
-There are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio as far below even the most liberal recommendations [e.g.
+There are 29 estimated parameters in this model, resulting in a estimated parameter to sample size ratio far below even the most liberal recommendations [e.g.
 10:1 parameters to sample size; @kline2015principles].
@@
 
-Although a whole host of methods exist to perform variable selection, the use of regularization has seen a wide array of application in the context of regression, and more recently, in areas such as graphical modeling, as well as a host of others.
+Although a host of methods exist to perform variable selection, the use of regularization has seen a wide array of application in the context of regression, and more recently, in areas such as graphical modeling, as well as a host of others.
 The two most common procedures for regularization in regression are the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996]; however, there are various alternative forms that can be seen as subsets or generalizations of these two procedures.
@@
 
-In the context of our example depicted in Figure 1, to use lasso regression to select among the covariates, the growth model would need to be reduced to two factor scores, which neglects both the relationship between both the slope and intercept, reducing both to independent factor scores.
+In the context of our example depicted in Figure 1, to use lasso regression to select among the covariates, the growth model would need to be reduced to two factor scores, which neglects both the relationship between both the slope and intercept, reducing both to independent variables.
 Particularly in models with a greater number of latent variables, this becomes increasingly problematic.
@@
 			\State Calculate initial fit $F_{t}$
-			\State Set step size $s$. .1 works well at this time.
+			\State Set step size $s$. 0.1 works well at this time.
 			\State Set tolerance (tol). e.g. 1e-6
@@
 
-Outside of both ridge and lasso penalties, a whole host of additional forms of regularization exist.
+Outside of both ridge and lasso penalties, a host of additional forms of regularization exist.
 
@@
 $$
-P_{enet}(\theta_{j}) = 0.5(1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{2}
+P_{enet}(\theta_{j}) = (1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{1}
 $$
@@
 
-## Smoothly Clipped Absolute Deviation Penalty
+## Sparse Extensionse
 [\\]: High dimensional statistics p. 32
@@
 
-## Minimax Concave Penalty
-
-A final regularization method developed to produce sparser penalties than the lasso was the minimax concave penalty [MCP,@zhang2010nearly]:
+Additionally, the MCP takes the form of:
 
@@
 RegSEM is implemented as the \pkg{regsem} package [@jacobucci2016package] in the \proglang{R} statistical environment [@statspackage].
-To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984, @mcardle2005] notation to derive an implied covariance matrix.
+To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984; @mcardle2005] notation to derive an implied covariance matrix.
 The parameters of each SEM are translated into three matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths; e.g.
@@
 covariances or variances).
-See @jacobucci2016regularized for more detail on RAM notation.
+See @jacobucci2016regularized for more detail on RAM notation and its application to RegsEm.
 
@@
 This can be done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with \code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the holdout covariance matrix.
+
+Structural equation modeling is hard, and pairing with regularization doesn't make it any easier.
+Given this, and the number of options available in the \pkg{regsem} package, a Google group forum was created in order to answer questions and trouble shoot at https://groups.google.com/forum/#!forum/regsem.
 
@@
   \hline
- & ML & lasso & alasso & SCAD & MCP \\ 
+ & MLE & lasso & alasso & SCAD & MCP \\ 
   \hline
@@
 
-While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect.
+While every regularization method erroneously set both simulated true intercept effects as zero (non-significant in MLE), both the adaptive lasso and SCAD correctly identified every true zero effect.
 The lasso identified two false effects while the MCP mistakenly identified one.
 Additionally, the lasso estimation of the true effects was attentuated in comparison to the other regularization methods.
-This is in line with previous research [@fan2001variable], necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed, see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.
+This is in line with previous research [@fan2001variable], necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed; see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, MLE mistakenly identified 3 false effects as significant.
 
 To compare the performance of each penalization method further, particularly in the presence of a small parameter to sample size ratio, a small simulation study was conducted.
-The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size.
+The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how MLE improves as sample size increases, while each of the regularization methods performs well regardless of sample size.
 Each run was replicated 200 times.
@@
 
-For false positives, the adaptive lasso demonstrated the best performance, where the performance of maximum likelihood estimation leveled off at the 0.05 level at a sample size of 1000 as expected.
-For false negatives, lasso penalties demonstrated similar results to maximum likelihood.
+For false positives, the adaptive lasso demonstrated the best performance, where the performance of MLEleveled off at the 0.05 level at a sample size of 1000 as expected.
+For false negatives, lasso penalties demonstrated similar results to MLE.
 This was expected given the tendency of the lasso to under-penalize small coefficients in comparison to the other regularization methods.
@@
 
-This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized structural equation modeling [RegSEM; @jacobucci2016regularized] method and the usage of the \pkg{regsem} package.
+This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of regularized structural equation modeling [RegSEM; @jacobucci2016regularized] and the usage of the \pkg{regsem} package.
 RegSEM allows the use of regularization while keeping the structural equation model intact, adding penalization directly into the estimation of the model.
@@
 This type of research will be facilitated by the general upsurge in the creation of open source software that gives users a general framework to test models.
-This was the motivation behind creating the \pkg{regsem} package in that users can estimate models ranging from simple factor analysis models, to latent longitudinal models with few to many time points, and finally to models with a large number of latent and observed variables.
+This was the motivation behind creating the \pkg{regsem} package, in that users can estimate models ranging from simple factor analysis models, to latent longitudinal models with few to many time points, and finally to models with a large number of latent and observed variables.
 The use of regularization allows for the estimation of much larger structural equation models than before.

### 2017-03-24 draft1.tex
final first draft

@@
 McArdle 2016), was recently developed with the goal of incorporating
-various forms of penalized likelihood estimation with a broad array of
+various forms of penalized likelihood estimation in a broad array of
 structural equations models. The forms of regularization include both
@@
 (e.g.~80). There are 29 estimated parameters in this model, resulting in
-a estimated parameter to sample size ratio as far below even the most
+a estimated parameter to sample size ratio far below even the most
 liberal recommendations (e.g.~10:1 parameters to sample size; Kline
@@
 
-Although a whole host of methods exist to perform variable selection,
-the use of regularization has seen a wide array of application in the
-context of regression, and more recently, in areas such as graphical
-modeling, as well as a host of others. The two most common procedures
-for regularization in regression are the \textit{ridge} (Hoerl and
-Kennard 1970) and the least absolute shrinkage and selection operator
+Although a host of methods exist to perform variable selection, the use
+of regularization has seen a wide array of application in the context of
+regression, and more recently, in areas such as graphical modeling, as
+well as a host of others. The two most common procedures for
+regularization in regression are the \textit{ridge} (Hoerl and Kennard
+1970) and the least absolute shrinkage and selection operator
 (\textit{lasso}; Tibshirani 1996); however, there are various
@@
 between both the slope and intercept, reducing both to independent
-factor scores. Particularly in models with a greater number of latent
+variables. Particularly in models with a greater number of latent
 variables, this becomes increasingly problematic. A method that keeps
@@
             \State Calculate initial fit $F_{t}$
-            \State Set step size $s$. .1 works well at this time.
+            \State Set step size $s$. 0.1 works well at this time.
             \State Set tolerance (tol). e.g. 1e-6
@@
 
-Outside of both ridge and lasso penalties, a whole host of additional
-forms of regularization exist.
+Outside of both ridge and lasso penalties, a host of additional forms of
+regularization exist.
 
@@
 \[
-P_{enet}(\theta_{j}) = 0.5(1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{2}
+P_{enet}(\theta_{j}) = (1-\alpha)\| \theta_{j} \|_{2} + \alpha\| \theta_{j} \|_{1}
 \]
@@
 
-\subsection{Smoothly Clipped Absolute Deviation
-Penalty}\label{smoothly-clipped-absolute-deviation-penalty}
+\subsection{Sparse Extensionse}\label{sparse-extensionse}
 
@@
 
-\subsection{Minimax Concave Penalty}\label{minimax-concave-penalty}
-
-A final regularization method developed to produce sparser penalties
-than the lasso was the minimax concave penalty (MCP, Zhang 2010):
+Additionally, the MCP takes the form of:
 
@@
 the maximum likelihood fit of the model, \pkg{regsem} uses
-\textit{Reticular Action Model} (RAM; J. J. McArdle and McDonald 1984,
-McArdle (2005)) notation to derive an implied covariance matrix. The
-parameters of each SEM are translated into three matrices: the
-\textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A};
-directed paths; e.g.~factor loadings or regressions), and the
-\textit{symmetric} (\textit{S}; undirected paths; e.g.~covariances or
-variances). See Jacobucci, Grimm, and McArdle (2016) for more detail on
-RAM notation.
+\textit{Reticular Action Model} (RAM; McArdle and McDonald 1984; McArdle
+2005) notation to derive an implied covariance matrix. The parameters of
+each SEM are translated into three matrices: the \textit{filter}
+(\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths;
+e.g.~factor loadings or regressions), and the \textit{symmetric}
+(\textit{S}; undirected paths; e.g.~covariances or variances). See
+Jacobucci, Grimm, and McArdle (2016) for more detail on RAM notation and
+its application to RegsEm.
 
@@
 
+Structural equation modeling is hard, and pairing with regularization
+doesn't make it any easier. Given this, and the number of options
+available in the \pkg{regsem} package, a Google group forum was created
+in order to answer questions and trouble shoot at
+\url{https://groups.google.com/forum/\#!forum/regsem}.
+
 \section{Comparison}\label{comparison}
@@
 While every regularization method erroneously set both simulated true
-intercept effects as zero (as in maximum likelihood, which accounts for
-these errors), both the adaptive lasso and SCAD correctly identified
-every true zero effect. The lasso identified two false effects while the
-MCP mistakenly identified one. Additionally, the lasso estimation of the
-true effects was attentuated in comparison to the other regularization
-methods. This is in line with previous research (Fan and Li 2001),
-necessitating the use of a two-step relaxed lasso method (Meinshausen
-2007, see Jacobucci, Grimm, and McArdle (2016)) As expected given the
-small ratio between number of estimated parameters and sample size,
-maximum likelihood mistakenly identified 3 false effects as significant.
+intercept effects as zero (non-significant in MLE), both the adaptive
+lasso and SCAD correctly identified every true zero effect. The lasso
+identified two false effects while the MCP mistakenly identified one.
+Additionally, the lasso estimation of the true effects was attentuated
+in comparison to the other regularization methods. This is in line with
+previous research (Fan and Li 2001), necessitating the use of a two-step
+relaxed lasso method (Meinshausen 2007; see Jacobucci, Grimm, and
+McArdle 2016) As expected given the small ratio between number of
+estimated parameters and sample size, MLE mistakenly identified 3 false
+effects as significant.
 
@@
 kept, but the sample size was varied to include 80, 200, and 1000 to
-demonstrate how maximum likelihood estimation of effects improves as
-sample size increases, while each of the regularization methods performs
-well regardless of sample size. Each run was replicated 200 times. For
-each regularization method, the BIC was used to choose a final model
-among the 40 penalty vales. The results are displayed in Table 2.
+demonstrate how MLE improves as sample size increases, while each of the
+regularization methods performs well regardless of sample size. Each run
+was replicated 200 times. For each regularization method, the BIC was
+used to choose a final model among the 40 penalty vales. The results are
+displayed in Table 2.
 
@@
 For false positives, the adaptive lasso demonstrated the best
-performance, where the performance of maximum likelihood estimation
-leveled off at the 0.05 level at a sample size of 1000 as expected. For
-false negatives, lasso penalties demonstrated similar results to maximum
-likelihood. This was expected given the tendency of the lasso to
-under-penalize small coefficients in comparison to the other
-regularization methods. The adaptive lasso and SCAD demonstrated
-slightly worse results, however, outside of the MCP, each method made
-either zero or near zero errors at a sample size of 1000. The poor
-performance of the MCP may be in part due to fixing the \(\gamma\)
-penalty to 3.7. Varying this parameter may improve the performance of
-the method. In summary, the regularization methods demonstrated an
-improvement over maximum likelihood, particularly at small samples, for
-a model that had a large number of estimated parameters.
+performance, where the performance of MLEleveled off at the 0.05 level
+at a sample size of 1000 as expected. For false negatives, lasso
+penalties demonstrated similar results to MLE. This was expected given
+the tendency of the lasso to under-penalize small coefficients in
+comparison to the other regularization methods. The adaptive lasso and
+SCAD demonstrated slightly worse results, however, outside of the MCP,
+each method made either zero or near zero errors at a sample size of
+1000. The poor performance of the MCP may be in part due to fixing the
+\(\gamma\) penalty to 3.7. Varying this parameter may improve the
+performance of the method. In summary, the regularization methods
+demonstrated an improvement over maximum likelihood, particularly at
+small samples, for a model that had a large number of estimated
+parameters.
 
@@
 This paper provides an introduction to the \pkg{regsem} package,
-outlining the mathematical details of the regularized structural
-equation modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) method
-and the usage of the \pkg{regsem} package. RegSEM allows the use of
-regularization while keeping the structural equation model intact,
-adding penalization directly into the estimation of the model. The
-application of RegSEM was detailed using two example models: a latent
-growth curve model with 20 predictors of both the latent intercept and
-slope, along with a factor analysis with one latent factor. With the
-latent growth curve model, the small parameter to sample size ratio
-resulted in a larger number of false positives in using maximum
-likelihood estimation. In both the simulated example and the small
-simulation, the different types of regularization in \pkg{regsem}
-demonstrated better false positive and negative rates in comparison to
-maxiumum likelihood across sample sizes.
+outlining the mathematical details of regularized structural equation
+modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) and the usage of
+the \pkg{regsem} package. RegSEM allows the use of regularization while
+keeping the structural equation model intact, adding penalization
+directly into the estimation of the model. The application of RegSEM was
+detailed using two example models: a latent growth curve model with 20
+predictors of both the latent intercept and slope, along with a factor
+analysis with one latent factor. With the latent growth curve model, the
+small parameter to sample size ratio resulted in a larger number of
+false positives in using maximum likelihood estimation. In both the
+simulated example and the small simulation, the different types of
+regularization in \pkg{regsem} demonstrated better false positive and
+negative rates in comparison to maxiumum likelihood across sample sizes.
 
@@
 gives users a general framework to test models. This was the motivation
-behind creating the \pkg{regsem} package in that users can estimate
+behind creating the \pkg{regsem} package, in that users can estimate
 models ranging from simple factor analysis models, to latent
@@
 latent change score models (Jacobucci and Grimm 2017), mediation models
-(Serang et al. 2017). Future updates to \pkg{regsem} will focus on
+(Serang et al. in press). Future updates to \pkg{regsem} will focus on
 decreasing the computational time of large latent variable models in
@@
 \hypertarget{ref-McArdle_1984}{}
-McArdle, John J., and Roderick P. McDonald. 1984. ``Some Algebraic
+McArdle, John J, and Roderick P. McDonald. 1984. ``Some Algebraic
 Properties of the Reticular Action Model for Moment Structures.''
@@
 \hypertarget{ref-serang2017xmed}{}
-Serang, Sarfaraz, Ross Jacobucci, Kim Brimhall, and Kevin J Grimm. 2017.
-``Exploratory Mediation Analysis via Regularization.'' \emph{Structural
-Equation Modeling: A Multidisciplinary Journal}. Taylor \& Francis.
+Serang, Sarfaraz, Ross Jacobucci, Kim Brimhall, and Kevin J Grimm. in
+press. ``Exploratory Mediation Analysis via Regularization.''
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}. Taylor
+\& Francis.
 

### 2017-03-24 create_fig.R
add code

@@ -1,0 +1,34 @@
+
+
+Xs <- seq(-2,2,.01)
+
+plot(Xs,abs(Xs),"l",xlab="X",ylab="P(x)",ylim=c(0,1.2),lwd=2)
+
+# see breheny
+
+library(DiceKriging)
+SCAD(.1,.1)
+
+out <- rep(NA,length(Xs))
+for(i in 1:length(Xs)){
+  out[i] <- SCAD(Xs[i],.5)
+}
+lines(Xs,out,"l",lty=2,lwd=2)
+
+mcp <- function(x,lambda){
+  x <- abs(x)
+  a <- 3.7
+  if(x <= a*lambda){
+    lambda*x - (x**2)/(2*a)
+  }else{
+    .5*a*(lambda**2)
+  }
+}
+
+out2 <- rep(NA,length(Xs))
+for(i in 1:length(Xs)){
+  out2[i] <- mcp(Xs[i],.5)
+}
+lines(Xs,out2,"l",lty=3,lwd=2)
+abline(a=0,b=0)
+legend("bottomright", c("Lasso","SCAD","MCP"),lty=c(1,2,3), lwd=2,cex=.8)

### 2017-03-24 sim.R

@@ -1,0 +1,90 @@
+library(lavaan)
+library(semPlot)
+library(semTools)
+library(regsem)
+
+count <- 0
+niters <- 200
+nobs <- c(80,200,1000)
+res.mat1 <- matrix(NA,niters*length(nobs),6)
+res.mat2 <- matrix(NA,niters*length(nobs),6)
+
+for(i in 1:niters){
+  for(j in 1:length(nobs)){
+
+count <- count + 1
+res.mat1[count,1] <- res.mat2[count,1] <- nobs[j]
+
+sim.mod <- "
+i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
+s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
+i ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10
+s ~ 1*c1 + .2*c2 + 0*c3 + 0*c4 + 0*c5 + 0*c6 + 0*c7 + 0*c8+ 0*c9+ 0*c10"
+
+dat <- simulateData(sim.mod,model.type="growth",sample.nobs=nobs[j],seed=i)
+
+mod1 <- "
+i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
+s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
+i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
+s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
+"
+
+out <- growth(mod1,dat,fixed.x=T)
+
+res.mat1[count,2] <- sum(parameterestimates(out)[c(11:18,21:28),"pvalue"] < .05)
+res.mat2[count,2] <- sum(parameterestimates(out)[c(9:10,19:20),"pvalue"] > .05)
+
+
+
+reg.out <- cv_regsem(out,pars_pen=c(1:20),type="lasso",n.lambda=40,mult.start=FALSE,jump=.015)
+reg.out
+
+
+loc1 <- which(reg.out[[2]][,"BIC"] ==min(reg.out[[2]][,"BIC"]))[1]
+res.mat1[count,3] <- sum(reg.out[[1]][loc1,c(3:10,13:20)] != 0)
+res.mat2[count,3] <- sum(reg.out[[1]][loc1,c(1:2,11:12)] == 0)
+
[…]

### 2017-04-05 Untitled/Untitled.Rmd
try and fail

---
title: Capitalized Title Here
author:
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Author Two
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
   The \pkg{regsem} package in R, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation in a broad array of structural equations models. The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996], along with sparser extensions. RegSEM is particularly useful for structural equation models that have a small parameter to sample size ratio, as the addition of penalties can reduce the complexity, thus reducing the bias of the parameter estimates. The paper covers the algorithmic details and an overview of the use of \pkg{regsem} with the application of both factor analysis and latent growth curve models.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

## Introduction

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

## Section title in sentence case

This section may contain a figure such as Figure \ref{figure:rlogo}.

\begin{figure}[htbp]
  \centering
  \includegraphics{Rlogo}
  \caption{The logo of R.}
  \label{figure:rlogo}
\end{figure}

## Another section

There will likely be several sections, perhaps including code snippets, such as:

```{r}
x <- 1:10
x
```

## Summary

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).
\bibliography{RJreferences}

### 2017-04-05 Untitled/Untitled.tex
try and fail

% !TeX root = RJwrapper.tex
\title{Capitalized Title Here}
\author{by Author One, Author Two}

\maketitle

\abstract{%
The \pkg{regsem} package in R, an implementation of regularized
structural equation modeling {[}RegSEM; @jacobucci2016regularized{]},
was recently developed with the goal of incorporating various forms of
penalized likelihood estimation in a broad array of structural equations
models. The forms of regularization include both the \textit{ridge}
{[}@hoerl1970{]} and the least absolute shrinkage and selection operator
{[}\textbackslash{}textit\{lasso\}; @Tibshirani1996{]}, along with
sparser extensions. RegSEM is particularly useful for structural
equation models that have a small parameter to sample size ratio, as the
addition of penalties can reduce the complexity, thus reducing the bias
of the parameter estimates. The paper covers the algorithmic details and
an overview of the use of \pkg{regsem} with the application of both
factor analysis and latent growth curve models.
}

\subsection{Introduction}\label{introduction}

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

\subsection{Section title in sentence
case}\label{section-title-in-sentence-case}

This section may contain a figure such as Figure \ref{figure:rlogo}.

\begin{figure}[htbp]
  \centering
  \includegraphics{Rlogo}
  \caption{The logo of R.}
  \label{figure:rlogo}
\end{figure}

\subsection{Another section}\label{another-section}

There will likely be several sections, perhaps including code snippets,
such as:

\begin{Schunk}
\begin{Sinput}
x <- 1:10
x
\end{Sinput}
\begin{Soutput}
#>  [1]  1  2  3  4  5  6  7  8  9 10
\end{Soutput}
\end{Schunk}

\subsection{Summary}\label{summary}

This file is only a basic article template. For full details of
\emph{The R Journal} style and information on how to prepare your
article for submission, see the
\href{https://journal.r-project.org/share/author-guide.pdf}{Instructions
for Authors}. \bibliography{RJreferences}

\address{%
Author One\\
Affiliation\\
line 1\\ line 2\\
}
\href{mailto:author1@work}{\nolinkurl{author1@work}}

\address{%
Author Two\\
Affiliation\\
line 1\\ line 2\\
}
\href{mailto:author2@work}{\nolinkurl{author2@work}}

### 2017-04-05 draft1.Rmd
try and fail

@@
 title:
-  formatted: "\\pkg{regsem}: Regularized Structural Equation Modeling"
+  formatted: "\\textbf{regsem}: Regularized Structural Equation Modeling"
   # If you use tex in the formatted title, also supply version without
@@
   # For running headers, if needed
-  short:     "\\pkg{regsem}"
+  short:     "\\textbf{regsem}"
 abstract: >
-  The \pkg{regsem} package in \proglang{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation in a broad array of structural equations models.
+   The \textbf{regsem} package in \textbf{R}, an implementation of regularized structural equation modeling [RegSEM; @jacobucci2016regularized], was recently developed with the goal of incorporating various forms of penalized likelihood estimation in a broad array of structural equations models.
 The forms of regularization include both the \textit{ridge} [@hoerl1970] and the least absolute shrinkage and selection operator [\textit{lasso}; @Tibshirani1996], along with sparser extensions.
 RegSEM is particularly useful for structural equation models that have a small parameter to sample size ratio, as the addition of penalties can reduce the complexity, thus reducing the bias of the parameter estimates.
-The paper covers the algorithmic details and an overview of the use of \pkg{regsem} with the application of both factor analysis and latent growth curve models.
+The paper covers the algorithmic details and an overview of the use of \textbf{regsem} with the application of both factor analysis and latent growth curve models.
 keywords:
   # at least one keyword must be supplied
-  formatted: [regularization, structural equation modeling, latent variables, "\\proglang{R}"]
+  formatted: [regularization, structural equation modeling, latent variables, "\\textbf{R}"]
   plain:     [regularization, structural equation modeling, latent variables, R]
@@
   \usepackage{algorithm}
+  \usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e} 
   \usepackage[noend]{algpseudocode}
@@
 
-output: rticles::jss_article
+output: pdf_document#rticles::rjournal_article
 bibliography: jss_regsem.bib
@@
 
-\begin{minipage}{\textwidth}
+% \begin{minipage}{\textwidth}
 	%	\renewcommand\footnoterule{}    
@@
 	\end{algorithm}
-\end{minipage}
+%\end{minipage}
 
@@
 For both the SCAD and MCP, both the $\gamma$ and $\lambda$ parameters are used as hyper-parameters.
-This involves testing models over a two-dimensional array of parameters, however, in \pkg{regsem}, $\gamma$ is by default fixed to 3.7 per @fan2001variable.
+This involves testing models over a two-dimensional array of parameters, however, in \textbf{regsem}, $\gamma$ is by default fixed to 3.7 per @fan2001variable.
 
@@
 
-RegSEM is implemented as the \pkg{regsem} package [@jacobucci2016package] in the \proglang{R} statistical environment [@statspackage].
-To estimate the maximum likelihood fit of the model, \pkg{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984; @mcardle2005] notation to derive an implied covariance matrix.
+RegSEM is implemented as the \textbf{regsem} package [@jacobucci2016package] in the \textbf{R} statistical environment [@statspackage].
+To estimate the maximum likelihood fit of the model, \textbf{regsem} uses \textit{Reticular Action Model} [RAM; @McArdle_1984; @mcardle2005] notation to derive an implied covariance matrix.
 The parameters of each SEM are translated into three matrices: the \textit{filter} (\textit{F}), the \textit{asymmetric} (\textit{A}; directed paths; e.g.
@@
 
-Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package [@rosseel2012] for structural equation models.
-\pkg{lavaan} is a general SEM software program that can fit a wide array of models with various estimation methods.
-To use \pkg{regsem}, the user has to first fit the model in \pkg{lavaan}.
+Syntax for using the \textbf{regsem} is based on the \textbf{lavaan} package [@rosseel2012] for structural equation models.
+\textbf{lavaan} is a general SEM software program that can fit a wide array of models with various estimation methods.
+To use \textbf{regsem}, the user has to first fit the model in \textbf{lavaan}.
 Note that particularly in cases that the number of variables is larger than the sample size, the model in lavaan does not need to converge, let alone run.
-In this case, the \code{do.fit=FALSE} argument in lavaan can be used.
+In this case, the \textbf{do.fit=FALSE} argument in lavaan can be used.
 As a canonical example, below is the code for a confirmatory factor analysis model with one latent factor and nince indicators from the @holzinger1939study dataset.
@@
 
-After a model is run in lavaan, using \code{lavaan()} or any of the wrapper functions for fitting a model (i.e.
-\code{sem()}, \code{cfa()}, or \code{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem()}.
-The \code{regsem()} function runs a model with one penalty value, whereas \code{multi_optim()} does the same but allows for the use of random starting values.
-However, the main function is \code{cv_regsem()} as this not only runs the model, but runs it across a vector of varying penalty values.
+After a model is run in lavaan, using \textbf{lavaan()} or any of the wrapper functions for fitting a model (i.e.
+\textbf{sem()}, \textbf{cfa()}, or \textbf{growth()}), the object is then used by the regsem package to translate the model into RAM notation and run using one of three functions: \textbf{regsem()}, \textbf{multi_optim()}, or \textbf{cv_regsem()}.
+The \textbf{regsem()} function runs a model with one penalty value, whereas \textbf{multi_optim()} does the same but allows for the use of random starting values.
+However, the main function is \textbf{cv_regsem()} as this not only runs the model, but runs it across a vector of varying penalty values.
 For instance in the above one-factor model, each of the factor loadings can be tested with lasso penalties to determine whether each indicator is a necessary component of the latent factor:
@@
 
-In this, the function \code{extractMatrices()} allows the user to examine at how the lavaan model is translated into RAM matrices.
+In this, the function \textbf{extractMatrices()} allows the user to examine at how the lavaan model is translated into RAM matrices.
 Further, by looking at the \textit{A} matrix, the parameter numbers corresponding to the factor loadings of interest for regularization can be identified.
-For this model, the factor loadings represent parameter numbers one through nine, of which we pass directly to the \code{pars_pen} argument of the \code{cv_regsem()} function (if \code{pars_pen=NULL} then all directed effects, outside of intercepts, are penalized).
-Additionally, we pass the arguments of how many values of penalty we want to test (\code{n.lambda=15}), how much the penalty should increase for each model (\code{jump=.05}), and finally that lasso estimation is used (\code{type="lasso"}).
+For this model, the factor loadings represent parameter numbers one through nine, of which we pass directly to the \textbf{pars_pen} argument of the \textbf{cv_regsem()} function (if \textbf{pars_pen=NULL} then all directed effects, outside of intercepts, are penalized).
+Additionally, we pass the arguments of how many values of penalty we want to test (\textbf{n.lambda=15}), how much the penalty should increase for each model (\textbf{jump=.05}), and finally that lasso estimation is used (\textbf{type="lasso"}).
 
-The \code{out.reg} object contains two components, \code{out.reg[[1]]} has the parameter estimates for each of the 15 models,
+The \textbf{out.reg} object contains two components, \textbf{out.reg[[1]]} has the parameter estimates for each of the 15 models,
 
@@
 
-while \code{out.reg[[2]]} contains information pertaining to the fit of each model:
+while \textbf{out.reg[[2]]} contains information pertaining to the fit of each model:
 
@@
 
-Instead of examining the \code{out.reg[[1]]} output matrix of parameter estimates, users also have the option to plot the trajectory of each of the penalized parameters.
-This is accomplished with \code{plot_cv(out.reg,pars=1:9)}, resulting in:
+Instead of examining the \textbf{out.reg[[1]]} output matrix of parameter estimates, users also have the option to plot the trajectory of each of the penalized parameters.
+This is accomplished with \textbf{plot_cv(out.reg,pars=1:9)}, resulting in:
 
 ```{r}
-plot_cv(out.reg,pars=1:9)
+plot(out.reg,pars=1:9)
 ```
 
-After a final model (penalty) is chosen, users have the option either just use the output from \code{cv_regsem()}, or the final model can be re-run with either \code{regsem()} or \code{multi_optim()} to attain additional information.
+After a final model (penalty) is chosen, users have the option either just use the output from \textbf{cv_regsem()}, or the final model can be re-run with either \textbf{regsem()} or \textbf{multi_optim()} to attain additional information.
 In the model above, the best fitting penalty, according to the BIC, is $\lambda=0$.
 However, for demonstration purposes, we can choose a penalty of 0.2.
-With this, the model is re-run with \code{regsem()}
+With this, the model is re-run with \textbf{regsem()}
 
@@
 
-Note that the arguments used above correspond to the same arguments in \code{multi_optim()}.
-However, \code{multi_optim()} has additional optional arguments corresponding to the number or random starts to try.
-Additional fit indices can be attained through the \code{fit_indices()} function.
+Note that the arguments used above correspond to the same arguments in \textbf{multi_optim()}.
+However, \textbf{multi_optim()} has additional optional arguments corresponding to the number or random starts to try.
+Additional fit indices can be attained through the \textbf{fit_indices()} function.
 
@@
 
-These same fit measures can be accessed through \code{cv_regsem} through changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
+These same fit measures can be accessed through \textbf{cv_regsem} through changing the defaults with the \textbf{fit.ret=c("rmsea","BIC")} argument.
 Finally, instead of assessing these fit indices on the same sample that the models were run on, a holdout dataset could be used.
-This can be done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with \code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the holdout covariance matrix.
+This can be done two ways: either with \textbf{cv_regsem(...,fit.ret2="test")} or with \textbf{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the holdout covariance matrix.
 
 Structural equation modeling is hard, and pairing with regularization doesn't make it any easier.
-Given this, and the number of options available in the \pkg{regsem} package, a Google group forum was created in order to answer questions and trouble shoot at https://groups.google.com/forum/#!forum/regsem.
+Given this, and the number of options available in the \textbf{regsem} package, a Google group forum was created in order to answer questions and trouble shoot at https://groups.google.com/forum/#!forum/regsem.
 
@@
 
-To compare the different types of penalties in \pkg{regsem}, we return to the the initial example of the latent growth curve model displayed in Figure 1.
-Using the same simulated data, the model can be run in \pkg{lavaan} as
+To compare the different types of penalties in \textbf{regsem}, we return to the the initial example of the latent growth curve model displayed in Figure 1.
+Using the same simulated data, the model can be run in \textbf{lavaan} as
 
@@
 
-Comparing different types of penalties in \pkg{regsem} requires a different specification of the \code{type} argument.
-The options currently include maximum likelihood (\code{"none"}), ridge (\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso (\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}), and MCP (\code{"mcp"}).
+Comparing different types of penalties in \textbf{regsem} requires a different specification of the \textbf{type} argument.
+The options currently include maximum likelihood (\textbf{"none"}), ridge (\textbf{"ridge"}), lasso (\textbf{"lasso"}), adaptive lasso (\textbf{"alasso"}), elastic net (\textbf{"enet"}), SCAD (\textbf{"scad"}), and MCP (\textbf{"mcp"}).
 For the elastic net, there is an additional hyperparameter, $\alpha$ that controls the tradeoff between ridge and lasso penalties.
-This is specified as \code{alpha=} , which has a default of 0.5.
-Additionally, both the SCAD and MCP have the additional hyper parameter of $\gamma$, which is specified as \code{gamma=} and defaults to 3.7 per @fan2001variable.
+This is specified as \textbf{alpha=} , which has a default of 0.5.
+Additionally, both the SCAD and MCP have the additional hyper parameter of $\gamma$, which is specified as \textbf{gamma=} and defaults to 3.7 per @fan2001variable.
 
@@
 If there was substantial collinearity among covariates, the elastic net would be more appropriate to simultaneously select predictors while also accounting for the collinearity.
-The parameter estimates corresponding the the best fit of the BIC are has the fit of each model, resulting in Table 1, created using the \pkg{xtable} package [@dahl2009xtable].
+The parameter estimates corresponding the the best fit of the BIC are has the fit of each model, resulting in Table 1, created using the \textbf{xtable} package [@dahl2009xtable].
 
@@
 
-This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of regularized structural equation modeling [RegSEM; @jacobucci2016regularized] and the usage of the \pkg{regsem} package.
+This paper provides an introduction to the \textbf{regsem} package, outlining the mathematical details of regularized structural equation modeling [RegSEM; @jacobucci2016regularized] and the usage of the \textbf{regsem} package.
 RegSEM allows the use of regularization while keeping the structural equation model intact, adding penalization directly into the estimation of the model.
@@
 With the latent growth curve model, the small parameter to sample size ratio resulted in a larger number of false positives in using maximum likelihood estimation.
-In both the simulated example and the small simulation, the different types of regularization in \pkg{regsem} demonstrated better false positive and negative rates in comparison to maxiumum likelihood across sample sizes.
+In both the simulated example and the small simulation, the different types of regularization in \textbf{regsem} demonstrated better false positive and negative rates in comparison to maxiumum likelihood across sample sizes.
 
@@
 This type of research will be facilitated by the general upsurge in the creation of open source software that gives users a general framework to test models.
-This was the motivation behind creating the \pkg{regsem} package, in that users can estimate models ranging from simple factor analysis models, to latent longitudinal models with few to many time points, and finally to models with a large number of latent and observed variables.
+This was the motivation behind creating the \textbf{regsem} package, in that users can estimate models ranging from simple factor analysis models, to latent longitudinal models with few to many time points, and finally to models with a large number of latent and observed variables.
 The use of regularization allows for the estimation of much larger structural equation models than before.
@@
 
-With highly constrained structural equation models, achieving model convergence can be particularly problematic in using \pkg{regsem}.
+With highly constrained structural equation models, achieving model convergence can be particularly problematic in using \textbf{regsem}.
 For instance, with the latent change score model [@mcardle2001latent], Bayesian regularization methods have less difficulty in reaching convergence across chains (Jacobucci and Grimm 2017).
@@
 
-Future research with \pkg{regsem} should focus on a number of avenues.
+Future research with \textbf{regsem} should focus on a number of avenues.
 One is comparing the different forms of regularization, delineating which method may be best in which setting.
@@
 Although 40 penalties in the models tested above can be run in a matter of seconds on a standard laptop, larger models can take much longer.
-To handle this, future implementation with \pkg{regsem} will test the inclusion of different types of optimization, specifically testing whether computation of the Hessian (or approximate Hessian) can reduce the number of optimization steps.
+To handle this, future implementation with \textbf{regsem} will test the inclusion of different types of optimization, specifically testing whether computation of the Hessian (or approximate Hessian) can reduce the number of optimization steps.
 
@@
 
-This paper provided a brief overview on the use of the \pkg{regsem} package as an implementation of regularized structural equation modeling.
-Because structural equation modeling encompasses a wide array of latent variable models, the \pkg{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.
-RegSEM, and thus the \pkg{regsem} package, has been evaluated in a wide array of SEM models, including confirmatory factor analysis [@jacobucci2016regularized], latent change score models (Jacobucci and Grimm 2017), mediation models [@serang2017xmed].
-Future updates to \pkg{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
+This paper provided a brief overview on the use of the \textbf{regsem} package as an implementation of regularized structural equation modeling.
+Because structural equation modeling encompasses a wide array of latent variable models, the \textbf{regsem} package was created as a general package for including different forms of regularization into a host of latent variable models.
+RegSEM, and thus the \textbf{regsem} package, has been evaluated in a wide array of SEM models, including confirmatory factor analysis [@jacobucci2016regularized], latent change score models (Jacobucci and Grimm 2017), mediation models [@serang2017xmed].
+Future updates to \textbf{regsem} will focus on decreasing the computational time of large latent variable models in order to provide an avenue of testing for researchers collecting larger and larger datasets.
 RegSEM is a method that operates at all ends of the data size spectrum: allowing for a reduction in complexity when the sample size is small, along with  dimension reduction in the presence of large data (both $N$ and $P$).
 
-# References
+\bibliography{RJreferences}

### 2017-04-05 draft1.tex
try and fail

@@
-\documentclass[article]{jss}
-\usepackage[utf8]{inputenc}
+% !TeX root = RJwrapper.tex
+\title{true}
+\author{by Ross Jacobucci}
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\maketitle
 
-\author{
-Ross Jacobucci\\University of Notre Dame
-}
-\title{\pkg{regsem}: Regularized Structural Equation Modeling}
-\Keywords{regularization, structural equation modeling, latent variables, \proglang{R}}
-
-\Abstract{
-The \pkg{regsem} package in \proglang{R}, an implementation of
+\abstract{%
+The \textbf{regsem} package in \textbf{R}, an implementation of
 regularized structural equation modeling (RegSEM; Jacobucci, Grimm, and
@@
 reducing the bias of the parameter estimates. The paper covers the
-algorithmic details and an overview of the use of \pkg{regsem} with the
-application of both factor analysis and latent growth curve models.
+algorithmic details and an overview of the use of \textbf{regsem} with
+the application of both factor analysis and latent growth curve models.
 }
-
-\Plainauthor{Ross Jacobucci}
-\Plaintitle{regsem: Regularized Structural Equation Modeling}
-\Shorttitle{\pkg{regsem}}
-\Plainkeywords{regularization, structural equation modeling, latent variables, R}
-
-%% publication information
-%% \Volume{50}
-%% \Issue{9}
-%% \Month{June}
-%% \Year{2012}
-\Submitdate{}
-%% \Acceptdate{2012-06-04}
-
-\Address{
-    Ross Jacobucci\\
-  University of Notre Dame\\
-  118 Haggar Hall, Notre Dame, IN 46556\\
-  E-mail: \href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}\\
-  URL: rjacobucci.com\\~\\
-  }
-
-\usepackage{amsmath} \usepackage{float} \usepackage{algorithm}
-\usepackage[noend]{algpseudocode} \usepackage[subnum]{cases}
-
-\begin{document}
 
@@
 involves testing models over a two-dimensional array of parameters,
-however, in \pkg{regsem}, \(\gamma\) is by default fixed to 3.7 per Fan
-and Li (2001).
+however, in \textbf{regsem}, \(\gamma\) is by default fixed to 3.7 per
+Fan and Li (2001).
 
@@
 
-RegSEM is implemented as the \pkg{regsem} package (Jacobucci 2017) in
-the \proglang{R} statistical environment (R Core Team 2017). To estimate
-the maximum likelihood fit of the model, \pkg{regsem} uses
+RegSEM is implemented as the \textbf{regsem} package (Jacobucci 2017) in
+the \textbf{R} statistical environment (R Core Team 2017). To estimate
+the maximum likelihood fit of the model, \textbf{regsem} uses
 \textit{Reticular Action Model} (RAM; McArdle and McDonald 1984; McArdle
@@
 
-Syntax for using the \pkg{regsem} is based on the \pkg{lavaan} package
-(Rosseel 2012) for structural equation models. \pkg{lavaan} is a general
-SEM software program that can fit a wide array of models with various
-estimation methods. To use \pkg{regsem}, the user has to first fit the
-model in \pkg{lavaan}. Note that particularly in cases that the number
-of variables is larger than the sample size, the model in lavaan does
-not need to converge, let alone run. In this case, the
-\code{do.fit=FALSE} argument in lavaan can be used. As a canonical
+Syntax for using the \textbf{regsem} is based on the \textbf{lavaan}
+package (Rosseel 2012) for structural equation models. \textbf{lavaan}
+is a general SEM software program that can fit a wide array of models
+with various estimation methods. To use \textbf{regsem}, the user has to
+first fit the model in \textbf{lavaan}. Note that particularly in cases
+that the number of variables is larger than the sample size, the model
+in lavaan does not need to converge, let alone run. In this case, the
+\textbf{do.fit=FALSE} argument in lavaan can be used. As a canonical
 example, below is the code for a confirmatory factor analysis model with
@@
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 library(lavaan)
@@
 out <- cfa(mod,HolzingerSwineford1939)
-\end{CodeInput}
-\end{CodeChunk}
+\end{Sinput}
+\end{Schunk}
 
-After a model is run in lavaan, using \code{lavaan()} or any of the
-wrapper functions for fitting a model (i.e. \code{sem()}, \code{cfa()},
-or \code{growth()}), the object is then used by the regsem package to
-translate the model into RAM notation and run using one of three
-functions: \code{regsem()}, \code{multi_optim()}, or \code{cv_regsem()}.
-The \code{regsem()} function runs a model with one penalty value,
-whereas \code{multi_optim()} does the same but allows for the use of
-random starting values. However, the main function is \code{cv_regsem()}
-as this not only runs the model, but runs it across a vector of varying
-penalty values. For instance in the above one-factor model, each of the
-factor loadings can be tested with lasso penalties to determine whether
-each indicator is a necessary component of the latent factor:
+After a model is run in lavaan, using \textbf{lavaan()} or any of the
+wrapper functions for fitting a model (i.e. \textbf{sem()},
+\textbf{cfa()}, or \textbf{growth()}), the object is then used by the
+regsem package to translate the model into RAM notation and run using
+one of three functions: \textbf{regsem()}, \textbf{multi_optim()}, or
+\textbf{cv_regsem()}. The \textbf{regsem()} function runs a model with
+one penalty value, whereas \textbf{multi_optim()} does the same but
+allows for the use of random starting values. However, the main function
+is \textbf{cv_regsem()} as this not only runs the model, but runs it
+across a vector of varying penalty values. For instance in the above
+one-factor model, each of the factor loadings can be tested with lasso
+penalties to determine whether each indicator is a necessary component
+of the latent factor:
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 library(regsem)
@@
                     pars_pen=c(1:9),n.lambda=15,jump=.05)
-\end{CodeInput}
-\end{CodeChunk}
+\end{Sinput}
+\end{Schunk}
 
-In this, the function \code{extractMatrices()} allows the user to
+In this, the function \textbf{extractMatrices()} allows the user to
 examine at how the lavaan model is translated into RAM matrices.
@@
 numbers one through nine, of which we pass directly to the
-\code{pars_pen} argument of the \code{cv_regsem()} function (if
-\code{pars_pen=NULL} then all directed effects, outside of intercepts,
+\textbf{pars_pen} argument of the \textbf{cv_regsem()} function (if
+\textbf{pars_pen=NULL} then all directed effects, outside of intercepts,
 are penalized). Additionally, we pass the arguments of how many values
-of penalty we want to test (\code{n.lambda=15}), how much the penalty
-should increase for each model (\code{jump=.05}), and finally that lasso
-estimation is used (\code{type="lasso"}).
+of penalty we want to test (\textbf{n.lambda=15}), how much the penalty
+should increase for each model (\textbf{jump=.05}), and finally that
+lasso estimation is used (\textbf{type="lasso"}).
 
-The \code{out.reg} object contains two components, \code{out.reg[[1]]}
-has the parameter estimates for each of the 15 models,
+The \textbf{out.reg} object contains two components,
+\textbf{out.reg[[1]]} has the parameter estimates for each of the 15
+models,
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 head(round(out.reg[[1]],2),5)
-\end{CodeInput}
-\begin{CodeOutput}
-     f1 -> x1 f1 -> x2 f1 -> x3 f1 -> x4 f1 -> x5 f1 -> x6 f1 -> x7
-[1,]     0.51     0.26     0.25     0.98     1.08     0.92     0.20
-[2,]     0.41     0.17     0.17     0.89     0.98     0.83     0.12
-[3,]     0.33     0.10     0.10     0.83     0.91     0.77     0.06
-[4,]     0.27     0.04     0.04     0.78     0.87     0.72     0.01
-[5,]     0.21     0.00     0.00     0.75     0.83     0.69     0.00
-     f1 -> x8 f1 -> x9 x1 ~~ x1 x2 ~~ x2 x3 ~~ x3 x4 ~~ x4 x5 ~~ x5
-[1,]     0.20     0.31     1.10     1.31     1.21     0.38     0.49
-[2,]     0.13     0.23     1.11     1.32     1.22     0.38     0.48
-[3,]     0.08     0.17     1.13     1.33     1.23     0.38     0.47
-[4,]     0.03     0.12     1.15     1.35     1.25     0.38     0.46
-[5,]     0.00     0.07     1.18     1.37     1.26     0.39     0.46
-     x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
-[1,]     0.36     1.15     0.98     0.92
-[2,]     0.36     1.15     0.99     0.93
-[3,]     0.36     1.16     1.00     0.94
-[4,]     0.37     1.17     1.01     0.96
-[5,]     0.38     1.18     1.02     0.97
-\end{CodeOutput}
-\end{CodeChunk}
+\end{Sinput}
+\begin{Soutput}
+#>      f1 -> x1 f1 -> x2 f1 -> x3 f1 -> x4 f1 -> x5 f1 -> x6 f1 -> x7
+#> [1,]     0.51     0.26     0.25     0.98     1.08     0.92     0.20
+#> [2,]     0.42     0.17     0.16     0.90     0.99     0.83     0.11
+#> [3,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
+#> [4,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
+#> [5,]     0.00     0.00     0.00     0.00     0.00     0.00     0.00
+#>      f1 -> x8 f1 -> x9 x1 ~~ x1 x2 ~~ x2 x3 ~~ x3 x4 ~~ x4 x5 ~~ x5
+#> [1,]     0.20     0.31      1.1     1.31     1.21     0.38     0.49
+#> [2,]     0.11     0.22      1.1     1.31     1.21     0.38     0.49
+#> [3,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
+#> [4,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
+#> [5,]     0.00     0.00      1.1     1.31     1.21     0.38     0.49
+#>      x6 ~~ x6 x7 ~~ x7 x8 ~~ x8 x9 ~~ x9
+#> [1,]     0.36     1.15     0.98     0.92
+#> [2,]     0.36     1.15     0.98     0.92
+#> [3,]     0.36     1.15     0.98     0.92
+#> [4,]     0.36     1.15     0.98     0.92
+#> [5,]     0.36     1.15     0.98     0.92
+\end{Soutput}
+\end{Schunk}
 
-while \code{out.reg[[2]]} contains information pertaining to the fit of
-each model:
+while \textbf{out.reg[[2]]} contains information pertaining to the fit
+of each model:
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 round(out.reg[[2]],2)
-\end{CodeInput}
-\begin{CodeOutput}
-      lambda conv rmsea     BIC
- [1,]   0.00    0  0.19 7805.18
- [2,]   0.05    0  0.19 7815.39
- [3,]   0.10    0  0.20 7840.40
- [4,]   0.15    0  0.21 7875.41
- [5,]   0.20    0  0.20 7885.68
- [6,]   0.25    0  0.21 7910.92
- [7,]   0.30    0  0.21 7933.99
- [8,]   0.35    0  0.22 7960.28
- [9,]   0.40    0  0.23 7990.80
-[10,]   0.45    0  0.23 8007.95
-[11,]   0.50    0  0.23 8034.00
-[12,]   0.55    0  0.24 8069.15
-[13,]   0.60    0  0.29 8360.53
-[14,]   0.65    0  0.29 8360.53
-[15,]   0.70    0  0.29 8360.51
-\end{CodeOutput}
-\end{CodeChunk}
+\end{Sinput}
+\begin{Soutput}
+#>       lambda conv rmsea     BIC
+#>  [1,]   0.00    0  0.19 7805.18
+#>  [2,]   0.05    0  0.19 7816.88
+#>  [3,]   0.10    0  0.43 9460.55
+#>  [4,]   0.15    0  0.43 9460.55
+#>  [5,]   0.20    0  0.43 9460.55
+#>  [6,]   0.25    0  0.43 9460.55
+#>  [7,]   0.30    0  0.43 9460.55
+#>  [8,]   0.35    0  0.43 9460.55
+#>  [9,]   0.40    0  0.43 9460.55
+#> [10,]   0.45    0  0.43 9460.55
+#> [11,]   0.50    0  0.43 9460.55
+#> [12,]   0.55    0  0.43 9460.55
+#> [13,]   0.60    0  0.43 9460.55
+#> [14,]   0.65    0  0.43 9460.55
+#> [15,]   0.70    0  0.43 9460.55
+\end{Soutput}
+\end{Schunk}
 
@@
 
-Instead of examining the \code{out.reg[[1]]} output matrix of parameter
-estimates, users also have the option to plot the trajectory of each of
-the penalized parameters. This is accomplished with
-\code{plot_cv(out.reg,pars=1:9)}, resulting in:
+Instead of examining the \textbf{out.reg[[1]]} output matrix of
+parameter estimates, users also have the option to plot the trajectory
+of each of the penalized parameters. This is accomplished with
+\textbf{plot_cv(out.reg,pars=1:9)}, resulting in:
 
-\begin{CodeChunk}
-\begin{CodeInput}
-plot_cv(out.reg,pars=1:9)
-\end{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
+plot(out.reg,pars=1:9)
+\end{Sinput}
 
-\begin{center}\includegraphics{draft1_files/figure-latex/unnamed-chunk-6-1} \end{center}
-
-\end{CodeChunk}
+\includegraphics{draft1_files/figure-latex/unnamed-chunk-6-1} \end{Schunk}
 
 After a final model (penalty) is chosen, users have the option either
-just use the output from \code{cv_regsem()}, or the final model can be
-re-run with either \code{regsem()} or \code{multi_optim()} to attain
+just use the output from \textbf{cv_regsem()}, or the final model can be
+re-run with either \textbf{regsem()} or \textbf{multi_optim()} to attain
 additional information. In the model above, the best fitting penalty,
@@
 purposes, we can choose a penalty of 0.2. With this, the model is re-run
-with \code{regsem()}
+with \textbf{regsem()}
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
 #summary(mod.out)
-\end{CodeInput}
-\end{CodeChunk}
+\end{Sinput}
+\end{Schunk}
 
 Note that the arguments used above correspond to the same arguments in
-\code{multi_optim()}. However, \code{multi_optim()} has additional
+\textbf{multi_optim()}. However, \textbf{multi_optim()} has additional
 optional arguments corresponding to the number or random starts to try.
-Additional fit indices can be attained through the \code{fit_indices()}
-function.
+Additional fit indices can be attained through the
+\textbf{fit_indices()} function.
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 fit_indices(mod.out)
-\end{CodeInput}
-\begin{CodeOutput}
-$Data_Type
-[1] "Train"
+\end{Sinput}
+\begin{Soutput}
+#> $Data_Type
+#> [1] "Train"
+#> 
+#> $fits
+#>           Fmin         varFit              p          chisq        p.chisq 
+#>        3.35383        0.00000        9.00000     2019.00407        0.00000 
+#>           nfac             df           npar              N baseline.chisq 
+#>        1.00000       36.00000        9.00000      301.00000      918.85159 
+#>    baseline.df           logl            ncp          rmsea    rmsea.lower 
+#>       36.00000    -4704.59420        6.61001        0.42850        0.41202 
+#>    rmsea.upper     rmsea.pval            CFI            TLI            BIC 
+#>             NA        0.00000       -1.24614       -1.24614     9460.55240 
+#>            AIC           CAIC         EBIC.5        EBIC.25 
+#>     9427.18840     9614.76378     9693.74446     9654.19442
+\end{Soutput}
+\end{Schunk}
 
-$fits
-          Fmin         varFit              p          chisq        p.chisq 
-       0.69087        0.00000        9.00000      415.90286        0.00000 
-          nfac             df           npar              N baseline.chisq 
-       1.00000       31.00000       14.00000      301.00000      918.85159 
-   baseline.df           logl            ncp          rmsea    rmsea.lower 
-      36.00000    -3903.04360        1.28301        0.20344        0.18598 
-   rmsea.upper     rmsea.pval            CFI            TLI            BIC 
-            NA        0.00000        0.56402        0.49370     7885.98674 
-           AIC           CAIC         EBIC.5        EBIC.25 
-    7834.08719     7983.11043     8051.12157     8017.06459 
-\end{CodeOutput}
-\end{CodeChunk}
-
-These same fit measures can be accessed through \code{cv_regsem} through
-changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument.
-Finally, instead of assessing these fit indices on the same sample that
-the models were run on, a holdout dataset could be used. This can be
-done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with
-\code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the
-holdout covariance matrix.
+These same fit measures can be accessed through \textbf{cv_regsem}
+through changing the defaults with the \textbf{fit.ret=c("rmsea","BIC")}
+argument. Finally, instead of assessing these fit indices on the same
+sample that the models were run on, a holdout dataset could be used.
+This can be done two ways: either with
+\textbf{cv_regsem(...,fit.ret2="test")} or with
+\textbf{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of
+the holdout covariance matrix.
 
@@
 doesn't make it any easier. Given this, and the number of options
-available in the \pkg{regsem} package, a Google group forum was created
-in order to answer questions and trouble shoot at
+available in the \textbf{regsem} package, a Google group forum was
+created in order to answer questions and trouble shoot at
 \url{https://groups.google.com/forum/\#!forum/regsem}.
@@
 
-To compare the different types of penalties in \pkg{regsem}, we return
-to the the initial example of the latent growth curve model displayed in
-Figure 1. Using the same simulated data, the model can be run in
-\pkg{lavaan} as
+To compare the different types of penalties in \textbf{regsem}, we
+return to the the initial example of the latent growth curve model
+displayed in Figure 1. Using the same simulated data, the model can be
+run in \textbf{lavaan} as
 
-\begin{CodeChunk}
-\begin{CodeInput}
+\begin{Schunk}
+\begin{Sinput}
 mod1 <- "
@@
 lav.growth <- growth(mod1,dat,fixed.x=T)
-\end{CodeInput}
-\end{CodeChunk}
+\end{Sinput}
+\end{Schunk}
 
-Comparing different types of penalties in \pkg{regsem} requires a
-different specification of the \code{type} argument. The options
-currently include maximum likelihood (\code{"none"}), ridge
-(\code{"ridge"}), lasso (\code{"lasso"}), adaptive lasso
-(\code{"alasso"}), elastic net (\code{"enet"}), SCAD (\code{"scad"}),
-and MCP (\code{"mcp"}). For the elastic net, there is an additional
-hyperparameter, \(\alpha\) that controls the tradeoff between ridge and
-lasso penalties. This is specified as \code{alpha=} , which has a
-default of 0.5. Additionally, both the SCAD and MCP have the additional
-hyper parameter of \(\gamma\), which is specified as \code{gamma=} and
-defaults to 3.7 per Fan and Li (2001).
+Comparing different types of penalties in \textbf{regsem} requires a
+different specification of the \textbf{type} argument. The options
+currently include maximum likelihood (\textbf{"none"}), ridge
+(\textbf{"ridge"}), lasso (\textbf{"lasso"}), adaptive lasso
+(\textbf{"alasso"}), elastic net (\textbf{"enet"}), SCAD
+(\textbf{"scad"}), and MCP (\textbf{"mcp"}). For the elastic net, there
+is an additional hyperparameter, \(\alpha\) that controls the tradeoff
+between ridge and lasso penalties. This is specified as \textbf{alpha=}
+, which has a default of 0.5. Additionally, both the SCAD and MCP have
+the additional hyper parameter of \(\gamma\), which is specified as
+\textbf{gamma=} and defaults to 3.7 per Fan and Li (2001).
 
@@
 fit of the BIC are has the fit of each model, resulting in Table 1,
-created using the \pkg{xtable} package (Dahl 2009).
+created using the \textbf{xtable} package (Dahl 2009).
 
@@
 
-This paper provides an introduction to the \pkg{regsem} package,
+This paper provides an introduction to the \textbf{regsem} package,
 outlining the mathematical details of regularized structural equation
 modeling (RegSEM; Jacobucci, Grimm, and McArdle 2016) and the usage of
-the \pkg{regsem} package. RegSEM allows the use of regularization while
-keeping the structural equation model intact, adding penalization
+the \textbf{regsem} package. RegSEM allows the use of regularization
+while keeping the structural equation model intact, adding penalization
 directly into the estimation of the model. The application of RegSEM was
@@
 simulated example and the small simulation, the different types of
-regularization in \pkg{regsem} demonstrated better false positive and
+regularization in \textbf{regsem} demonstrated better false positive and
 negative rates in comparison to maxiumum likelihood across sample sizes.
@@
 gives users a general framework to test models. This was the motivation
-behind creating the \pkg{regsem} package, in that users can estimate
+behind creating the \textbf{regsem} package, in that users can estimate
 models ranging from simple factor analysis models, to latent
@@
 With highly constrained structural equation models, achieving model
-convergence can be particularly problematic in using \pkg{regsem}. For
-instance, with the latent change score model (McArdle and Hamagami
+convergence can be particularly problematic in using \textbf{regsem}.
+For instance, with the latent change score model (McArdle and Hamagami
 2001), Bayesian regularization methods have less difficulty in reaching
@@
 
-Future research with \pkg{regsem} should focus on a number of avenues.
-One is comparing the different forms of regularization, delineating
-which method may be best in which setting. Additionally, as structural
-equation models become larger, with the advent of much larger datasets,
-computational speed will become a principal concern. Although 40
-penalties in the models tested above can be run in a matter of seconds
-on a standard laptop, larger models can take much longer. To handle
-this, future implementation with \pkg{regsem} will test the inclusion of
-different types of optimization, specifically testing whether
-computation of the Hessian (or approximate Hessian) can reduce the
-number of optimization steps.
+Future research with \textbf{regsem} should focus on a number of
+avenues. One is comparing the different forms of regularization,
+delineating which method may be best in which setting. Additionally, as
+structural equation models become larger, with the advent of much larger
+datasets, computational speed will become a principal concern. Although
+40 penalties in the models tested above can be run in a matter of
+seconds on a standard laptop, larger models can take much longer. To
+handle this, future implementation with \textbf{regsem} will test the
+inclusion of different types of optimization, specifically testing
+whether computation of the Hessian (or approximate Hessian) can reduce
+the number of optimization steps.
 
@@
 
-This paper provided a brief overview on the use of the \pkg{regsem}
+This paper provided a brief overview on the use of the \textbf{regsem}
 package as an implementation of regularized structural equation
 modeling. Because structural equation modeling encompasses a wide array
-of latent variable models, the \pkg{regsem} package was created as a
+of latent variable models, the \textbf{regsem} package was created as a
 general package for including different forms of regularization into a
-host of latent variable models. RegSEM, and thus the \pkg{regsem}
+host of latent variable models. RegSEM, and thus the \textbf{regsem}
 package, has been evaluated in a wide array of SEM models, including
@@
 latent change score models (Jacobucci and Grimm 2017), mediation models
-(Serang et al. in press). Future updates to \pkg{regsem} will focus on
-decreasing the computational time of large latent variable models in
+(Serang et al. in press). Future updates to \textbf{regsem} will focus
+on decreasing the computational time of large latent variable models in
 order to provide an avenue of testing for researchers collecting larger
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
+\bibliography{RJreferences}
 
@@
 
-\end{document}
+\address{%
+Ross Jacobucci\\
+University of Notre Dame\\
+118 Haggar Hall, Notre Dame, IN 46556\\
+}
+\href{mailto:rcjacobuc@gmail.com}{\nolinkurl{rcjacobuc@gmail.com}}
